### 2015-08-23 latex/article.tex
restyled

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{parcolumns}
\usepackage[left=2.cm,right=2.cm,top=2.cm,bottom=2.cm]{geometry}
\usepackage[final]{pdfpages} %serve per aggiungere altre pagine pdf al file

\author{Davide Bazzanella}
\title{Improving phase-matching of FWM with temperature}

\begin{document}
\includepdf[pages={1}]{intestazione.pdf} % \input{intestazione.tex}
\newpage
\section{Introduction: Four-Wave Mixing}
Four-Wave Mixing (FWM) is a nonlinear optical effect
\section{Four-Wave Mixing}

\end{document}

### 2015-08-23 gitcode/comsol-extractor/comsol_extractor.m

@@ -1,0 +1,663 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%   refacing of stanamodi v04 from
+%
+%                                         M.Borghi, M.Mancinelli, M.Bernard
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+
+close all;
+clear all;
+clc;
+
+fprintf('Memory Cleared\n');
+
+%% INITIAL PARAMETERS
+
+% setting up initial parameters
+fprintf('\nSetting up initial parameters\n');
+
+[ans1 ans2] = uigetfile({'../comsol/*.mph'});  % choose file to load
+setting.comsolfile = strcat(ans2,ans1);         % filepath of the comsol model
+setting.data_set = 'dset3';                     % name of the dataset in the consol model
+setting.save_path = '../data/';                 % filepath of filesaves
+
+% file-saving parameters
+setting.FILE_EXT	= '.mat';         	% Determines the extension of the files: .mat or .dat
+setting.FILE_TYP	= '-mat';        	% Determines the file type of the files: -mat or -ascii
+
+% processig parameters
+setting.SAVE_H		= false;        	% 1: saves also the H fields
+setting.COMPUTE_H	= true;            	% 1: Compute H from matlab though impedance, 0 loads from COMsol.
+setting.IMAGINARY	= false;            % Extract also imaginary part of the fields
+setting.FIT_ORD     = true;             % Order of the fit in the effective index dispersion as a function of lambda
+setting.TM_TOO      = true;             % classify also TM modes [1=yes]
+setting.SAVE_FIELDS = true;             % 1: saves fields as matrix
+
+% sampling parameters
+setting.smpx		= 1300;             % Total samples per x direction for all the box
+setting.smpy        = 1300;             % Total samples per y direction for all the box
+setting.BOX_CONST   = true;             % If the box is fixed, the grid is generated only once
[…]

### 2015-08-23 gitcode/comsol-extractor/get_par.m

@@ -1,0 +1,12 @@
+function [ output_args ] = get_par( model, parameter, data_set)
+%UNTITLED3 Summary of this function goes here
+%   Detailed explanation goes here
+
+tmp = mphglobal(model,{parameter},'dataset', data_set,'outersolnum','all');
+tmp = tmp(1,:);
+tmp = sort(tmp);
+tmp = unique(tmp);
+output_args = tmp;
+
+clear ans tmp
+end

### 2015-08-23 gitcode/phase-matching/phasematching.m

@@ -1,0 +1,460 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+%   This file will search for phase matching condition                    %
+%                                                                         %
+%                                                         D. Bazzanella   %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Import HTE & HTM structures
+
+fprintf('\nChoose the file to import.\nShould be something like yyyy-MM-dd_HH:mm:ss.mat\n');
+[ans1 ans2] = uigetfile({'../data/*.mat'});     % choose file to load
+load( strcat(ans2, ans1) );
+
+% adjust parameters
+vec.wlen = vec.wlen'.*1e-6;                     % [m]
+%vec.temp = vec.temp'-vec.temp(1);
+
+clear ans1 ans2
+
+%% Set initial parameters
+
+tic
+fprintf('\nSetting initial parameters\n');
+% physical constants
+const.c     = 299792458;            % [m/s]
+
+% waves parameters
+    % pump structure
+    ws.pump.wlen   = 1.55e-6;              % [m]
+    ws.pump.freq   = const.c/ws.pump.wlen;    % [1/s]
+
+    % signal structure
+    ws.signal.wlen = 1.4e-6;               % [m]
+    ws.signal.freq = const.c/ws.signal.wlen;  % [1/s]
+
+    % idler structure
+    ws.idler.wlen  = 1.7e-6;               % [m]
+    ws.idler.freq  = const.c/ws.idler.wlen;   % [1/s]
+
+par.n_sample = 51; % should be an odd number
+par.stepF = (1.7e-6 -1.4e-6)/(par.n_sample - 1);
+vec.sample_wlen = zeros(par.n_sample,1);
+for ( ww=1:par.n_sample )
+    vec.sample_wlen(ww) = 1.4e-6 + ww*par.stepF;
+end
+
+clear ww
+toc
+
+%% Temperature dependence analysis
+
+tic
+fprintf('\nAnalysing the temperature dependence of the data\n');
+% temperature dependence of HTE modes
+for jj=1:par.n_wg_wid               % number of widths
+    for kk=1:par.n_wg_hgt           % number of heights
[…]

### 2015-08-23 gitcode/phase-matching/phasematching.m
commented betas(T)

@@ -8,15 +8,36 @@
 
 %% Import HTE & HTM structures
 
-fprintf('\nChoose the file to import.\nShould be something like yyyy-MM-dd_HH:mm:ss.mat\n');
-[ans1 ans2] = uigetfile({'../data/*.mat'});     % choose file to load
+ans1 = 0;
+while ( ans1 == 0 )
+    % Construct a questdlg with three options
+    choice = questdlg('Import a file or to exit the program?', 'Import File', 	'Import File','Exit program', ...
+        'Import File');
+    % Handle response
+    switch choice
+        case 'Import File'
+            disp('\nFile chosen.\n')
+            ans1 = 0;
+        case 'Exit program'
+            %disp('\n\nExiting right now.')
+            clear ans1 choice
+            error('Exiting right now.');
+    end
+    
+    if (ans1 == 0 )
+        fprintf('\nChoose the file to import.\nShould be something like yyyy-MM-dd_HH:mm:ss.mat\n');
+        [ans1 ans2] = uigetfile({'../data/*.mat'});     % choose file to load
+    end
+end
+    
 load( strcat(ans2, ans1) );
 
 % adjust parameters
 vec.wlen = vec.wlen'.*1e-6;                     % [m]
+vec.temp = vec.temp';
 %vec.temp = vec.temp'-vec.temp(1);
 
-clear ans1 ans2
+clear ans1 ans2 choice
 
 %% Set initial parameters
 
@@ -86,6 +107,7 @@ for jj=1:par.n_wg_wid               % number of widths
                 end
                 
                 %% beta1
+                %{
 %fprintf(' b1 ');
                 if ~( isempty(HTE.DIM(jj,kk).T(1).O(mm).beta1) )
                     x = vec.temp;
@@ -202,6 +224,7 @@ for jj=1:par.n_wg_wid               % number of widths
                 end
                
 %fprintf('\n');
+                %}
 
             end
         end
@@ -244,13 +267,21 @@ for jj=1:par.n_wg_wid               % number of widths
                 end
                 
                 %% beta1
+                %{
 %fprintf(' b1 ');
-                if ~( isempty(HTM.DIM(jj,kk).T(1).O(mm).beta1) )
+                emp =  par.n_temp;
+                for tt=1:par.n_temp
+                    if isempty( HTM.DIM(jj,kk).T(tt).O(mm).beta1 )
+                        emp = emp -1;
+                    end
+                end
+
+                if ( emp > 1 )
[…]

### 2015-08-23 latex/article.tex
better phasematching outputs and draft of linear optics

@@
 \includepdf[pages={1}]{intestazione.pdf} % \input{intestazione.tex}
+
 \newpage
-\section{Introduction: Four-Wave Mixing}
+\section{Introduction}
+\subsection{Motivation}
+\subsection{Four-Wave Mixing}
 Four-Wave Mixing (FWM) is a nonlinear optical effect
-\section{Four-Wave Mixing}
+
+\section{Linear optics}
+In linear optics the technology for trasmitting a light wave by confining it in a finite space is the guided-wave optics.
+The instruments employed for achieving such purpose are called waveguides.
+\subsection{Silicon waveguides}
+Silicon waveguides are dielectric waveguides and make use of the interface between two media with different refractive index.
+Precisely they exploit the phenomenon of total internal reflection, which states that if a propagating wave reaches a boundary between two mediums, one with higher refractive index ($n_H$) and another with lower refractive index ($n_L$), with an angle of incidence (relative to the norm of the interface) greater than the \textit{critical angle}, then the wave is completely reflected in the first medium.
+%accorciare la precedente frase%
+The critical angle can be obtained by the Snell law.
+
+$$	\theta_C = \arcsin \left( \frac{n_L}{n_H} \right)$$
+
+Silicon waveguides are composed by core and cladding \textbf{(?)}. %is called cladding only for fiber or also for slab/strip wg?
+The former is the higher refractive index medium in which the wave is confined, the latter is the lower refractive index medium which surrounds the core, thus creating the interface.
+Theoretically the cladding could also be vacuum.
+
+Considering an ideal dielectric waveguide (no absorption) and the total field distribution as sum of transverse electromagnetic (TEM) plane waves is possible to study the propagation of the wave along the waveguide with an electromagnetic analysis.
+Furthermore it can be shown that not all field distribution are transmitted through the waveguide without energy loss.
+
+% Modes are fields that maintain the same transverse distribution and polarization at all locations along the waveguide axis.
+Those field distributions, which maintain the same transverse distribution and polarization at all locations along the waveguide axis, are called \textbf{modes}.
+These modes can be categorized in two main groups, depending on the polarization of the wave: transverse electric (TE) modes and transverse magnetic (TM) modes, which have respectively the electric and magnetic field transverse to the waveguide axis.
+Both TE and TM modes can be again classified by their order, that is proportional to the number of maxima of the modulus of the electric and magnetic fields in the core section.
+
+\subsection{Rectangular dielectric waveguides}
+In a rectangular (2D) dielectric waveguide
+
+\section{Non-linear optics}
+
+\subsection{Third order effect: Four-Wave Mixing}
+
+\section{Simulating and coding ?}
+
+\section{Prototyping}
+\subsection{Heater configurations}
+\subsection{Different geometries}
 

### 2015-08-23 gitcode/phase-matching/phasematching.m

@@ -452,21 +452,24 @@ for jj=1:par.n_wg_wid                                   % number of widths ?
                 tmp = [vec.comb(oo,2) vec.comb(oo,3)];
                 results.DIM(jj,kk).PO( vec.comb(oo,1) ).orders = vertcat(results.DIM(jj,kk).PO( vec.comb(oo,1) ).orders, tmp);
                 tmp = zeros(par.n_sample,1);
+                fprintf('m_ord:\n\tpump %d,\tsignal %d,\tidler %d\nwlen:\n', vec.comb(oo,1), vec.comb(oo,2), vec.comb(oo,3) );
                 for ww=1:par.n_sample
                     ws.signal.wlen = vec.sample_wlen(ww);
                     % conservation of energy
                     ws.idler.wlen  = 2*ws.pump.wlen - ws.signal.wlen;
                     
                     % conservation of momentum
-                    fprintf('\npump ');
+                    fprintf('\tp ');
                     kp = wavenumber(1,jj,kk,vec.comb(oo,1), ws.pump.wlen, temp, vec, HTE, HTM, TOC );
-                    fprintf(' signal ');
+                    fprintf('s ');
                     ks = wavenumber(1,jj,kk,vec.comb(oo,2), ws.signal.wlen, temp, vec, HTE, HTM, TOC );
-                    fprintf(' idler ');
+                    fprintf('i ');
                     ki = wavenumber(1,jj,kk,vec.comb(oo,3), ws.idler.wlen, temp, vec, HTE, HTM, TOC );
                     tmp(ww) = 2*kp -ks -ki ;
+                    fprintf('\n');
                 end
                 results.DIM(jj,kk).PO( vec.comb(oo,1) ).data = vertcat(results.DIM(jj,kk).PO( vec.comb(oo,1) ).data, tmp');
+                fprintf('\n');
             end
             
         end

### 2015-08-23 gitcode/phase-matching/wavenumber.m

@@ -20,7 +20,7 @@ Fmega  = cps/wlen - cps/wlen0;  % [1/ps]
 % c/Omega is in [m/s/m]=[1/s] --> (c/Omega)^x*beta_x = [s^x/m/s^x] = [1/m]
 % alpha is in [1/T] --> alpha*T = [1]
 if ( TE == 1 )
-    fprintf('mord %d wlen %d\n', wid, hgt, order, index.wlen );
+    fprintf('%d,\t', index.wlen );
     tmp =       2*pi/wlen0     * HTE.DIM(wid, hgt).T(1).O(order).neff(index.wlen);           % [1/m] ~1e7
     tmp = tmp + (Fmega)        * HTE.DIM(wid, hgt).T(1).O(order).beta1(index.wlen)*100;      % [1/m] ~1e6
     tmp = tmp + (Fmega)^2 / 2  * HTE.DIM(wid, hgt).T(1).O(order).beta2(index.wlen)*100;      % [1/m] ~1e4

### 2015-08-25 gitcode/phase-matching/phasematching.m
swapped taylor with fit

@@ -11,26 +11,32 @@
 ans1 = 0;
 while ( ans1 == 0 )
     % Construct a questdlg with three options
-    choice = questdlg('Import a file or to exit the program?', 'Import File', 	'Import File','Exit program', ...
+    choice = questdlg('Import a file or to exit the program?', 'Import File', 	'Import File', 'Exit program', 'Go on', ...
         'Import File');
     % Handle response
     switch choice
         case 'Import File'
-            disp('\nFile chosen.\n')
+            disp('File chosen.')
             ans1 = 0;
         case 'Exit program'
             %disp('\n\nExiting right now.')
             clear ans1 choice
             error('Exiting right now.');
+        %{
+        case 'Go on'
+            disp('\nGoing on...\n');
+            ans1 = 1;
+        %}
     end
     
     if (ans1 == 0 )
         fprintf('\nChoose the file to import.\nShould be something like yyyy-MM-dd_HH:mm:ss.mat\n');
         [ans1 ans2] = uigetfile({'../data/*.mat'});     % choose file to load
+        
+        load( strcat(ans2, ans1) );
     end
 end
     
-load( strcat(ans2, ans1) );
 
 % adjust parameters
 vec.wlen = vec.wlen'.*1e-6;                     % [m]
@@ -52,18 +58,18 @@ const.c     = 299792458;            % [m/s]
     ws.pump.freq   = const.c/ws.pump.wlen;    % [1/s]
 
     % signal structure
-    ws.signal.wlen = 1.4e-6;               % [m]
+    ws.signal.wlen = 1.45e-6;               % [m]
     ws.signal.freq = const.c/ws.signal.wlen;  % [1/s]
 
     % idler structure
-    ws.idler.wlen  = 1.7e-6;               % [m]
+    ws.idler.wlen  = 1.65e-6;               % [m]
     ws.idler.freq  = const.c/ws.idler.wlen;   % [1/s]
 
-par.n_sample = 51; % should be an odd number
-par.stepF = (1.7e-6 -1.4e-6)/(par.n_sample - 1);
+par.n_sample = 101; % should be an odd number, to center the pump wlen.
+par.stepF = (1.65e-6 -1.45e-6)/(par.n_sample - 1);
 vec.sample_wlen = zeros(par.n_sample,1);
 for ( ww=1:par.n_sample )
[…]

### 2015-08-25 gitcode/phase-matching/wavenumber.m

@@ -8,9 +8,11 @@ function [ output ] = wavenumber( TE, wid, hgt, order, wlen, temp, vec, HTE, HTM
 c     = 299792458;  % [m/s]
 cps   = c*1e-12;	% [m/ps]
 
+
 [value.wlen, index.wlen] = min( abs(vec.wlen - wlen) );
 [value.temp, index.temp] = min( abs(vec.temp - temp) );
 
+%{
 wlen0 = vec.wlen(index.wlen);
 Omega  = wlen - wlen0;
 Fmega  = cps/wlen - cps/wlen0;  % [1/ps]
@@ -39,4 +41,18 @@ if ( TE == 0 )
     
     output = tmp;
 end
+%}
 
+if ( TE == 1 )
+    %fprintf('%d,\t', index.wlen );
+    tmp =       2*pi/wlen * feval( HTE.DIM(wid, hgt).T(1).O(order).fit_neff, wlen );
+    tmp = tmp + 2*pi/wlen * TOC.TE.DIM(wid, hgt).O(order).WL(index.wlen).alpha * temp;  % [1/m] ~1e5
+    
+    output = tmp;
+end
+if ( TE == 0 )
+    tmp =       2*pi/wlen * feval( HTE.DIM(wid, hgt).T(1).O(order).fit_neff, wlen );
+    tmp = tmp + 2*pi/wlen * TOC.TM.DIM(wid, hgt).O(order).WL(index.wlen).alpha * temp;  % [1/m] ~1e5
+    
+    output = tmp;
+end

### 2015-08-26 gitcode/comsol-extractor/comsol_extractor_v2.m
structures to matrixes

@@ -1,0 +1,366 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%   refacing of stanamodi v04 from
+%
+%                                         M.Borghi, M.Mancinelli, M.Bernard
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+
+close all;
+clear all;
+clc;
+
+fprintf('Memory Cleared\n');
+
+%% INITIAL PARAMETERS
+
+% setting up initial parameters
+fprintf('\nSetting up initial parameters\n');
+
+[ans1, ans2] = uigetfile({'../comsol/*.mph'});  % choose file to load
+setting.comsolfile = strcat(ans2,ans1);         % filepath of the comsol model
+setting.data_set = 'dset3';                     % name of the dataset in the consol model
+setting.save_path = '../data/';                 % filepath of filesaves
+
+% file-saving parameters
+setting.FILE_EXT	= '.mat';         	% Determines the extension of the files: .mat or .dat
+setting.FILE_TYP	= '-mat';        	% Determines the file type of the files: -mat or -ascii
+
+% processig parameters
+setting.SAVE_H		= false;        	% 1: saves also the H fields
+setting.COMPUTE_H	= true;            	% 1: Compute H from matlab though impedance, 0 loads from COMsol.
+setting.IMAGINARY	= false;            % Extract also imaginary part of the fields
+setting.FIT_ORD     = true;             % Order of the fit in the effective index dispersion as a function of lambda
+setting.TM_TOO      = true;             % classify also TM modes [1=yes]
+setting.SAVE_FIELDS = true;             % 1: saves fields as matrix
+
+% sampling parameters
+setting.smpx		= 1300;             % Total samples per x direction for all the box
+setting.smpy        = 1300;             % Total samples per y direction for all the box
+setting.BOX_CONST   = true;             % If the box is fixed, the grid is generated only once
[…]

### 2015-08-26 gitcode/phase-matching/phasematching_v2.m

@@ -6,7 +6,7 @@
 %                                                                         %
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%% Import HTE & HTM structures
+%% Import data structures
 
 ans1 = 0;
 while ( ans1 == 0 )
@@ -31,17 +31,11 @@ while ( ans1 == 0 )
     
     if (ans1 == 0 )
         fprintf('\nChoose the file to import.\nShould be something like yyyy-MM-dd_HH:mm:ss.mat\n');
-        [ans1 ans2] = uigetfile({'../data/*.mat'});     % choose file to load
+        [ans1, ans2] = uigetfile({'../data/*.mat'});     % choose file to load
         
         load( strcat(ans2, ans1) );
     end
 end
-    
-
-% adjust parameters
-vec.wlen = vec.wlen'.*1e-6;                     % [m]
-vec.temp = vec.temp';
-%vec.temp = vec.temp'-vec.temp(1);
 
 clear ans1 ans2 choice
 
@@ -50,32 +44,32 @@ clear ans1 ans2 choice
 tic
 fprintf('\nSetting initial parameters\n');
 % physical constants
-const.c     = 299792458;            % [m/s]
+const.c     = 299792458;        % [m/s]
 
-% waves parameters
-    % pump structure
-    ws.pump.wlen   = 1.55e-6;              % [m]
-    ws.pump.freq   = const.c/ws.pump.wlen;    % [1/s]
+% phase matching parameters
+% wlens
+pm.pump_w   = 1.55e-6;          % [m]
+pm.signal_w = 1.45e-6;          % [m]
+pm.idler_w  = 1.65e-6;          % [m]
 
-    % signal structure
-    ws.signal.wlen = 1.45e-6;               % [m]
-    ws.signal.freq = const.c/ws.signal.wlen;  % [1/s]
+% low & high wlen
+pm.low_w = 1.45e-6;             % [m]
+pm.high_w = 1.65e-6;            % [m]
 
-    % idler structure
-    ws.idler.wlen  = 1.65e-6;               % [m]
-    ws.idler.freq  = const.c/ws.idler.wlen;   % [1/s]
+% number of points in wlen interval [low_w, high_w]
+pm.n_sample = 101;              % should be an odd number, to center the pump wlen.
[…]

### 2015-08-26 gitcode/phase-matching/phasematching_v2.m
working plot

@@ -343,7 +343,7 @@ for ww=1:par.n_wg_wid                                   % number of widths ?
             if pm.ok_fit < 1
                 results.orders(oo,:) = pm.comb(oo,:);
                 
-                fprintf('mode orders:\tpump %d,\tsignal %d,\tidler %d (sol %d/%d)\n', pm.comb(oo,1), pm.comb(oo,2), pm.comb(oo,3), oo, pm.n_results );
+                fprintf('mode orders:\tpump %d,\tsignal %d,\tidler %d (sol %d/%d)\n', pm.comb(oo,2), pm.comb(oo,4), pm.comb(oo,6), oo, pm.n_results );
                 for ll=1:pm.n_sample
                     pm.signal_w = vec.sample_wlen(ll);
                     % conservation of energy
@@ -373,15 +373,21 @@ toc
 clear ww hh oo ll ff tt kp ks ki ans
 
 %% surface plot w/ temperature
+% it plots only surfaces that cross the plane z=0
 xdata = vec.sample_wlen;
 ydata = vec.temp;
 
-for ii=1:par.n_modi
-    zdata = 1;%results.data(,
-    if ~isempty(ydata)
-        figure(ii)
-        surf(xdata,ydata,permute(zdata,[2,1]) );
-        grid on
+for rr=1:pm.n_results
+    fprintf('\n%d\n',rr);
+    if ~isnan(results.data(:,:,rr))
+        zdata = results.data(:,:,rr);
+        if min(zdata(:))*max(zdata(:))<=0
+            figure(rr)
+            [xData, yData, zData] = prepareSurfaceData( xdata, ydata, zdata );
+            [fitresult, gof] = fit( [xData, yData], zData, 'loess', 'Normalize', 'on' );
+            plot( fitresult, [xData, yData], zData );
+            grid on;
+        end
     end
 end
 
@@ -391,6 +397,7 @@ clear xdata ydata ans ii
  
 [xData, yData, zData] = prepareSurfaceData( xdata, ydata, zdata );
 [fitresult, gof] = fit( [xData, yData], zData, 'loess', 'Normalize', 'on' );
+plot( fitresult, [xData, yData], zData );
  %}
  
  %%

### 2015-08-27 gitcode/comsol-extractor/comsol_extractor_v2.m
plot of delta_k and l_coh

@@ -8,7 +8,6 @@
 %%
 
 close all;
-clear all;
 clc;
 
 fprintf('Memory Cleared\n');

### 2015-08-27 gitcode/phase-matching/phasematching.m

@@ -31,7 +31,7 @@ while ( ans1 == 0 )
     
     if (ans1 == 0 )
         fprintf('\nChoose the file to import.\nShould be something like yyyy-MM-dd_HH:mm:ss.mat\n');
-        [ans1 ans2] = uigetfile({'../data/*.mat'});     % choose file to load
+        [ans1, ans2] = uigetfile({'../data/*.mat'});     % choose file to load
         
         load( strcat(ans2, ans1) );
     end
@@ -68,7 +68,7 @@ const.c     = 299792458;            % [m/s]
 par.n_sample = 101; % should be an odd number, to center the pump wlen.
 par.stepF = (1.65e-6 -1.45e-6)/(par.n_sample - 1);
 vec.sample_wlen = zeros(par.n_sample,1);
-for ( ww=1:par.n_sample )
+for ww=1:par.n_sample
     vec.sample_wlen(ww) = 1.45e-6 + ww*par.stepF;
 end
 

### 2015-08-27 gitcode/phase-matching/phasematching_v2.m

@@ -65,7 +65,16 @@ for ww=1:pm.n_sample
     vec.sample_wlen(ww) = pm.low_w + ww*pm.step;
 end
 
-clear ww
+% sampling temperature
+pm.n_sample_t = 11;
+pm.step_t = (vec.temp(end) - vec.temp(1) )/(pm.n_sample_t - 1);
+
+vec.sample_temp = zeros(pm.n_sample_t,1);
+for tt=1:pm.n_sample_t
+    vec.sample_temp(tt) = vec.temp(1) + tt*pm.step_t;
+end
+
+clear ww tt
 toc
 
 %% Temperature dependence analysis
@@ -317,7 +326,7 @@ fprintf('\nCreating structure of data for results...');
 
 results.orders  = zeros(pm.n_results,6).*NaN;
 
-results.data    = zeros(pm.n_sample,par.n_temp, pm.n_results, par.n_wg_wid, par.n_wg_hgt).*NaN;
+results.data    = zeros(pm.n_sample,pm.n_sample_t, pm.n_results, par.n_wg_wid, par.n_wg_hgt).*NaN;
 
 fprintf('\b\b\b:\tstructure created.\n');
 clear jj kk oo
@@ -350,12 +359,14 @@ for ww=1:par.n_wg_wid                                   % number of widths ?
                     pm.idler_w  = 2*pm.pump_w - pm.signal_w;
                     
                     % conservation of momentum
-                    for tt=1:par.n_temp
+                    for tt=1:pm.n_sample_t
 %                        fprintf('\tp ');
-                        %kp = wavenumber(1,ww,hh,vec.comb(oo,1), pm.pump.wlen, vec.temp(tt) , vec, HTE, HTM, TOC );
-                        kp = 2*pi*feval( data.fit_neff( ww, hh, pm.comb(oo,1), pm.comb(oo,2)).fit, pm.pump_w, vec.temp(tt))/pm.pump_w;
-                        ks = 2*pi*feval( data.fit_neff( ww, hh, pm.comb(oo,3), pm.comb(oo,4)).fit, pm.signal_w, vec.temp(tt))/pm.signal_w;
-                        ki = 2*pi*feval( data.fit_neff( ww, hh, pm.comb(oo,5), pm.comb(oo,6)).fit, pm.idler_w, vec.temp(tt))/pm.idler_w;
[…]

### 2015-08-28 gitcode/phase-matching/phasematching_v2.m
better graphs

@@ -391,20 +391,23 @@ ydata = vec.sample_temp;
 f(pm.n_results) = figure(pm.n_results);
 close(f(pm.n_results));
 
-for rr=1:pm.n_results
+for rr=1:pm.n_results-100;
     fprintf('\n%d\n',rr);
-    if ~isnan(results.data(:,:,rr))
+    if ~isnan(results.data(:,:,rr))    
         zdata = results.data(:,:,rr);
         if min(zdata(:))*max(zdata(:))<=0
             f(rr) = figure(rr);
+            str_title = strcat('Solution %d: combination (p,s,i) %d %d %d',rr, pm.comb(rr,2), pm.comb(rr,4), pm.comb(rr,6));
+            title(str_title);
             set(f(rr), 'Position', [100, 100, 960, 480]);
             [xData, yData, zData] = prepareSurfaceData( xdata, ydata, zdata );
-            
+            % zData = [m] --> 2pi*100./zData = [cm]
             % fit & plot Delta_k
             subplot(1,2,1)
             title('delta_k');
-            [fitresult, ~] = fit( [xData, yData], zData, 'loess', 'Normalize', 'on' );
-            plot( fitresult, [xData, yData], zData );
+            %[fitresult, ~] = fit( [xData, yData], zData, 'loess', 'Normalize', 'on' );
+            [fitresult, ~] = fit( [xData, yData], zData./100, 'cubicinterp', 'Normalize', 'on' ); % zData in [1/cm]
+            plot( fitresult, [xData, yData], zData./100 );
             grid on;
             
             hold on;
@@ -412,19 +415,26 @@ for rr=1:pm.n_results
             % fit & plot l_coh
             subplot(1,2,2);
             title('L_coh [cm]');
-            %zData = 2*pi*100./zData;            % 2pi./zData = [m] --> 2pi*100./zData = [cm]
+            zData = 2*pi*100./abs(zData);            % 2pi./zData = [m] --> 2pi*100./zData = [cm]
+            % eliminates +inf points
+            if max(zData) == inf
+                indexes = find(max(zData) == zData);
+                zData(indexes) = -inf;
+                zData(indexes) = max(zData)*10;
+            end
             %[fitresult, ~] = fit( [xData, yData], zData, 'loess', 'Normalize', 'on' );
[…]

### 2015-08-28 gitcode/comsol-extractor/comsol_extractor_v2.m
update temperature vetors & FWM template with 101f x 8t

@@ -80,7 +80,7 @@ vec.temp    = zeros(par.n_temp,1);				% Vector for the temperatures
 vec.wlen    = get_par(model, 'la', setting.data_set)'.*1e-6;                     % 'la' would be in [um]
 vec.wid     = get_par(model, 'w', setting.data_set)';
 vec.hgt     = get_par(model, 'hg', setting.data_set)';                      % {'hn'} ?
-vec.temp    = get_par(model, 'Temp', setting.data_set)';
+vec.temp    = get_par(model, 'Temp', setting.data_set)'+273.15;		    % [K]
 
 % get materials
 par.neff_si     = mphglobal(model,{'n_si'},'dataset', setting.data_set,'outersolnum',1);

### 2015-08-30 latex/article.tex
linear optic draft
swapped taylor with fit
it appears no phasematch

@@
 \usepackage[final]{pdfpages} %serve per aggiungere altre pagine pdf al file
+\usepackage{siunitx}
 
@@
 \subsection{Motivation}
-\subsection{Four-Wave Mixing}
+\subsection{Degenerate Four-Wave Mixing}
 Four-Wave Mixing (FWM) is a nonlinear optical effect
@@
 Silicon waveguides are dielectric waveguides and make use of the interface between two media with different refractive index.
-Precisely they exploit the phenomenon of total internal reflection, which states that if a propagating wave reaches a boundary between two mediums, one with higher refractive index ($n_H$) and another with lower refractive index ($n_L$), with an angle of incidence (relative to the norm of the interface) greater than the \textit{critical angle}, then the wave is completely reflected in the first medium.
+Precisely they exploit the phenomenon of total internal reflection: if a propagating wave reaches a boundary between two mediums, one with higher refractive index ($n_H$) and another with lower refractive index ($n_L$), with an angle of incidence greater than the \textit{critical angle}, then the wave is completely reflected in the first medium.
 %accorciare la precedente frase%
-The critical angle can be obtained by the Snell law.
+Angles are defined relative to the normal vector of the interface and the critical angle can be obtained by the Snell law:
 
@@
 % Modes are fields that maintain the same transverse distribution and polarization at all locations along the waveguide axis.
-Those field distributions, which maintain the same transverse distribution and polarization at all locations along the waveguide axis, are called \textbf{modes}.
+Those field distributions, which maintain the same transverse distribution and polarization at all locations along the waveguide axis, are called modes.
 These modes can be categorized in two main groups, depending on the polarization of the wave: transverse electric (TE) modes and transverse magnetic (TM) modes, which have respectively the electric and magnetic field transverse to the waveguide axis.
@@
 \subsection{Rectangular dielectric waveguides}
-In a rectangular (2D) dielectric waveguide
+In a rectangular dielectric waveguide the classification of modes need two indexes because we have two degrees of freedom.
 
 \section{Non-linear optics}
-
+A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field, $\mathrm{P} = \varepsilon_0 \chi \mathrm{E}$, where $\varepsilon_0$ is the permittivity of free space and $\chi$ is the susceptibility of the medium.
+A nonlinear dielectric medium is characterized by a nonlinear relation between P and E, such as
+$$\mathrm{P} = \varepsilon_0\chi \mathrm{E} + 2\mathrm{d}\mathrm{E}^2 + 4\chi^{(3)}\mathrm{E}^3 + \cdots$$
+In everyday condition linear effects are much larger than nonlinear ones.
+The relation between $\mathrm{P}$ and $\mathrm{E}$ becomes nonlinear when $\mathrm{E}$ has a value comparable to interatomic electric fields, which are typically $\sim 10^5-10^8$ \si{\V\per\m}
 \subsection{Third order effect: Four-Wave Mixing}
@@
 
+\newpage
+\begin{thebibliography}{9}
+\bibitem{agrawal} G. Agrawal. Nonlinear Fiber Optics, 5th edition. 2013
+\bibitem{saleh} B. E. A. Saleh, M. C. Teich. Fundamentals of photonics, 2nd edition. 2007
+\end{thebibliography}
 \end{document}
+% Ref. \cite{agrawal}

### 2015-08-30 gitcode/comsol-extractor/comsol_extractor_v3.m

@@ -1,0 +1,279 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%   fork of stanamodi v04 of M.Borghi, M.Mancinelli, M.Bernard from
+%
+%                                                         D. Bazzanella   
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+
+close all;
+clc;
+
+fprintf('Memory Cleared\n');
+
+%% INITIAL PARAMETERS
+
+% setting up initial parameters
+fprintf('\nSetting up initial parameters\n');
+
+[ans1, ans2] = uigetfile({'../comsol/*.mph'});  % choose file to load
+setting.comsolfile = strcat(ans2,ans1);         % filepath of the comsol model
+setting.data_set = 'dset3';                     % name of the dataset in the consol model
+setting.save_path = '../data/';                 % filepath of filesaves
+
+% file-saving parameters
+setting.FILE_EXT	= '.mat';         	% Determines the extension of the files: .mat or .dat
+setting.FILE_TYP	= '-mat';        	% Determines the file type of the files: -mat or -ascii
+
+% processig parameters
+setting.SAVE_H		= false;        	% 1: saves also the H fields
+setting.COMPUTE_H	= true;            	% 1: Compute H from matlab though impedance, 0 loads from COMsol.
+setting.IMAGINARY	= false;            % Extract also imaginary part of the fields
+setting.FIT_ORD     = true;             % Order of the fit in the effective index dispersion as a function of lambda
+setting.TM_TOO      = true;             % classify also TM modes [1=yes]
+setting.SAVE_FIELDS = true;             % 1: saves fields as matrix
+
+% sampling parameters
+setting.smpx		= 1300;             % Total samples per x direction for all the box
+setting.smpy        = 1300;             % Total samples per y direction for all the box
+setting.BOX_CONST   = true;             % If the box is fixed, the grid is generated only once
[…]

### 2015-08-30 gitcode/phase-matching/phasematching_v2.m

@@ -391,7 +391,7 @@ ydata = vec.sample_temp;
 f(pm.n_results) = figure(pm.n_results);
 close(f(pm.n_results));
 
-for rr=1:pm.n_results-100;
+for rr=1:pm.n_results;
     fprintf('\n%d\n',rr);
     if ~isnan(results.data(:,:,rr))    
         zdata = results.data(:,:,rr);

### 2015-08-30 gitcode/phase-matching/phasematching_v3.m

@@ -1,0 +1,375 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+%   This file will search for phase matching condition                    %
+%                                                                         %
+%                                                         D. Bazzanella   %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Import data structures
+
+ans1 = 0;
+while ( ans1 == 0 )
+    % Construct a questdlg with three options
+    choice = questdlg('Import a file or to exit the program?', 'Import File', 	'Import File', 'Exit program', 'Go on', ...
+        'Import File');
+    % Handle response
+    switch choice
+        case 'Import File'
+            disp('File chosen.')
+            ans1 = 0;
+        case 'Exit program'
+            %disp('\n\nExiting right now.')
+            clear ans1 choice
+            error('Exiting right now.');
+        %{
+        case 'Go on'
+            disp('\nGoing on...\n');
+            ans1 = 1;
+        %}
+    end
+    
+    if (ans1 == 0 )
+        fprintf('\nChoose the file to import.\nShould be something like yyyy-MM-dd_HH:mm:ss.mat\n');
+        [ans1, ans2] = uigetfile({'../data/*.mat'});     % choose file to load
+        
+        load( strcat(ans2, ans1) );
+    end
+end
+
+% physical constants
+const.c     = 299792458;        % [m/s]
+const.T     = 293.15;           % [K]
+
+% rescale unit of measure
+vec.wid  = vec.wid .* 1e-6;     % [m]
+vec.hgt  = vec.hgt .* 1e-6;     % [m]
+vec.temp = vec.temp + const.T;  % [K]
+
+clear ans1 ans2 choice
+
+%% Set initial parameters
+
+tic
+fprintf('\nSetting initial parameters\n');
+
+% phase matching parameters
+% wlens
+pm.pump_w   = 1.55e-6;          % [m]
+pm.signal_w = 1.45e-6;          % [m]   it's an example wl
+pm.idler_w  = 1.65e-6;          % [m]   it's an example wl
+
+% low & high wlen
[…]

### 2015-08-30 gitcode/createFit.m
stuck

@@ -1,0 +1,38 @@
+function [fitresult, gof] = createFit(wlvec, tvec, zdata)
+%CREATEFIT(WLVEC,TVEC,ZDATA)
+%  Create a fit.
+%
+%  Data for 'untitled fit 1' fit:
+%      X Input : wlvec
+%      Y Input : tvec
+%      Z Output: zdata
+%  Output:
+%      fitresult : a fit object representing the fit.
+%      gof : structure with goodness-of fit info.
+%
+%  See also FIT, CFIT, SFIT.
+
+%  Auto-generated by MATLAB on 28-Aug-2015 18:47:18
+
+
+%% Fit: 'untitled fit 1'.
+[xData, yData, zData] = prepareSurfaceData( wlvec, tvec, zdata );
+
+% Set up fittype and options.
+ft = fittype( 'poly52' );
+
+% Fit model to data.
+[fitresult, gof] = fit( [xData, yData], zData, ft );
+
+% Plot fit with data.
+figure( 'Name', 'untitled fit 1' );
+h = plot( fitresult, [xData, yData], zData );
+legend( h, 'untitled fit 1', 'zdata vs. wlvec, tvec', 'Location', 'NorthEast' );
+% Label axes
+xlabel wlvec
+ylabel tvec
+zlabel zdata
+grid on
+view( 0.5, 38.0 );
+
+

### 2015-08-30 gitcode/phase-matching/phasematching_v3.m

@@ -144,15 +144,15 @@ for ww=1:par.n_wg_wid
                     zdata = data.neff(:,:,ww,hh,pp,mm);
                     zdata = zdata(:);
                     
-                    [fit1, gof1] = fit( [xdata(disp.pte),ydata(disp.pte)],zdata(disp.pte),setting.fit_str);
-                    data.fit_neff(ww,hh,pp,mm).exist = true;
+                    [fit1, gof1] = fit( [xdata(disp.pte),ydata(disp.pte)],zdata(disp.pte),setting.fit_str, 'Normalize', 'on');
+                    data.fit_neff(ww,hh,pp,mm).exist = true;                % 'Normalize', 'on' means it center & scales data
                     data.fit_neff(ww,hh,pp,mm).fit = fit1;
                     data.fit_neff(ww,hh,pp,mm).gof = gof1;
                     
                     zdata = data.Aeff(:,:,ww,hh,pp,mm).*1e12;   % why is there .*1e12 ?
                     zdata = zdata(:);
                     
-                    [fit1, gof1] = fit( [xdata(disp.pte),ydata(disp.pte)],zdata(disp.pte),setting.fit_str);
+                    [fit1, gof1] = fit( [xdata(disp.pte),ydata(disp.pte)],zdata(disp.pte),setting.fit_str, 'Normalize', 'on');
                     data.fit_Aeff(ww,hh,pp,mm).exist = true;
                     data.fit_Aeff(ww,hh,pp,mm).fit = fit1;
                     data.fit_Aeff(ww,hh,pp,mm).gof = gof1;
@@ -230,59 +230,32 @@ tic
 
 % the pump wlen is static 1.55 [um], so i can pre-compute its values out of
 % the for loops
-%{
-for tt=1:pm.n_sample_t
-    for oo=1:par.ord_max
-        for TE=1:2
-            for ww=1:par.n_wg_wid
-                for hh=1:par.n_wg_hgt
-                    if (data.fit_neff(1,1,TE,pp).exist && data.fit_neff(1,1,TE,ss).exist && data.fit_neff(1,1,TE,ii).exist)
-                        pm.pump_k(tt,oo,TE,ww,hh) = 2*pi/pm.pump_w*2*pi*data.fit_neff( ww, hh, TE, oo).fit( pm.pump_w, vec.sample_temp(tt) );
-                    end 
-                end
-            end
[…]

### 2015-08-30 gitcode/phase-matching/phasematching_v3.m
not that interesting

@@ -103,6 +103,7 @@ disp.lp = 2.1;
 %setting.fit_str = 'loess';
 setting.fit_str = 'poly52';
 %setting.fit_str = 'poly25';
+%setting.fit_str = 'cubicinterp';
 
 [xdata, ydata, ~] = prepareSurfaceData( vec.wlen, vec.temp, ones(par.n_wlen,par.n_temp) );
 
@@ -271,50 +272,55 @@ clear ww hh oo ll ff tt kp ks ki ans
 % it plots only surfaces that cross the plane z=0
 xdata = vec.sample_wlen;
 ydata = vec.sample_temp;
+[xData, yData, ~] = prepareSurfaceData( xdata, ydata, results.data(:,:,1) );
 
 f(pm.n_results) = figure(pm.n_results);
 close(f(pm.n_results));
+
+%setting.fit_str = 'linearinterp'; % Linear interpolation          
+%setting.fit_str = 'nearestinterp'; % Nearest neighbor interpolation         
+setting.fit_str = 'cubicinterp'; % Cubic spline interpolation
+%setting.fit_str = 'biharmonicinterp'; % Biharmonic (MATLAB griddata) interpolation % ALSO NOT GOOD
+%setting.fit_str = 'thinplateinterp'; % Thin-plate spline interpolation % very computation needy DO NOT USE
+
+%setting.fit_str = 'poly55';    % doesn't work DO NOT USE
 
 for rr=1:pm.n_results;
     fprintf('\n%d\n',rr);
     if ~isnan(results.data(:,:,rr))    
         zdata = results.data(:,:,rr);
-        %if min(zdata(:))*max(zdata(:))<=0
-            f(rr) = figure(rr);
-            str_title = strcat('Solution %d: combination (p,s,i) %d %d %d',rr, pm.comb(rr,2), pm.comb(rr,4), pm.comb(rr,6));
-            title(str_title);
-            set(f(rr), 'Position', [100, 100, 960, 480]);
-            [xData, yData, zData] = prepareSurfaceData( xdata, ydata, zdata );
-            % zData = [m] --> 2pi*100./zData = [cm]
-            % fit & plot Delta_k
-            subplot(1,2,1)
-            title('delta_k');
-            %[fitresult, ~] = fit( [xData, yData], zData, 'loess', 'Normalize', 'on' );
-            [fitresult, ~] = fit( [xData, yData], zData./100, 'cubicinterp', 'Normalize', 'on' ); % zData in [1/cm]
[…]

### 2015-08-30 latex/article.tex
not that interesting

@@
 \section{Linear optics}
+
+A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field, $\mathrm{P} = \varepsilon_0 \chi \mathrm{E}$, where $\varepsilon_0$ is the permittivity of free space and $\chi$ is the susceptibility of the medium.
+
 In linear optics the technology for trasmitting a light wave by confining it in a finite space is the guided-wave optics.
@@
 \section{Non-linear optics}
-A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field, $\mathrm{P} = \varepsilon_0 \chi \mathrm{E}$, where $\varepsilon_0$ is the permittivity of free space and $\chi$ is the susceptibility of the medium.
 A nonlinear dielectric medium is characterized by a nonlinear relation between P and E, such as

### 2015-08-30 latex/article.tex
added asymmetric study

@@
-\documentclass[12pt,a4paper]{article}
+\documentclass[12pt,a4paper,twocolumn,twoside]{article}
 \usepackage[utf8]{inputenc}
@@
 
-\newpage
+\cleardoublepage 
+\tableofcontents
+
+\cleardoublepage 
 \section{Introduction}
 \subsection{Motivation}
-\subsection{Degenerate Four-Wave Mixing}
+\subsection{Partially degenerate Four-Wave Mixing}
 Four-Wave Mixing (FWM) is a nonlinear optical effect
 
+****
 \section{Linear optics}
 
-A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field, $\mathrm{P} = \varepsilon_0 \chi \mathrm{E}$, where $\varepsilon_0$ is the permittivity of free space and $\chi$ is the susceptibility of the medium.
+A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field, $\textbf{P} = \varepsilon_0 \chi \textbf{E}$, where $\varepsilon_0$ is the permittivity of free space and $\chi$ is the susceptibility of the medium.
+
+****
 
@@
 Considering an ideal dielectric waveguide (no absorption) and the total field distribution as sum of transverse electromagnetic (TEM) plane waves is possible to study the propagation of the wave along the waveguide with an electromagnetic analysis.
-Furthermore it can be shown that not all field distribution are transmitted through the waveguide without energy loss.
+Furthermore it can be shown that not all field distribution are transmitted through the waveguide without energy loss \textbf{(?)}.
 
@@
 A nonlinear dielectric medium is characterized by a nonlinear relation between P and E, such as
-$$\mathrm{P} = \varepsilon_0\chi \mathrm{E} + 2\mathrm{d}\mathrm{E}^2 + 4\chi^{(3)}\mathrm{E}^3 + \cdots$$
+$$\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) $$
 In everyday condition linear effects are much larger than nonlinear ones.
-The relation between $\mathrm{P}$ and $\mathrm{E}$ becomes nonlinear when $\mathrm{E}$ has a value comparable to interatomic electric fields, which are typically $\sim 10^5-10^8$ \si{\V\per\m}
+The relation between $\mathrm{P}$ and $\mathrm{E}$ becomes nonlinear when $\mathrm{E}$ has a value comparable to interatomic electric fields, which are typically $\sim 10^5-10^8$ \si{\V\per\m}.
+
+For an isotropic medium the second order term is zero (in the dipole approximation) and this is our scenario.
+Thus the dominant nonlinearity is the third order and the material is called a Kerr medium.
 \subsection{Third order effect: Four-Wave Mixing}
+Many processes are result of third order nonlinearities: Third-Harmonic Generation (THG), Optical Kerr Effect, Cross-phase modulation (XPM), Self-phase modulation (SPM) and Four-Wave Mixing (FWM).
 
+Four-Wave Mixing originates from the third order nonlinear response of a material to an electromagnetic field, precisely from the behaviour of bound electrons.
+This parametric process involve nonlinear interaction among four optical waves.
 \section{Simulating and coding ?}
+
+$$\omega_1 + \omega_2 = \omega_3 + \omega_4$$
+$$\omega_1 = \omega_2 = \omega_P$$
+$$\omega_I = 2\omega_P - \omega_S$$
+$$\Omega_S = \omega_1 + \omega_3 = \omega_4 - \omega_1$$
+where we assume $\omega_3 < \omega_4$.
+$$\Omega_S = |\omega_P - \omega_I| = |\omega_S - \omega_P|$$
+
+$$\Delta k = \beta_3 + \beta_4 - \beta_1 - \beta_2$$
+$$\Delta k = \beta_3 + \beta_4 - 2\beta_1$$
+
+$$L_{coh} = \frac{2\pi}{|\Delta k|}$$
 

### 2015-08-30 gitcode/phase-matching/phasematching_v3.m

@@ -242,8 +242,7 @@ for ww=1:par.n_wg_wid                                   % number of widths ?
             fprintf('mode orders:\tpump %d,\tsignal %d,\tidler %d (sol %d/%d)\n', pm.comb(oo,2), pm.comb(oo,4), pm.comb(oo,6), oo, pm.n_results );
             for tt=1:pm.n_sample_t
                 %kp = 2*pi*feval( data.fit_neff( ww, hh, pm.comb(oo,1), pm.comb(oo,2)).fit, pm.pump_w, vec.sample_temp(tt))/pm.pump_w;
-                %kp = 2*pi*data.fit_neff( ww, hh, pm.comb(oo,1), pm.comb(oo,2)).fit(pm.pump_w, vec.sample_temp(tt))/pm.pump_w;
-                kp = pm.pump_k(tt,pm.comb(oo,2),pm.comb(oo,1),ww,hh);
+                kp = 2*pi*data.fit_neff( ww, hh, pm.comb(oo,1), pm.comb(oo,2)).fit(pm.pump_w, vec.sample_temp(tt))/pm.pump_w;
 
                 for ll=1:pm.n_sample_wl
                     pm.signal_w = vec.sample_wlen(ll);

### 2015-09-15 gitcode/phase-matching/phasematching_v3.m
stuck because of bandwidth

@@ -214,6 +214,8 @@ fprintf('\nCreating structure of data for results...');
 results.orders  = zeros(2, 3, pm.n_results).*NaN;
 
 results.data    = zeros(pm.n_sample_wl, pm.n_sample_t, pm.n_results, par.n_wg_wid, par.n_wg_hgt).*NaN;
+results.maxima  = zeros(pm.n_sample_wl, pm.n_sample_t, pm.n_results, par.n_wg_wid, par.n_wg_hgt).*NaN;
+results.bw      = zeros(pm.n_sample_wl, pm.n_sample_t, pm.n_results, par.n_wg_wid, par.n_wg_hgt).*NaN;
 
 fprintf('\b\b\b:\tstructure created.\n');
 clear jj kk oo
@@ -236,7 +238,7 @@ for ww=1:par.n_wg_wid                                   % number of widths
             
             results.orders(:,:,oo) = pm.comb(:,:,oo);
 
-            fprintf('mode orders:\tpump %d,\tsignal %d,\tidler %d (sol %d/%d)\n', pm.comb(2,1,oo), pm.comb(2,2,oo), pm.comb(2,3,oo), oo, pm.n_results );
+            fprintf('mode orders:\tpump %d, signal %d, idler %d\t\t(sol %d/%d)\n', pm.comb(2,1,oo), pm.comb(2,2,oo), pm.comb(2,3,oo), oo, pm.n_results );
             
             kp = 2*pi*data.fit_neff( ww, hh, pm.comb(1,1,oo), pm.comb(2,1,oo)).fit(pgrid, ygrid)./pgrid;
             ks = 2*pi*data.fit_neff( ww, hh, pm.comb(1,2,oo), pm.comb(2,2,oo)).fit(sgrid, ygrid)./sgrid;
@@ -254,18 +256,13 @@ clear ww hh oo kp ks ki pgrid sgrid igrid ygrid ans
 
 %% 3D surface plot w/ temperature
 % it plots only surfaces that cross the plane z=0
+fprintf('\nGenerating plots...\n');
+tic
+
 [xGrid, yGrid]  = meshgrid(vec.sample_temp, vec.sample_wlen);
 
 f(pm.n_results) = figure(pm.n_results);
 close(f(pm.n_results));
-
-% interpolation is not used anymore
-%{
-xdata = vec.sample_wlen;
-ydata = vec.sample_temp;
[…]

### 2015-09-15 latex/article.tex
introduction

@@
 \subsection{Motivation}
+In my scholastic career I approached the study of optics in an elective course of my third year of undergraduate academic degree.
+I became very interested in the subject, in particular because of the potential developement of photonics for communication and computing.
+I discussed different topics with the professors and some researchers.
+One of them suggested me a few interesting topics in guided-wave optics which could be studied as a undergraduate thesis.
+
+I choose to study the the temperature behaviour of silicon waveguides.
+The reason of the choice is that there are always discrepancies between the design of silicon objects and their actual production by the factory.
+The aim of the study is to exploit this behaviour to correct possible production defects of the materials.
+
+The study is focused on a silicon-based waveguide with rectangular section with a silicon ($\mathrm{Si}$) core and a silica ($\mathrm{Si0}_2$) cladding.
+Its purpose is to generate light through a partial degenerate Four-Wave Mixing phenomenon
+
 \subsection{Partially degenerate Four-Wave Mixing}
-Four-Wave Mixing (FWM) is a nonlinear optical effect
+Four-Wave Mixing (FWM) is a nonlinear optical effect due to the susceptibility of silicon.
+Silicon is an isotropic material and therefore second order susceptibility $\chi^{(2)}$ (almost) vanishes.
+Third order susceptibility $\chi^{(3)}$, on the other hand, is not zero and is responsible among the other effects for FWM, which is indeed a third order phenomenon.
 
-****
+In general FWM implies the mix of four waves of different frequency.
+Partial degenerate FWM, instead, is a specific case in which two waves have the same frequency.
+Therfore it is about two waves (pump and signal) which generate a third wave (idler).
+
 \section{Linear optics}
@@
 
+****
+
+photos?
 \section{Non-linear optics}

### 2015-09-16 latex/article.tex
sections improved

@@
 
+\pagenumbering{roman}	% numeration in roman numbers
 \begin{document}
+
 \includepdf[pages={1}]{intestazione.pdf} % \input{intestazione.tex}
@@
 \cleardoublepage 
+\setcounter{page}{3}
 \tableofcontents
@@
 \cleardoublepage
+\pagenumbering{arabic}
+
 \section{Introduction}
@@
 
-I choose to study the the temperature behaviour of silicon waveguides.
+I chose to study the the temperature behaviour of silicon waveguides.
 The reason of the choice is that there are always discrepancies between the design of silicon objects and their actual production by the factory.
@@
 Partial degenerate FWM, instead, is a specific case in which two waves have the same frequency.
-Therfore it is about two waves (pump and signal) which generate a third wave (idler).
+Therefore it is about two waves (pump and signal) which generate a third wave (idler).
 
@@
 
+\vspace{18pt}
 ****
+\vspace{12pt}
 
@@
 
+\vspace{18pt}
+****		\textit{effective index}
+\vspace{12pt}
+
 \subsection{Rectangular dielectric waveguides}
-In a rectangular dielectric waveguide the classification of modes need two indexes because we have two degrees of freedom.
+In general, in a rectangular dielectric waveguide the classification of modes need two indexes because we have two degrees of freedom.
+For our purpose, due to the thin geometry of the core, modes with the higher effective index are fundamental modes in the height axis.
+Only one significant index is then left to describe the order of modes.
 
+\vspace{18pt}
 ****
@@
 Thus the dominant nonlinearity is the third order and the material is called a Kerr medium.
+
 \subsection{Third order effect: Four-Wave Mixing}
@@
 This parametric process involve nonlinear interaction among four optical waves.
-\section{Simulating and coding ?}
+
+\section{Simulating and coding}
+
+To understand the behaviour of the waveguide, it is necessary to first know how waves of different frequency are transmitted through the waveguide.
+We chose to simulate the modes with temperature and frequency as a parameters.
+
+Our aim was to develop a model to work with an infrared laser pump with $\lambda_{p} = \SI{1.55}{\um}$.
+We narrowed our simulations to a frequency gap centered in $\omega_p = 2\pi \nu_p = 2\pi c / \lambda_{p}$.
+The gap chosen was precisely $[\SI{1.45}{\um} ,\, \SI{1.65}{\um}]$ or the equivalent $[\SI{182}{\THz} ,\, \SI{207}{\THz}]$.
+
+\vspace{18pt}
+****
+\vspace{12pt}
+
+Our data output was therefore the field distribution and effective index for a number of modes for each parametric configuration.
+
+The next step was to classify these data depending on the order and type (TE or TM) of the modes.
+We achieved this by analyzing the maxima of the field distributions.
+We obtained then a well organized data matrix filled with the value of effective index for each combination of parameters.
+
+\subsection{Data processing}
+Then we fit effective index data for each parametric configuration with a polinomial function of frequency $\omega = 2\pi \nu$ and temperature $T$:
+$$n_{eff} = f_{mt,\,mo} \left( \omega, T \right)$$
+where $mt$ and $mo$ means respectively \textit{mode type} (TE or TM) and \textit{mode order} (0, 1, 2, ...)
+
+\vspace{18pt}
+************************************
 
@@
 \subsection{Heater configurations}
+In order to achieve a greater effect from the different temperature, we tried to move the heater from the center of the core to the side.
+This operation was intended to increase the difference of behaviour between low and high orders.
 \subsection{Different geometries}
 
-\newpage
+\section{Conclusion}
+
+\cleardoublepage
 \begin{thebibliography}{9}

### 2015-09-16 gitcode/phase-matching/phasematching_v3.m

@@ -1,6 +1,6 @@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                                                                         %
-%   This file will search for phase matching condition                    %
+%   This script will search for phase matching condition                    %
 %                                                                         %
 %                                                         D. Bazzanella   %
 %                                                                         %
@@ -11,7 +11,7 @@
 ans1 = 0;
 while ( ans1 == 0 )
     % Construct a questdlg with three options
-    choice = questdlg('Import a file or to exit the program?', 'Import File', 	'Import File', 'Exit program', 'Go on', ...
+    choice = questdlg('Import a file or to exit the program?', 'Import File', 'Import File', 'Exit program', 'Go on', ...
         'Import File');
     % Handle response
     switch choice
@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 201;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 4001;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -215,7 +215,14 @@ results.orders  = zeros(2, 3, pm.n_results).*NaN;
 
 results.data    = zeros(pm.n_sample_wl, pm.n_sample_t, pm.n_results, par.n_wg_wid, par.n_wg_hgt).*NaN;
 results.maxima  = zeros(pm.n_sample_wl, pm.n_sample_t, pm.n_results, par.n_wg_wid, par.n_wg_hgt).*NaN;
-results.bw      = zeros(pm.n_sample_wl, pm.n_sample_t, pm.n_results, par.n_wg_wid, par.n_wg_hgt).*NaN;
+results.bwid    = zeros(pm.n_sample_wl, pm.n_sample_t, pm.n_results, par.n_wg_wid, par.n_wg_hgt).*NaN;
+
+results.max.q 	= zeros(pm.n_results,10).*NaN;
+results.max.m 	= zeros(pm.n_results,10).*NaN;
+results.bw.q 	= zeros(pm.n_results,10).*NaN;
+results.bw.m 	= zeros(pm.n_results,10).*NaN;
+
[…]

### 2015-09-16 latex/article.tex
sections improved

@@
 I discussed different topics with the professors and some researchers.
-One of them suggested me a few interesting topics in guided-wave optics which could be studied as a undergraduate thesis.
+One of the researcher, who would later become my advisor, suggested me a few interesting topics in guided-wave optics which could be studied as a undergraduate thesis.
 
-I chose to study the the temperature behaviour of silicon waveguides.
+I chose to study the temperature behaviour of silicon waveguides.
 The reason of the choice is that there are always discrepancies between the design of silicon objects and their actual production by the factory.
-The aim of the study is to exploit this behaviour to correct possible production defects of the materials.
+The aim of the study is to exploit behaviour of silicon to correct these possible production defects of the materials.
 
-The study is focused on a silicon-based waveguide with rectangular section with a silicon ($\mathrm{Si}$) core and a silica ($\mathrm{Si0}_2$) cladding.
-Its purpose is to generate light through a partial degenerate Four-Wave Mixing phenomenon
+The study is focused on a silicon-based waveguide with a silicon ($\mathrm{Si}$) core of rectangular section and a silica ($\mathrm{Si0}_2$) cladding.
+The purpose of the waveguide is to generate light through a partial degenerate Four-Wave Mixing phenomenon.
 
@@
 Silicon is an isotropic material and therefore second order susceptibility $\chi^{(2)}$ (almost) vanishes.
-Third order susceptibility $\chi^{(3)}$, on the other hand, is not zero and is responsible among the other effects for FWM, which is indeed a third order phenomenon.
+Third order susceptibility $\chi^{(3)}$, on the other hand, is non-zero and is responsible among the other effects for FWM, which is indeed a third order phenomenon.
 
 In general FWM implies the mix of four waves of different frequency.
-Partial degenerate FWM, instead, is a specific case in which two waves have the same frequency.
-Therefore it is about two waves (pump and signal) which generate a third wave (idler).
+Partial degenerate FWM, instead, is a specific case in which two waves have the same frequency and are considered as one (pump).
+Therefore it is about the pump wave and a second weaker one (signal) which generate a third wave (idler) of frequency different from that of the former two.
 
@@
 \subsection{Silicon waveguides}
-Silicon waveguides are dielectric waveguides and make use of the interface between two media with different refractive index.
+In a ray-optics picture, silicon waveguides are dielectric waveguides and make use of the interface between two media with different refractive index.
 Precisely they exploit the phenomenon of total internal reflection: if a propagating wave reaches a boundary between two mediums, one with higher refractive index ($n_H$) and another with lower refractive index ($n_L$), with an angle of incidence greater than the \textit{critical angle}, then the wave is completely reflected in the first medium.
@@
 \vspace{12pt}
+
+A very important parameter of modes is the \textit{propagation constant} $\beta$, defined as the component of the wavevector $k$ in the waveguide axis:
+$$ \beta \equiv k_z$$
+Higher-order modes travel with smaller propagation constants.
+For a 1D slab waveguide $\beta$ has a simple relation with the bounce angles $\theta_m$, which are quantized between $0$ and $\bar{\theta}_C = \pi - \theta_C$:
+$$\beta_m = n_H k_0 \cos \theta_m$$
+
+From the propagation constant, we can also define the refractive index relative to the propagation mode, called \textit{effective index}:
+$$\beta_m = n_H k_0 \cos \theta_m = k_0 n_{eff}$$
+$$ \Longrightarrow n_{eff} \equiv n_H \cos \theta_m$$
+Its value is between the higher index of the core and lower one of the cladding.
 
@@
 
+\vspace{18pt}
+****		è necessario verificare conservazione di energia e momento
+\vspace{12pt}
+
 \section{Simulating and coding}
@@
 \subsection{Data processing}
-Then we fit effective index data for each parametric configuration with a polinomial function of frequency $\omega = 2\pi \nu$ and temperature $T$:
+Starting from raw data consisting of the effective index for each parametric configuration, we fitted them with a polinomial function of frequency $\omega = 2\pi \nu$ and temperature $T$, obtaining:
 $$n_{eff} = f_{mt,\,mo} \left( \omega, T \right)$$
-where $mt$ and $mo$ means respectively \textit{mode type} (TE or TM) and \textit{mode order} (0, 1, 2, ...)
+where $mt$ and $mo$ means respectively \textit{mode type} (TE or TM) and \textit{mode order} (1, 2, 3, ...)
 

### 2015-09-16 latex/article.tex
two figures

@@
-\documentclass[12pt,a4paper,twocolumn,twoside]{article}
+\documentclass[12pt,a4paper,twoside]{article}
+%\documentclass[12pt,a4paper,twocolumn,twoside]{article}
 \usepackage[utf8]{inputenc}
@@
 
-\section{Linear optics}
+\section{Electromagnetic waves in dielectric media}
 
-A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field, $\textbf{P} = \varepsilon_0 \chi \textbf{E}$, where $\varepsilon_0$ is the permittivity of free space and $\chi$ is the susceptibility of the medium.
+**** 	pg 156 saleh or chp 2 agrawal
+\vspace{12pt}
 
-\vspace{18pt}
-****
-\vspace{12pt}
+To understand electromagnetic phenomena the starting point is the well known Maxwell's equations:
+\begin{subequations}
+\begin{align}
+	\nabla \times \textbf{E} &= -\frac{\partial \textbf{B}}{\partial t} \\
+	\nabla \times \textbf{H} &= \textbf{J} + \frac{\partial \textbf{D}}{\partial t} \\
+	\nabla \cdot \textbf{D} &= \rho_{\mathrm{f}} \\
+	\nabla \cdot \textbf{B} &= 0
+\end{align}
+\label{eq_maxwell}
+\end{subequations}
+where \textbf{E} and \textbf{H} are electri and magnetic field vectors and \textbf{D} and \textbf{B} are corresponding electric and magnetic flux densities.
+\textbf{J} is the current density vector and $\rho_{\mathrm{f}}$ is the free charge density.
+In dielectric media, such as silicon, we can also consider $\textbf{J} = 0$ and $\rho_\mathrm{f} = 0$.
+
+\textbf{D} and \textbf{B} are related to the electromagnetic fields through the relations:
+\begin{subequations}
+\begin{align}
+	\textbf{D} &= \varepsilon_0 \textbf{E} + \textbf{P} \\
+	\textbf{H} &= \mu_0 \textbf{H} + \textbf{M}	
+\end{align}
+\end{subequations}
+where $\varepsilon_0$ is the vacuum permittivity, $\mu_0$ is the vacuum permeability, and \textbf{P} and \textbf{M} are the induced electric and magnetic polarizations repectively.
+For a nonmagnetic medium, as in our case, $\textbf{M} = 0$.
+
+A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field:
+\begin{equation}
+\textbf{P} = \varepsilon_0 \chi \textbf{E}
+\end{equation}
+where $\chi$ is the susceptibility of the medium and $\varepsilon_r \equiv 1+\chi$ is the relative dielectric constant.
+
+Taking the curl of eq (\ref{eq_maxwell}a) and substituting in it eq (\ref{eq_maxwell}c) it leads to the Helmholtz equation:
+\begin{equation}
+\nabla^2 \textbf{E} - \frac{1}{c^2}\frac{\partial^2 \textbf{E}}{\partial t^2} = \mu_0\frac{\partial^2 \textbf{P}}{\partial t^2}
+\label{eq_helm_P}
+\end{equation}
+where $c = 1/\sqrt{\mu_0 \varepsilon_0}$ is the speed of light in vacuum.
+
+Defining the refractive index $n \equiv \sqrt{\varepsilon_r}$ of the material the previous equation (\ref{eq_helm_P})
+\begin{equation}
+\nabla^2 \textbf{E} - \frac{n^2}{c^2}\frac{\partial^2 \textbf{E}}{\partial t^2} = 0
+\end{equation}
+Moreover, $n$ represent the ratio between the speed of light in vacuum and in the material $n = c/v$.
 
@@
 The instruments employed for achieving such purpose are called waveguides.
+
 \subsection{Silicon waveguides}
@@
 
+\vspace{18pt}
+**** ripresa delle eq di maxwell?
+\vspace{12pt}
+
 Considering an ideal dielectric waveguide (no absorption) and the total field distribution as sum of transverse electromagnetic (TEM) plane waves is possible to study the propagation of the wave along the waveguide with an electromagnetic analysis.
@@
 % Modes are fields that maintain the same transverse distribution and polarization at all locations along the waveguide axis.
-Those field distributions, which maintain the same transverse distribution and polarization at all locations along the waveguide axis, are called modes.
+Those field distributions which maintain the same transverse distribution and polarization at all locations along the waveguide axis are called modes.
 These modes can be categorized in two main groups, depending on the polarization of the wave: transverse electric (TE) modes and transverse magnetic (TM) modes, which have respectively the electric and magnetic field transverse to the waveguide axis.
+
 Both TE and TM modes can be again classified by their order, that is proportional to the number of maxima of the modulus of the electric and magnetic fields in the core section.
+The first order has only one maximum at the center of the core, the second order has two maxima placed simmetrically from the center and so on.
+
+Moreover it is noteworthy that the field distributions of odd orders are even functions and those of even order are odd functions.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.75\textwidth]{1D_fields.png}
+	\label{fig_1dmodes}
+	\caption{graphical rapresentation of field distribution of 1D modes}
+\end{figure}
 
@@
 
-A very important parameter of modes is the \textit{propagation constant} $\beta$, defined as the component of the wavevector $k$ in the waveguide axis:
-$$ \beta \equiv k_z$$
+A very important parameter of each mode is its \textit{propagation constant} $\beta$, defined as the component of the wavevector $k$ in the waveguide axis:
+\begin{equation}
+\beta \equiv k_z
+\end{equation}
+
 Higher-order modes travel with smaller propagation constants.
@@
 From the propagation constant, we can also define the refractive index relative to the propagation mode, called \textit{effective index}:
-$$\beta_m = n_H k_0 \cos \theta_m = k_0 n_{eff}$$
-$$ \Longrightarrow n_{eff} \equiv n_H \cos \theta_m$$
+\begin{equation}
+\beta = k_0 n_{eff} \quad \Rightarrow \quad n_{eff} \equiv \frac{\beta}{k_0}
+\end{equation}
+
 Its value is between the higher index of the core and lower one of the cladding.
+Again, for the 1D slab waveguide case, the effective index can be rewritten as in the following formula:
+$$ n_{eff} \equiv n_H \cos \theta_m$$
 
@@
 
-\vspace{18pt}
-****
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.5\textwidth]{2Dmodes.png}
+	\label{fig_2dmodes}
+	\caption{graphical rapresentation of field distribution of 2D modes}
+\end{figure}
 
-photos?
 \section{Non-linear optics}
 A nonlinear dielectric medium is characterized by a nonlinear relation between P and E, such as
-$$\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) $$
+\begin{equation}
+\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right)
+\end{equation}
+which originates from the behaviour of bound electrons.
+
 In everyday condition linear effects are much larger than nonlinear ones.
@@
 \subsection{Third order effect: Four-Wave Mixing}
-Many processes are result of third order nonlinearities: Third-Harmonic Generation (THG), Optical Kerr Effect, Cross-phase modulation (XPM), Self-phase modulation (SPM) and Four-Wave Mixing (FWM).
+Many processes are result of third order nonlinearities: Third-Harmonic Generation (THG), Kerr Effect, Cross-phase modulation (XPM), Self-phase modulation (SPM) and Four-Wave Mixing (FWM).
 
-Four-Wave Mixing originates from the third order nonlinear response of a material to an electromagnetic field, precisely from the behaviour of bound electrons.
-This parametric process involve nonlinear interaction among four optical waves.
+The parametric process of Four-Wave Mixing originates from the third order nonlinear response of a material to an electromagnetic field and involves interaction among four optical waves.
 
@@
 \vspace{12pt}
+
+In order to be efficient, the parametric process needs to verify both the conservation of energy and momentum.
+\begin{equation}
+\omega_1 + \omega_2 = \omega_3 + \omega_4
+\end{equation}
+\begin{equation}
+\beta_1 + \beta_2 = \beta_3 + \beta_4
+\end{equation}
+%\Delta k = \beta_3 + \beta_4 - \beta_1 - \beta_2
 
@@
 The gap chosen was precisely $[\SI{1.45}{\um} ,\, \SI{1.65}{\um}]$ or the equivalent $[\SI{182}{\THz} ,\, \SI{207}{\THz}]$.
+
+The reason for this choice is that silicon is transparent at these wavelenght and also for the availability of laser that emit at the specific wavelenght.
 
@@
 
-$$\omega_1 + \omega_2 = \omega_3 + \omega_4$$
+\subsubsection*{Order combination}
+
+Due to the intrinsic symmetry of the problem (and thus of the integrals) not all combinations of orders can produce FWM.
+Only those in which the sum of the orders is an even number are interesting.
+To narrow the possible sets, we chose to permit only full TE or full TM  combinations.
+
+We eventually obtained a list of combinations, for each of which we verified the conservation of energy and momentum.
+
 $$\omega_1 = \omega_2 = \omega_P$$
@@
 
-$$\Delta k = \beta_3 + \beta_4 - \beta_1 - \beta_2$$
 $$\Delta k = \beta_3 + \beta_4 - 2\beta_1$$
@@
 \section{Prototyping}
+
 \subsection{Heater configurations}
-In order to achieve a greater effect from the different temperature, we tried to move the heater from the center of the core to the side.
+In order to achieve a greater effect from the different temperature, we tried to move the heater from over the center of the core to the side.
 This operation was intended to increase the difference of behaviour between low and high orders.

### 2015-09-16 gitcode/phase-matching/phasematching_v3.m

@@ -386,6 +386,8 @@ for rr=1:pm.n_results;
             results.maxima( 1:size(y,1), 1:size(y,2), rr, 1, 1) = y;
             results.bwid( 1:size(y2,1), 1:size(y2,2), rr, 1, 1) = y2;
             
+            saveas(f, strcat('sol',num2str(rr),'_',num2str(pm.comb(2,:,rr))), 'pdf');
+            
         end 
     end
 end
@@ -393,15 +395,69 @@ results.indexes = find(results.indexes == 1);
 results.n_final = length(results.indexes);
 toc
 %%
-clear ans xGrid yGrid zdata zData rr jj tt y y2 maxL locs bw fitresult f name subplot1 subplot2
+clear ans xGrid yGrid zdata zData rr jj tt y y2 maxL locs bw fitresult f name subplot1 subplot2 top
 
 %% 2D plots data vs orders
 
-f = figure;
-plot( 1e11*results.max.m(results.indexes,1), 'o' );
+f = figure('name', 'peak position at ambient temperature');
+title('peak position at ambient temperature [um]');
+hold on;
+plot( 1e6*results.max.q(results.indexes,1:end), 'o' );
+saveas(f, 'ppaat', 'pdf');
 
-f = figure;
-plot( 1e11*results.bw.m(results.indexes,1), 'o' );
+f = figure('name', 'peak position: m');
+title('peak position change [nm/100°C]');
+hold on;
+plot( 1e11*results.max.m(results.indexes,1:end), 'o' );
+saveas(f, 'ppc', 'pdf');
+
+f = figure('name', 'bandwidth');
+title('bandwidth at ambient temperature [nm]');
+hold on;
+plot( 1e9*results.bw.q(results.indexes,1:end), 'o' );
+saveas(f, 'baat', 'pdf');
+
+f = figure('name', 'bandwidth: m');
+title('bandwidth change [nm/100°C]');
+hold on;
+plot( 1e11*results.bw.m(results.indexes,1:end), 'o' );
+saveas(1, 'bc', 'pdf');
+
+%% 2D plots data vs orders, w/out degenerate states
+
+results.indexes2 = [];
+for jj=1:results.n_final
+    if ~(results.max.q(results.indexes(jj),1) >= 1.549e-6 && results.max.q(results.indexes(jj),1) <= 1.551e-6)
+        results.indexes2 = [results.indexes2; results.indexes(jj)];
+    end
+end
+clear jj
+
[…]

### 2015-09-16 latex/article.tex
added ampliture formulas

@@
 
+The nonlinear component of the induced electric polarization vector, considering significant only the third-order term, is
+$$ \textbf{P}_{NL} = \varepsilon_0 \chi^{(3)} \vdots \textbf{E}^3 $$
+
+\vspace{18pt}
+****		è necessario verificare conservazione di energia e momento
+\vspace{12pt}
+\begin{equation}
+	\textbf{E} = \frac{1}{2}\hat{x} \sum_{j=1}^4 E_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
+	\label{eq_E}
+\end{equation}
+(``c.c." means complex conjugate)
+
+\begin{equation}
+	\textbf{P} = \frac{1}{2}\hat{x} \sum_{j=1}^4 P_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
+	\label{eq_P}
+\end{equation}
+considering $E_j(\textbf{r}) = F_j(x,y)A_j(z)$ where $F_j$ is the spatial distribution of the mode
+
+\begin{subequations}
+\begin{align}
+	\frac{dA_1}{dz} &= \frac{\mathrm{i}n_L\omega_1}{c}\left[ \left( f_{11} |A_1|^2 + 2 \sum_{k\neq1} f_{1k}|A_k|^2\right)A_1 + 2f_{1234}A_2^*A_3A_4\mathrm{e}^{\mathrm{i}\Delta k_z} \right] \\
+	\frac{dA_2}{dz} &= \frac{\mathrm{i}n_L\omega_2}{c}\left[ \left( f_{22} |A_2|^2 + 2 \sum_{k\neq2} f_{2k}|A_k|^2\right)A_2 + 2f_{2134}A_1^*A_3A_4\mathrm{e}^{\mathrm{i}\Delta k_z} \right] \\
+	\frac{dA_3}{dz} &= \frac{\mathrm{i}n_L\omega_3}{c}\left[ \left( f_{33} |A_3|^2 + 2 \sum_{k\neq3} f_{3k}|A_k|^2\right)A_3 + 2f_{3412}A_1A_2A_4^*\mathrm{e}^{-\mathrm{i}\Delta k_z} \right] \\
+	\frac{dA_4}{dz} &= \frac{\mathrm{i}n_L\omega_4}{c}\left[ \left( f_{44} |A_4|^2 + 2 \sum_{k\neq4} f_{4k}|A_k|^2\right)A_4 + 2f_{4321}A_1A_2A_3^*\mathrm{e}^{-\mathrm{i}\Delta k_z} \right]
+\end{align}
+\label{eq_coupled_amplitude}
+\end{subequations}
+
+where
+
+\begin{equation}
+	f_{ij} = \frac{\langle |F_i|^2 |F_j|^2 \rangle}{\sqrt{\langle |F_i|^2 \rangle\langle |F_j|^2 \rangle}}
+\end{equation}
+and
+\begin{equation}
+	f_{ijkl} = \frac{\langle F_i^* F_j^* F_k F_l \rangle}{\sqrt{\langle |F_i|^2 \rangle\langle |F_j|^2 \rangle\langle |F_k|^2 \rangle\langle |F_l|^2 \rangle}}
+\end{equation}
+
 \vspace{18pt}

### 2015-09-17 latex/article.tex
formulae

@@
 
-**** 	pg 156 saleh or chp 2 agrawal
-\vspace{12pt}
-
+%pg 156 saleh or chp 2 agrawal
 To understand electromagnetic phenomena the starting point is the well known Maxwell's equations:
@@
 \end{subequations}
-where \textbf{E} and \textbf{H} are electri and magnetic field vectors and \textbf{D} and \textbf{B} are corresponding electric and magnetic flux densities.
+where \textbf{E} and \textbf{H} are electric and magnetic field vectors and \textbf{D} and \textbf{B} are corresponding electric and magnetic flux densities.
 \textbf{J} is the current density vector and $\rho_{\mathrm{f}}$ is the free charge density.
@@
 
+\subsubsection*{Solution in linear dielectric medium}
 A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field:
@@
 	\nabla^2 \textbf{E} - \frac{n^2}{c^2}\frac{\partial^2 \textbf{E}}{\partial t^2} = 0
+	\label{eq_helm_lin}
 \end{equation}
-Moreover, $n$ represent the ratio between the speed of light in vacuum and in the material $n = c/v$.
+Moreover, $n$ represent the ratio between the speed of light in vacuum and in the material $n = c/v$ and it depends on the frequency of the EM wave.
 
+The general solution of eq (\ref{eq_helm_P}) is a transverse electromagnetic (TEM) wave, whose electric and magnetic fields are perpendicular to the propagation direction.
+Without losing generality, we could assume $\hat{z}$ as the propagation direction and electric field of the form:
+\begin{equation}
+	\textbf{E} = \frac{1}{2}\hat{x}\,E\,\mathrm{exp}[\mathrm{i}(kz-\omega t)] + c.c.
+	\label{eq_wave}
+\end{equation}
+with $E$ amplitude of the electric field, $k = 2\pi/\lambda$ the wavevector and $\omega = 2\pi f$ the angular frequency.
+$\lambda$ and $f$ are relatively the wavelenght and the frequency of the electromagnetic wave.
+The magnetic field has a similar equation.
+
+\subsection{Silicon waveguides}
 In linear optics the technology for trasmitting a light wave by confining it in a finite space is the guided-wave optics.
@@
 
-\subsection{Silicon waveguides}
 In a ray-optics picture, silicon waveguides are dielectric waveguides and make use of the interface between two media with different refractive index.
@@
 **** ripresa delle eq di maxwell?
+
+**** soluzione generale: onde TE, TM
 \vspace{12pt}
 
-Considering an ideal dielectric waveguide (no absorption) and the total field distribution as sum of transverse electromagnetic (TEM) plane waves is possible to study the propagation of the wave along the waveguide with an electromagnetic analysis.
-Furthermore it can be shown that not all field distribution are transmitted through the waveguide without energy loss \textbf{(?)}.
+Considering an ideal dielectric waveguide (no absorption) with the purpose of transmitting EM waves in the $\hat{z}$ direction, the total field distribution is a sum of continous TEM plane waves.
+Defining the amplitude of the fields as $E(\textbf{r},t) = F(x,y)A(z,t)$ is possible to study the propagation of the wave along the waveguide using the Helmholtz equation (\ref{eq_helm_P}) or (\ref{eq_helm_lin}).
+\vspace{18pt}
+Defining $k=\beta$ in eq (\ref{eq_wave}) leads to the following equations:
+\begin{subequations}
+\begin{align}
+	\frac{\partial^2F(x,y)}{\partial x^2} + \frac{\partial^2F(x,y)}{\partial y^2} + \left[ k_0^2n^2-\beta^2\right]F(x,y) = 0 \\
+	??? \qquad \qquad \frac{\partial^2A(z,t)}{\partial z^2} + \frac{n^2}{c^2}\frac{\partial^2A(z,t)}{\partial t^2} = 0 \\
+	??? \qquad \qquad \frac{\partial^2A(z,t)}{\partial z^2} + k^2n^2\frac{\partial^2A(z,t)}{\partial t^2} = 0
+\end{align}
+\end{subequations}
+\vspace{18pt}
+****
+\vspace{12pt}
 
+Not all field distribution are transmitted through the waveguide without energy loss \textbf{(?)}.
 % Modes are fields that maintain the same transverse distribution and polarization at all locations along the waveguide axis.
@@
 
-\vspace{18pt}
-****		\textit{effective index}
-\vspace{12pt}
+\subsubsection*{Propagation constant and effective index}
 
@@
 \section{Non-linear optics}
-A nonlinear dielectric medium is characterized by a nonlinear relation between P and E, such as
+A nonlinear dielectric medium is characterized by a nonlinear relation between \textbf{P} and \textbf{E}, such as
 \begin{equation}
@@
 In everyday condition linear effects are much larger than nonlinear ones.
-The relation between $\mathrm{P}$ and $\mathrm{E}$ becomes nonlinear when $\mathrm{E}$ has a value comparable to interatomic electric fields, which are typically $\sim 10^5-10^8$ \si{\V\per\m}.
+The relation between \textbf{P} and \textbf{E} becomes nonlinear when $\mathrm{E}$ has a value comparable to interatomic electric fields, which are typically $\sim 10^5-10^8$ \si{\V\per\m}.
 
@@
 \end{equation}
-(``c.c." means complex conjugate)
-
+and the induced electric polarization:
 \begin{equation}

### 2015-09-17 latex/article.tex
formulae again

@@
 	\textbf{P} = \varepsilon_0 \chi \textbf{E}
+	\label{eq_P_L}
 \end{equation}
@@
 
-Defining the refractive index $n \equiv \sqrt{\varepsilon_r}$ of the material the previous equation (\ref{eq_helm_P})
+Defining the refractive index $n \equiv \sqrt{\varepsilon_r}$ of the material the previous equation (\ref{eq_helm_P}) and using the definition of \textbf{P} as in eq (\ref{eq_P_L})
 \begin{equation}
@@
 
-\vspace{18pt}
-**** ripresa delle eq di maxwell?
+\subsubsection*{Wave equation and modes}
+Considering an ideal dielectric waveguide (no absorption) with the purpose of transmitting EM waves in the $\hat{z}$ direction, the total field distribution is a sum of continous TEM plane waves.
+Defining the amplitude of the fields as $E(\textbf{r},t) = F(x,y)A(z,t)$ and $k=\beta$ and substituting them in eq (\ref{eq_wave}) leads to the following equation:
+\begin{equation*}
+	\textbf{E} = \frac{1}{2}\hat{x}\,F(x,y)A(z,t)\,\mathrm{exp}[\mathrm{i}(\beta z-\omega t)] + c.c.
+\end{equation*}
 
-**** soluzione generale: onde TE, TM
-\vspace{12pt}
+The previous equation represents what is called a ``transverse electric" (TE) wave.
+A second family of solution could be acquired by defining the sum of TEM wave with the magnetic field always perpendicular to the propagation direction.
+This is called a ``transverse magnetic" (TM) wave.
 
-Considering an ideal dielectric waveguide (no absorption) with the purpose of transmitting EM waves in the $\hat{z}$ direction, the total field distribution is a sum of continous TEM plane waves.
-Defining the amplitude of the fields as $E(\textbf{r},t) = F(x,y)A(z,t)$ is possible to study the propagation of the wave along the waveguide using the Helmholtz equation (\ref{eq_helm_P}) or (\ref{eq_helm_lin}).
-\vspace{18pt}
-Defining $k=\beta$ in eq (\ref{eq_wave}) leads to the following equations:
+Is then possible to study the propagation of the wave along the waveguide using the Helmholtz equation (\ref{eq_helm_P}) or (\ref{eq_helm_lin}), obtaining the next equations:
+
 \begin{subequations}
@@
 	\frac{\partial^2F(x,y)}{\partial x^2} + \frac{\partial^2F(x,y)}{\partial y^2} + \left[ k_0^2n^2-\beta^2\right]F(x,y) = 0 \\
-	??? \qquad \qquad \frac{\partial^2A(z,t)}{\partial z^2} + \frac{n^2}{c^2}\frac{\partial^2A(z,t)}{\partial t^2} = 0 \\
-	??? \qquad \qquad \frac{\partial^2A(z,t)}{\partial z^2} + k^2n^2\frac{\partial^2A(z,t)}{\partial t^2} = 0
+	\frac{\partial^2A(z,t)}{\partial z^2} + \frac{n^2}{c^2}\frac{\partial^2A(z,t)}{\partial t^2} = 0
+	\quad ??? \quad or \quad ??? \quad
+	\frac{\partial^2A(z,t)}{\partial z^2} + k^2n^2\frac{\partial^2A(z,t)}{\partial t^2} = 0
 \end{align}
 \end{subequations}
+where $k_0$ is the wavevector in vacuum and $n$ is a function of the position (mainly $x$ and $y$).
+
 \vspace{18pt}
-****
+************************************************************************
+\vspace{12pt}
+
+These equations, once solved, lead to the distribution of the fields in the plane xy and to their modification along the z axis.
+
+\vspace{18pt}
+************************************************************************
 \vspace{12pt}
@@
 In general, in a rectangular dielectric waveguide the classification of modes need two indexes because we have two degrees of freedom.
-For our purpose, due to the thin geometry of the core, modes with the higher effective index are fundamental modes in the height axis.
-Only one significant index is then left to describe the order of modes.
+In Figure (\ref{fig_2dmodes}) is *** a graphical representation of the distribution of the fields in modulus.
 
@@
 
+For our purpose, due to the thin geometry of the core, modes with the higher effective index are fundamental modes in the height axis.
+The first row is of our interest.
+Only one significant index is then left to describe the order of modes.
+
 \section{Non-linear optics}
@@
 	\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right)
+	\label{eq_P_general}
 \end{equation}
@@
 The nonlinear component of the induced electric polarization vector, considering significant only the third-order term, is
-$$ \textbf{P}_{NL} = \varepsilon_0 \chi^{(3)} \vdots \textbf{E}^3 $$
+\begin{equation}
+	\textbf{P}_{NL} = \varepsilon_0 \chi^{(3)} \vdots \textbf{E}^3
+	\label{eq_P_NL}
+\end{equation}
 
 \vspace{18pt}
-****		è necessario verificare conservazione di energia e momento
+************************************************************************
 \vspace{12pt}
+
 \begin{equation}
@@
 \begin{align}
-	\frac{dA_1}{dz} &= \frac{\mathrm{i}n_L\omega_1}{c}\left[ \left( f_{11} |A_1|^2 + 2 \sum_{k\neq1} f_{1k}|A_k|^2\right)A_1 + 2f_{1234}A_2^*A_3A_4\mathrm{e}^{\mathrm{i}\Delta k_z} \right] \\
-	\frac{dA_2}{dz} &= \frac{\mathrm{i}n_L\omega_2}{c}\left[ \left( f_{22} |A_2|^2 + 2 \sum_{k\neq2} f_{2k}|A_k|^2\right)A_2 + 2f_{2134}A_1^*A_3A_4\mathrm{e}^{\mathrm{i}\Delta k_z} \right] \\
+	\frac{dA_1}{dz} &= \frac{\mathrm{i}n_L\omega_1}{c}\left[ \left( f_{11} |A_1|^2 + 2 \sum_{k\neq1} f_{1k}|A_k|^2\right)A_1 + 2f_{1234}A_2^*A_3A_4\mathrm{e}^{+\mathrm{i}\Delta k_z} \right] \\
+	\frac{dA_2}{dz} &= \frac{\mathrm{i}n_L\omega_2}{c}\left[ \left( f_{22} |A_2|^2 + 2 \sum_{k\neq2} f_{2k}|A_k|^2\right)A_2 + 2f_{2134}A_1^*A_3A_4\mathrm{e}^{+\mathrm{i}\Delta k_z} \right] \\
 	\frac{dA_3}{dz} &= \frac{\mathrm{i}n_L\omega_3}{c}\left[ \left( f_{33} |A_3|^2 + 2 \sum_{k\neq3} f_{3k}|A_k|^2\right)A_3 + 2f_{3412}A_1A_2A_4^*\mathrm{e}^{-\mathrm{i}\Delta k_z} \right] \\
@@
 	f_{ijkl} = \frac{\langle F_i^* F_j^* F_k F_l \rangle}{\sqrt{\langle |F_i|^2 \rangle\langle |F_j|^2 \rangle\langle |F_k|^2 \rangle\langle |F_l|^2 \rangle}}
+\end{equation}
+
+\subsubsection*{Approximate solution}
+The previous equations are quite general (they include SPM, XPM in addition to FWM) and require a numerical approach to be solved exactly.
+For this reason, we propose an approximate solution to understand the physical implication.
+The first approximation is called ``undepleted pump" and consist of assuming the pump waves to be much more intense than the other waves.
+As a further simplification, we assume that all overlap integrals are nearly the same
+\begin{equation}
+	f_{ijkl} \approx f_{ij} \approx \frac{1}{A_{eff}}	\qquad \qquad i,j,k,l = 1,2,3,4
+	\label{eq_overlap_approx}
+\end{equation}
+From this definition follows naturally the nonlinear parameter definition
+\begin{equation}
+	\gamma_j = \frac{n_2\omega_j}{cA_{eff}} \approx \gamma
+	\label{eq_gamma_approx}
+\end{equation}
+where $\gamma$ is the average value (because frequencies have relatively small differencies).
+
+Using the last two equations and the undepleted pump approximation, (\ref{eq_coupled_amplitude}a) and (\ref{eq_coupled_amplitude}b) are easily solved to obtain the pump fields
+\begin{subequations}
+\begin{align}
+	A_1(z) &= A_1(0)\mathrm{exp}[\mathrm{i}\gamma(P_1 + 2P_2)z] \\
+	A_2(z) &= A_2(0)\mathrm{exp}[\mathrm{i}\gamma(P_2 + 2P_1)z]
+	\label{eq_pump_sol}
+\end{align}
+\end{subequations}
+where $P_j = |A_j(z=0)|^2$.
+
+Using the same approximations on (\ref{eq_coupled_amplitude}c) and (\ref{eq_coupled_amplitude}d) and replacing eq (\ref{eq_pump_sol}) where needed we obtain two linear coupled equation for signal and idler:
+\begin{subequations}
+\begin{align}
+	\frac{dA_3}{dz} &= 2\mathrm{i}\gamma [(P_1 + P_2)A_3 + A_1(0)A_2(0)\mathrm{e}^{-\mathrm{i}\phi}A_4^*] \\
+	\frac{dA_4}{dz} &= 2\mathrm{i}\gamma [(P_1 + P_2)A_4 + A_1(0)A_2(0)\mathrm{e}^{-\mathrm{i}\phi}A_3^*]
+	\label{eq_sig_idl}
+\end{align}
+\end{subequations}
+where $\phi = [\Delta k - 3\gamma(P_1 + P_2)]z$
+
+\vspace{18pt}
+************************************************************************
+\vspace{12pt}
+
+The \textit{effective} phase mismatch is therefore given by
+\begin{equation}
+	\kappa = \Delta k + \gamma(P_1 + P_2)
 \end{equation}

### 2015-09-18 latex/article.tex
again

@@
 \usepackage{parcolumns}
-\usepackage[left=2.cm,right=2.cm,top=2.cm,bottom=2.cm]{geometry}
+\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}
 \usepackage[final]{pdfpages} %serve per aggiungere altre pagine pdf al file
@@
 \begin{align}
-	\nabla \times \textbf{E} &= -\frac{\partial \textbf{B}}{\partial t} \\
-	\nabla \times \textbf{H} &= \textbf{J} + \frac{\partial \textbf{D}}{\partial t} \\
-	\nabla \cdot \textbf{D} &= \rho_{\mathrm{f}} \\
+	\nabla \times \textbf{E} &= -\frac{\partial \textbf{B}}{\partial t}
+		\label{eq_maxwell_a} \\
+	\nabla \times \textbf{H} &= \textbf{J} + \frac{\partial \textbf{D}}{\partial t}
+		\label{eq_maxwell_b} \\
+	\nabla \cdot \textbf{D} &= \rho_{\mathrm{f}} 
+		\label{eq_maxwell_c} \\
 	\nabla \cdot \textbf{B} &= 0
+		\label{eq_maxwell_d}
 \end{align}
-\label{eq_maxwell}
 \end{subequations}
@@
 
-Taking the curl of eq (\ref{eq_maxwell}a) and substituting in it eq (\ref{eq_maxwell}c) it leads to the Helmholtz equation:
+Taking the curl of Eq. (\ref{eq_maxwell_a}) and substituting in it Eq. (\ref{eq_maxwell_c}) it leads to the Helmholtz equation:
 \begin{equation}
@@
 
-Defining the refractive index $n \equiv \sqrt{\varepsilon_r}$ of the material the previous equation (\ref{eq_helm_P}) and using the definition of \textbf{P} as in eq (\ref{eq_P_L})
+Defining the refractive index $n \equiv \sqrt{\varepsilon_r}$ of the material the previous equation (\ref{eq_helm_P}) and using the definition of \textbf{P} as in Eq. (\ref{eq_P_L})
 \begin{equation}
@@
 
-The general solution of eq (\ref{eq_helm_P}) is a transverse electromagnetic (TEM) wave, whose electric and magnetic fields are perpendicular to the propagation direction.
+The general solution of Eq. (\ref{eq_helm_P}) is a transverse electromagnetic (TEM) wave, whose electric and magnetic fields are perpendicular to the propagation direction.
 Without losing generality, we could assume $\hat{z}$ as the propagation direction and electric field of the form:
@@
 with $E$ amplitude of the electric field, $k = 2\pi/\lambda$ the wavevector and $\omega = 2\pi f$ the angular frequency.
-$\lambda$ and $f$ are relatively the wavelenght and the frequency of the electromagnetic wave.
+$\lambda$ and $f$ are relatively the wavelength and the frequency of the electromagnetic wave.
 The magnetic field has a similar equation.
@@
 Considering an ideal dielectric waveguide (no absorption) with the purpose of transmitting EM waves in the $\hat{z}$ direction, the total field distribution is a sum of continous TEM plane waves.
-Defining the amplitude of the fields as $E(\textbf{r},t) = F(x,y)A(z,t)$ and $k=\beta$ and substituting them in eq (\ref{eq_wave}) leads to the following equation:
+Defining the amplitude of the fields as $E(\textbf{r},t) = F(x,y)A(z,t)$ and $k=\beta$ and substituting them in Eq. (\ref{eq_wave}) leads to the following equation:
 \begin{equation*}
@@
 \begin{align}
-	\frac{\partial^2F(x,y)}{\partial x^2} + \frac{\partial^2F(x,y)}{\partial y^2} + \left[ k_0^2n^2-\beta^2\right]F(x,y) = 0 \\
-	\frac{\partial^2A(z,t)}{\partial z^2} + \frac{n^2}{c^2}\frac{\partial^2A(z,t)}{\partial t^2} = 0
-	\quad ??? \quad or \quad ??? \quad
-	\frac{\partial^2A(z,t)}{\partial z^2} + k^2n^2\frac{\partial^2A(z,t)}{\partial t^2} = 0
+	\frac{\partial^2F(x,y)}{\partial x^2} + \frac{\partial^2F(x,y)}{\partial y^2} + \left[ k_0^2n^2(x,y)-\beta^2\right]F(x,y) = 0
+	\label{eq_wg_a} \\
+	\frac{\partial^2\tilde{A}(z,\omega)}{\partial z^2} +2\mathrm{i}\beta\frac{\partial \tilde{A}(z,\omega)}{\partial z} +3n^2k_0^2\tilde{A}(z,\omega) = 0
+	\quad ! \neq ! \quad
+	2\mathrm{i}\beta_0\frac{\partial \tilde{A}(z,\omega)}{\partial z} +(\tilde{\beta}^2 - \beta_0^2)\tilde{A}(z,\omega) = 0
+	\label{eq_wg_b}
 \end{align}
 \end{subequations}
-where $k_0$ is the wavevector in vacuum and $n$ is a function of the position (mainly $x$ and $y$).
+where $k_0$ is the wavevector in vacuum and $n=n(x,y)$ is a function of the position (mainly $x$ and $y$ for a straight waveguide).
 
-\vspace{18pt}
-************************************************************************
-\vspace{12pt}
+The first equation, once solved, leads to the field distribution $F(x,y)$ in the plane perpendicular to the waveguide axis ($\hat{z}$).
+Its solution is strictly linked to the geometry of the waveguide and to the dependence of the refractive index $n$ to the position in the plane.
 
-These equations, once solved, lead to the distribution of the fields in the plane xy and to their modification along the z axis.
-
-\vspace{18pt}
-************************************************************************
-\vspace{12pt}
-
-Not all field distribution are transmitted through the waveguide without energy loss \textbf{(?)}.
+The second equation (\ref{eq_wg_b}), on the other hand, define the change of field distribution along the $\hat{z}$ axis, or the waveguide axis.
+Imposing to this equation to be zero means that we force the field distribution $F$ not to change.
+Indeed not all field distributions are transmitted through the waveguide without energy loss \textbf{(?)} and thus without changing $F$.
 % Modes are fields that maintain the same transverse distribution and polarization at all locations along the waveguide axis.
@@
 
-Both TE and TM modes can be again classified by their order, that is proportional to the number of maxima of the modulus of the electric and magnetic fields in the core section.
+Solving for $\beta$, we obtain that only a discrete set of values $\beta_m$ verify the equation.
+Replacing those values in Eq. (\ref{eq_wg_a}), leads to the field distribution F(x,y) to be defined.
+Therefore both TE and TM modes can be again classified by their order, that is proportional to the number of maxima of the modulus of the electric and magnetic fields in the core section.
 The first order has only one maximum at the center of the core, the second order has two maxima placed simmetrically from the center and so on.
 
-Moreover it is noteworthy that the field distributions of odd orders are even functions and those of even order are odd functions.
+Moreover it is noteworthy that the field distributions of even orders are even functions and those of odd orders are odd functions.
 
@@
 \begin{equation}
-\beta \equiv k_z
+\beta \equiv k|_z
 \end{equation}
@@
 \begin{equation}
-	\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right)
+	\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) = \textbf{P}_L + \textbf{P}_{NL}
 	\label{eq_P_general}
@@
 
+Considering a silicon waveguide with a rectangular core section, to study the propagation of four wave, the total electric field and be expressed as
+\begin{equation}
+	\textbf{E} = \frac{1}{2}\hat{x} \sum_{j=1}^4 E_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
+	\label{eq_E}
+\end{equation}
+
+Substituting Eq. (\ref{eq_P_NL}) in Eq. (\ref{eq_E}) we obtain $8^3=512$ terms.
+We can then write the non linear terms $P_{NL}$ of the induced electric polarization as
+\begin{equation}
+	\textbf{P} = \frac{1}{2}\hat{x} \sum_{j=1}^4 P_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
+	\label{eq_P}
+\end{equation}
+
+Replacing \ref{} in Eq. (\ref{eq_helm_P}) leads to eight coupled equation: four of them are equivalent of Eq. (\ref{eq_wg_a}) and describe the field distribution of the mode of each wave.
+The latter four are the equivalent of Eq. (\ref{eq_wg_b}) and describe how the field change while travelling through the waveguide.
+
 \vspace{18pt}
@@
 
-\begin{equation}
-	\textbf{E} = \frac{1}{2}\hat{x} \sum_{j=1}^4 E_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
-	\label{eq_E}
-\end{equation}
-and the induced electric polarization:
-\begin{equation}
-	\textbf{P} = \frac{1}{2}\hat{x} \sum_{j=1}^4 P_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
-	\label{eq_P}
-\end{equation}
 considering $E_j(\textbf{r}) = F_j(x,y)A_j(z)$ where $F_j$ is the spatial distribution of the mode
@@
 \begin{align}
-	\frac{dA_1}{dz} &= \frac{\mathrm{i}n_L\omega_1}{c}\left[ \left( f_{11} |A_1|^2 + 2 \sum_{k\neq1} f_{1k}|A_k|^2\right)A_1 + 2f_{1234}A_2^*A_3A_4\mathrm{e}^{+\mathrm{i}\Delta k_z} \right] \\
-	\frac{dA_2}{dz} &= \frac{\mathrm{i}n_L\omega_2}{c}\left[ \left( f_{22} |A_2|^2 + 2 \sum_{k\neq2} f_{2k}|A_k|^2\right)A_2 + 2f_{2134}A_1^*A_3A_4\mathrm{e}^{+\mathrm{i}\Delta k_z} \right] \\
-	\frac{dA_3}{dz} &= \frac{\mathrm{i}n_L\omega_3}{c}\left[ \left( f_{33} |A_3|^2 + 2 \sum_{k\neq3} f_{3k}|A_k|^2\right)A_3 + 2f_{3412}A_1A_2A_4^*\mathrm{e}^{-\mathrm{i}\Delta k_z} \right] \\
+	\frac{dA_1}{dz} &= \frac{\mathrm{i}n_L\omega_1}{c}\left[ \left( f_{11} |A_1|^2 + 2 \sum_{k\neq1} f_{1k}|A_k|^2\right)A_1 + 2f_{1234}A_2^*A_3A_4\mathrm{e}^{+\mathrm{i}\Delta k_z} \right]
+		\label{eq_coupled_amplitude_a}\\
+	\frac{dA_2}{dz} &= \frac{\mathrm{i}n_L\omega_2}{c}\left[ \left( f_{22} |A_2|^2 + 2 \sum_{k\neq2} f_{2k}|A_k|^2\right)A_2 + 2f_{2134}A_1^*A_3A_4\mathrm{e}^{+\mathrm{i}\Delta k_z} \right]
+		\label{eq_coupled_amplitude_b}\\
+	\frac{dA_3}{dz} &= \frac{\mathrm{i}n_L\omega_3}{c}\left[ \left( f_{33} |A_3|^2 + 2 \sum_{k\neq3} f_{3k}|A_k|^2\right)A_3 + 2f_{3412}A_1A_2A_4^*\mathrm{e}^{-\mathrm{i}\Delta k_z} \right]
+		\label{eq_coupled_amplitude_c}\\
 	\frac{dA_4}{dz} &= \frac{\mathrm{i}n_L\omega_4}{c}\left[ \left( f_{44} |A_4|^2 + 2 \sum_{k\neq4} f_{4k}|A_k|^2\right)A_4 + 2f_{4321}A_1A_2A_3^*\mathrm{e}^{-\mathrm{i}\Delta k_z} \right]
+		\label{eq_coupled_amplitude_d}
 \end{align}
-\label{eq_coupled_amplitude}
 \end{subequations}
@@
 
-Using the last two equations and the undepleted pump approximation, (\ref{eq_coupled_amplitude}a) and (\ref{eq_coupled_amplitude}b) are easily solved to obtain the pump fields
+Using the last two equations and the undepleted pump approximation, (\ref{eq_coupled_amplitude_a}) and (\ref{eq_coupled_amplitude_b}) are easily solved to obtain the pump fields
 \begin{subequations}
@@
 	A_2(z) &= A_2(0)\mathrm{exp}[\mathrm{i}\gamma(P_2 + 2P_1)z]
+\end{align}
 	\label{eq_pump_sol}
-\end{align}
 \end{subequations}
@@
 
-Using the same approximations on (\ref{eq_coupled_amplitude}c) and (\ref{eq_coupled_amplitude}d) and replacing eq (\ref{eq_pump_sol}) where needed we obtain two linear coupled equation for signal and idler:
+Using the same approximations on (\ref{eq_coupled_amplitude_c}) and (\ref{eq_coupled_amplitude_d}) and replacing Eqs (\ref{eq_pump_sol}) where needed we obtain two linear coupled equations for signal and idler:
 \begin{subequations}
 \begin{align}
-	\frac{dA_3}{dz} &= 2\mathrm{i}\gamma [(P_1 + P_2)A_3 + A_1(0)A_2(0)\mathrm{e}^{-\mathrm{i}\phi}A_4^*] \\
+	\frac{dA_3}{dz} &= 2\mathrm{i}\gamma [(P_1 + P_2)A_3 + A_1(0)A_2(0)\mathrm{e}^{-\mathrm{i}\phi}A_4^*]
+	\label{eq_sig}\\
 	\frac{dA_4}{dz} &= 2\mathrm{i}\gamma [(P_1 + P_2)A_4 + A_1(0)A_2(0)\mathrm{e}^{-\mathrm{i}\phi}A_3^*]
-	\label{eq_sig_idl}
+	\label{eq_idl}
 \end{align}
 \end{subequations}
-where $\phi = [\Delta k - 3\gamma(P_1 + P_2)]z$
+where $\phi = [\Delta k - 3\gamma(P_1 + P_2)]z$.
+
+These equations can be solved introducing $B_j = A_j \,\mathrm{exp}[-2\mathrm{i}\gamma(P_1+P_2)z]$ for $j=3,4$ giving their general solution as
+\begin{equation*}
+	B_j(z) = (a_j\mathrm{e}^{gz}+b_j\mathrm{e}^{-gz})\mathrm{exp}(-i\kappa z/2)
+\end{equation*}
+with $\kappa = \Delta + \gamma(P_1 + P_2)$ \textit{effective phase mismatch} and $g = \sqrt{4\gamma^2P_1P_2 - \kappa^2/4}$ the \textit{parametric gain}.
+
+The solutions of Eqs (\ref{eq_sig}) and (\ref{eq_idl}) are therefore
+\begin{subequations}
+\begin{align}
+	A_3(z) &= \left(a_3\mathrm{e}^{gz}+b_3\mathrm{e}^{-gz}\right)\mathrm{exp}\left[-\frac{\mathrm{i}}{2}(\Delta k -3\gamma(P_1 + P_2))z\right]
+		\label{eq_sig_sol} \\
+	A_4(z) &= \left(a_4\mathrm{e}^{gz}+b_4\mathrm{e}^{-gz}\right)\mathrm{exp}\left[-\frac{\mathrm{i}}{2}(\Delta k -3\gamma(P_1 + P_2))z\right]	
+		\label{eq_idl_sol}
+\end{align}
+\end{subequations}
 
@@
 
-The \textit{effective} phase mismatch is therefore given by
-\begin{equation}
-	\kappa = \Delta k + \gamma(P_1 + P_2)
-\end{equation}
-
-\vspace{18pt}
 ****		è necessario verificare conservazione di energia e momento
@@
 In order to be efficient, the parametric process needs to verify both the conservation of energy and momentum.
-\begin{equation}
-\omega_1 + \omega_2 = \omega_3 + \omega_4
-\end{equation}
-\begin{equation}
-\beta_1 + \beta_2 = \beta_3 + \beta_4
-\end{equation}
-%\Delta k = \beta_3 + \beta_4 - \beta_1 - \beta_2
+$$\omega_1 + \omega_2 = \omega_3 + \omega_4$$
+$$\Delta k = \beta_3 + \beta_4 - \beta_1 - \beta_2$$
+****
+$$\Omega_S = \omega_1 + \omega_3 = \omega_4 - \omega_1$$
+where we assume $\omega_3 < \omega_4$.
+$$\Omega_S = |\omega_P - \omega_I| = |\omega_S - \omega_P|$$
+****
 
-\section{Simulating and coding}
+parlare di $L_{coh}$
 
+\section{Computational models}
+\subsection{Simulation}
 To understand the behaviour of the waveguide, it is necessary to first know how waves of different frequency are transmitted through the waveguide.
@@
 
-The reason for this choice is that silicon is transparent at these wavelenght and also for the availability of laser that emit at the specific wavelenght.
+The reason for this choice is that silicon is transparent at these wavelength and also because of the availability of lasers that emit at the specific wavelength.
 
@@
 
-We eventually obtained a list of combinations, for each of which we verified the conservation of energy and momentum.
+We eventually obtained a list of combinations and for each one we verified the conservation of energy and momentum.
 
-$$\omega_1 = \omega_2 = \omega_P$$
-$$\omega_I = 2\omega_P - \omega_S$$
-$$\Omega_S = \omega_1 + \omega_3 = \omega_4 - \omega_1$$
-where we assume $\omega_3 < \omega_4$.
-$$\Omega_S = |\omega_P - \omega_I| = |\omega_S - \omega_P|$$
+\subsubsection*{Conservation of energy and momentum}
+Starting from the data of the effective index of each order at different wavelengths and temperatures, we evaluated the phase mismatch of all sets.
+The evaluation was made on a grid of temperature and signal wavelength.
 
-$$\Delta k = \beta_3 + \beta_4 - 2\beta_1$$
+Each point was evaluated with the next system:
+\[
+\left\{
+	\begin{array}{rl}
+		\omega_I		&= 2\omega_P - \omega_S \\
+		\\
+		\Delta k		&= \beta_S + \beta_I - 2\beta_P \\
+					&= \frac{2\pi}{\lambda_S}n_{eff}\left( \omega_s, T \right) + \frac{2\pi}{\lambda_I}n_{eff}\left( \omega_I, T \right) - 2\frac{2\pi}{\lambda_P}n_{eff}\left( \omega_P, T \right)
+	\end{array}
+\right.
+\]
+Imposing the conservation of energy, we obtained the only frequency permitted for $\omega_I$.
+We replaced its value in the conservation of momentum formula, giving us the phase mismatch as a function of signal wavelength and temperature, for each set of orders.
 
-$$L_{coh} = \frac{2\pi}{|\Delta k|}$$
+\subsubsection*{Selection of sets}
+Once evaluated all the points on the grid for all the sets available, we selected only the interesting combinations.
+The critical parameter on which the choice was based on is the coherence length: only those sets which had a maximum value of coherence length greater than a supposed sample length $L_{sam} = $\SI{1}{\cm} was chosen.
+$$L_{coh} = \frac{2\pi}{|\Delta k|} \geq L_{sam}$$
+Again, we had a list of the only combination interesting for our purpose.
 
+It is important to note that, in general, each combination could have more that one maximum of coherence length $L_{coh}$ in wavelength for each temperature value.
+
+\subsubsection*{Data aggregation}
+After the selection of sets, we evaluated the dependence of each maximum in temperature.
 \section{Prototyping}

### 2015-09-18 latex/article.tex
big changes: comsol, mainly but also phasematch

@@
 \begin{equation}
-	\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) = \textbf{P}_L + \textbf{P}_{NL}
+	\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) = \mathrm{\textbf{P}_L} + \mathrm{\textbf{P}_{NL}}
 	\label{eq_P_general}
@@
 Substituting Eq. (\ref{eq_P_NL}) in Eq. (\ref{eq_E}) we obtain $8^3=512$ terms.
-We can then write the non linear terms $P_{NL}$ of the induced electric polarization as
+We can then write the non linear terms $\mathrm{\textbf{P}_{NL}}$ of the induced electric polarization as
 \begin{equation}
-	\textbf{P} = \frac{1}{2}\hat{x} \sum_{j=1}^4 P_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
+	\mathrm{\textbf{P}_{NL}} = \frac{1}{2}\hat{x} \sum_{j=1}^4 P_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
 	\label{eq_P}
@@
 
-Replacing \ref{} in Eq. (\ref{eq_helm_P}) leads to eight coupled equation: four of them are equivalent of Eq. (\ref{eq_wg_a}) and describe the field distribution of the mode of each wave.
-The latter four are the equivalent of Eq. (\ref{eq_wg_b}) and describe how the field change while travelling through the waveguide.
+where for example $P_4$ would be
+\[
+\begin{array}{rl}
+	P_4 &= \frac{3\varepsilon_0}{4} \chi^3_{xxxx}\left[ |\mathrm{E}_4|^2\mathrm{E}_4 2(|\mathrm{E}_1|^2+|\mathrm{E}_2|^2+|\mathrm{E}_3|^2)\mathrm{E}_4 \right. \\
+	&+ \left. 2\mathrm{E}_1\mathrm{E}_2\mathrm{E}_3\mathrm{e}^{i\phi_+}+2\mathrm{E}_1\mathrm{E}_2\mathrm{E}_3^*\mathrm{e}^{i\phi_-}\right] \\
 
-\vspace{18pt}
-************************************************************************
-\vspace{12pt}
+\end{array}
+\]
+\hspace{18pt}with $\phi_+$ and $\phi_-$ defined as
+\[
+\begin{array}{lr}
+\phi_+ &= (\beta_1+\beta_2+\beta_3-\beta_4+)z - (\omega_1+\omega_2+\omega_3-\omega_4)t \\
+\phi_- &= (\beta_1+\beta_2-\beta_3-\beta_4+)z - (\omega_1+\omega_2-\omega_3-\omega_4)t \\
+\end{array}
+\]
 
-considering $E_j(\textbf{r}) = F_j(x,y)A_j(z)$ where $F_j$ is the spatial distribution of the mode
+Replacing Eq.
+(\ref{eq_P}) in Helmholtz equation (\ref{eq_helm_P}) leads to eight coupled equations: four of them are equivalent of Eq.
+(\ref{eq_wg_a}) and describe the field distribution of the mode of each wave.
+The remaining four are the equivalent of Eq. (\ref{eq_wg_b}) and describe how the field change while travelling through the waveguide.
+Those, considering $E_j(\textbf{r}) = F_j(x,y)A_j(z)$ where $F_j$ is the spatial distribution of the mode, can be written as:
 
@@
 where
-
 \begin{equation}
@@
 \end{equation}
-and
+\hspace{18pt}and
 \begin{equation}
@@
 \end{equation}
+\hspace{18pt}are the overlap integrals of the different modes, where the brackets mean an integration on a plane $\langle g(x,y)\rangle = \int\int_{-\inf}^{\inf}g(x,y)\mathrm{dxdy}$.
+The physical interpretation of such quantities is how much different modes are superimposed/\ref{}/overlapped with each others.
 
@@
 \end{equation*}
-with $\kappa = \Delta + \gamma(P_1 + P_2)$ \textit{effective phase mismatch} and $g = \sqrt{4\gamma^2P_1P_2 - \kappa^2/4}$ the \textit{parametric gain}.
+with $\kappa = \Delta k + \gamma(P_1 + P_2)$ \textit{effective phase mismatch} and $g = \sqrt{4\gamma^2P_1P_2 - \kappa^2/4}$ the \textit{parametric gain}.
 
@@
 parlare di $L_{coh}$
+
+We can define a length scale, known as the coherence length, using $L_{coh} = 2\pi/|\Delta\kappa|$, where $\Delta\kappa$ is the maximum value of the effective phase mismatch that can be tolerated.
+Moreover significant FWM occurs if $L_{sam}<L_{coh}$ where $L_{sam}$ is the sample length.
 
@@
 In order to achieve a greater effect from the different temperature, we tried to move the heater from over the center of the core to the side.
-This operation was intended to increase the difference of behaviour between low and high orders.
+This operation was intended to increase the difference of behaviour between low and high orders enabling thus the creation of new peaks in the coherence length.
 \subsection{Different geometries}

### 2015-09-18 gitcode/createFit.m

@@ -1,38 +1,0 @@
-function [fitresult, gof] = createFit(wlvec, tvec, zdata)
-%CREATEFIT(WLVEC,TVEC,ZDATA)
-%  Create a fit.
-%
-%  Data for 'untitled fit 1' fit:
-%      X Input : wlvec
-%      Y Input : tvec
-%      Z Output: zdata
-%  Output:
-%      fitresult : a fit object representing the fit.
-%      gof : structure with goodness-of fit info.
-%
-%  See also FIT, CFIT, SFIT.
-
-%  Auto-generated by MATLAB on 28-Aug-2015 18:47:18
-
-
-%% Fit: 'untitled fit 1'.
-[xData, yData, zData] = prepareSurfaceData( wlvec, tvec, zdata );
-
-% Set up fittype and options.
-ft = fittype( 'poly52' );
-
-% Fit model to data.
-[fitresult, gof] = fit( [xData, yData], zData, ft );
-
-% Plot fit with data.
-figure( 'Name', 'untitled fit 1' );
-h = plot( fitresult, [xData, yData], zData );
-legend( h, 'untitled fit 1', 'zdata vs. wlvec, tvec', 'Location', 'NorthEast' );
-% Label axes
-xlabel wlvec
-ylabel tvec
-zlabel zdata
-grid on
-view( 0.5, 38.0 );
-
-

### 2015-09-18 gitcode/phase-matching/phasematching_v3.m

@@ -16,7 +16,7 @@ while ( ans1 == 0 )
     % Handle response
     switch choice
         case 'Import File'
-            disp('File chosen.')
+            disp('Choose the file to import.\nShould be something like yyyy-MM-dd_HH:mm:ss.mat\n');
             ans1 = 0;
         case 'Exit program'
             %disp('\n\nExiting right now.')
@@ -30,9 +30,9 @@ while ( ans1 == 0 )
     end
     
     if (ans1 == 0 )
-        fprintf('\nChoose the file to import.\nShould be something like yyyy-MM-dd_HH:mm:ss.mat\n');
         [ans1, ans2] = uigetfile({'../data/*.mat'});     % choose file to load
         
+        fprintf('File chosen: ', strcat(ans2, ans1));
         load( strcat(ans2, ans1) );
     end
 end
@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 4001;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 601;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -328,8 +328,10 @@ for rr=1:pm.n_results;
             
             for tt=1:pm.n_sample_t
                 [~, locs] = findpeaks(zData(:,tt));
+                locs = locs( find(zData(locs,tt) >= 1 ) );
+                
                 maxL = max([maxL, length(locs)]);
-                y(tt, 1:length(locs)) = locs;
+                y(tt, 1:length(locs)) = vec.sample_wlen(locs);
                 
                 zData_0 = zData;
                 zData_0(1,tt) = 0;
@@ -349,18 +351,34 @@ for rr=1:pm.n_results;
             end
             
             y(:, maxL+1:end) = [];
-            y = vec.sample_wlen(y);
             y2(:, maxL+1:end) = [];
             
             for tt=1:maxL
-                [results.max.ft, ~] = fit( vec.sample_temp, y(:,tt), 'poly1');
-                results.max.m(rr, tt)   = results.max.ft.p1;
-                results.max.q(rr, tt)   = y(1,tt);
+                a = y(:,tt);
+                b = find(isnan(a) == 0);
+                if length(b)>1
[…]

### 2015-09-19 gitcode/phase-matching/single_combination.m
single combination analyzer

@@ -1,0 +1,325 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+%   This script will search for phase matching conditions                 %
+%                                                                         %
+%                                                         D. Bazzanella   %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Import data structures
+
+ans1 = false;
+while ~ans1
+    % Construct a questdlg with three options
+    choice = questdlg('Import a file or to exit the program?', 'Import File', 'Import File', 'Exit program', 'Go on', ...
+        'Import File');
+    % Handle response
+    switch choice
+        case 'Import File'
+            disp('Choose the file to import.\nShould be something like yyyy-MM-dd_HH:mm:ss.mat\n');
+            ans1 = false;
+        case 'Exit program'
+            %disp('\n\nExiting right now.')
+            clear ans1 choice
+            error('Exiting right now.');
+        %{
+        case 'Go on'
+            disp('\nGoing on...\n');
+            ans1 = 1;
+        %}
+    end
+    
+    if ~ans1
+        [ans1, ans2] = uigetfile({'../data/*.mat'});     % choose file to load
+        
+        fprintf(strcat('File chosen: ', ans1) );
+        load( strcat(ans2, ans1) );
+    end
+end
+
+% physical constants
+const.c     = 299792458;        % [m/s]
+const.T     = 293.15;           % [K]
+
+% rescale unit of measure
+vec.wid  = vec.wid .* 1e-6;     % [m]
+vec.hgt  = vec.hgt .* 1e-6;     % [m]
+vec.temp = vec.temp + const.T;  % [K]
+
+clear ans1 ans2 choice ans
+
+%% Set initial parameters
+
+tic
+fprintf('\nSetting initial parameters\n');
+
+% phase matching parameters
[…]

### 2015-09-19 gitcode/phase-matching/single_combination.m
fixed

@@ -317,7 +317,7 @@ f = figure(1);
 axes1 = axes('Parent',f);
 mesh(wlen_grid, temp_grid, f_Lcoh(wlen_grid, temp_grid));
 hold(axes1,'on');
-zlim(axes1,[0.9 1]);
+zlim(axes1,[-0.1 2]);
 
 clear wlen_grid temp_grid
 

### 2015-09-19 latex/article.tex
computational model section & other

@@
 \usepackage{siunitx}
+\usepackage{booktabs}	% better tables
+\usepackage{multirow}
 
@@
 
+\makeatletter
+\renewcommand\paragraph{
+   \@startsection{paragraph}{4}{\z@}%
+   {-3.25ex\@plus -1ex \@minus -.2ex}%
+   {1.5ex \@plus .2ex}%
+   {\normalfont\normalsize\bfseries}}
+\makeatother
+
 \pagenumbering{roman}	% numeration in roman numbers
+
 \begin{document}
@@
 
-The study is focused on a silicon-based waveguide with a silicon ($\mathrm{Si}$) core of rectangular section and a silica ($\mathrm{Si0}_2$) cladding.
+The study is focused on a silicon-based waveguide with a silicon ($\mathrm{Si}$) core of rectangular section and a silica ($\mathrm{SiO}_2$) cladding.
 The purpose of the waveguide is to generate light through a partial degenerate Four-Wave Mixing phenomenon.
@@
 
-The general solution of Eq. (\ref{eq_helm_P}) is a transverse electromagnetic (TEM) wave, whose electric and magnetic fields are perpendicular to the propagation direction.
+The general solution of Eq. (\ref{eq_helm_P}) is a transverse electromagnetic (TEM) wave, which electric and magnetic fields are perpendicular to the propagation direction.
 Without losing generality, we could assume $\hat{z}$ as the propagation direction and electric field of the form:
@@
 $$\Omega_S = |\omega_P - \omega_I| = |\omega_S - \omega_P|$$
-****
-
-parlare di $L_{coh}$
 
@@
 \section{Computational models}
-\subsection{Simulation}
 To understand the behaviour of the waveguide, it is necessary to first know how waves of different frequency are transmitted through the waveguide.
@@
 Our aim was to develop a model to work with an infrared laser pump with $\lambda_{p} = \SI{1.55}{\um}$.
+The reason for this choice is that silicon is transparent at these wavelength and also because of the availability of lasers that emit at the specific wavelength.
+
 We narrowed our simulations to a frequency gap centered in $\omega_p = 2\pi \nu_p = 2\pi c / \lambda_{p}$.
 The gap chosen was precisely $[\SI{1.45}{\um} ,\, \SI{1.65}{\um}]$ or the equivalent $[\SI{182}{\THz} ,\, \SI{207}{\THz}]$.
+The temperature gap, on the other hand, was chosen to be $[\SI{0}{\K} - \SI{400}{\K}]$ over ambient temperature $T_{amb} = \SI{293.15}{\K} = \SI{20}{\celsius}$, that is $[\SI{293.15}{\K} - \SI{693.15}{\K}]$.
 
-The reason for this choice is that silicon is transparent at these wavelength and also because of the availability of lasers that emit at the specific wavelength.
+\subsection{Simulation}
+To obtain definite solutions, we had to assign the materials and a geometry to the problem first.
 
-\vspace{18pt}
-****
-\vspace{12pt}
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.55\textwidth]{geometry.png}
+	\label{fig_wg_Section}
+	\caption{Section of the rectangular waveguide}
+\end{figure}
 
-Our data output was therefore the field distribution and effective index for a number of modes for each parametric configuration.
+We modelized a dielectric waveguide with a silicon (Si) core \SI{3}{\um} wide and \SI{.25}{\um} high.
+The cladding was set to be silica (SiO2) and coated the top of the core with a thickness of \SI{.35}{\um}.
+For both materials was defined a refractive index dependent on the wavelength $n=n(\lambda)$, as given by the empirical relationship called \textit{Sellmeier equation}.
+\begin{equation}
+	n^2(\lambda) = 1+ \sum_i \chi_{0i}\frac{\lambda^2}{\lambda^2-\lambda^2_i}
+	\label{eq_sellmeier}
+\end{equation}
+where the weights are defined experimentally and vary depending on the material.
 
-The next step was to classify these data depending on the order and type (TE or TM) of the modes.
-We achieved this by analyzing the maxima of the field distributions.
-We obtained then a well organized data matrix filled with the value of effective index for each combination of parameters.
+We positioned a thermal reservoir, a ``\textit{heater}", \SI{0.3}{\um} wide at the top of the cladding, exactly over the center of the waveguide core and set to mantain a specific temperature in the gap, given by the configuration chosen.
+To 
+define the density $\rho$ in [\si{\kg\m^3}], the thermal conductivity $\kappa_{TH}$ in [\si{\W\per\m\per\K}] and the heat capacity $C_P$ in [\si{\J\per\kg\per\K}] of the different materials.
+
+\begin{table}[ht]
+\centering
+  \begin{tabular}{lcccc}  
+    \toprule
+		& \multicolumn{3}{c}{Properties} \\
+    \cmidrule(r){2-5}
+    	\multirow{2}{*}{Materials}    & $\rho$ & $\kappa_{TH}$ & $C_P$ & TOC\\
+  		& [\si{\kg\m^3}] & [\si{\W\per\m\per\K}] & [\si{\J\per\kg\per\K}] & [$10^{-4}$\si{\per\K}] \\
+    \midrule
+    Silicon (Si)			& 2329	& 130	& 700	& 1.87\\
+    Silica (SiO$_2$)		& 2203	& 1.38	& 703	& 0\\
+    \bottomrule
+  \end{tabular}
+  \label{tab_materials}
+  \caption{Thermal properties of silicon and silica glass}
+\end{table}
+
+Moreover, in order to be influenced by the different temperatures, we had to add to the definition of refractive index of the silicon a term dependent on the temperature.
+For our purpose this dependence can easily be considered linear:
+\begin{equation}
+n = n(\lambda)+\mathrm{TOC}\cdot T
+\end{equation}
+where $\mathrm{TOC}|_{\mathrm{Si}} = \SI{1.87e-4}{\per\K}$\cite{n_db} is called Termo-Optic Coefficient.
+The coefficient of silica glass is negligible and coefficient was therefore considered zero $\mathrm{TOC}|_{\mathrm{SiO}_2} \approx 0$.
+
+\subsubsection{Numerical solution}
+Because the degree of freedom of the problem were too many, we resorted to automated algorithms which gave us a numerical, and therefore approximate, solution.
+
+\paragraph{Heat transfer: stationary solution}
+The first step was solving the equation for the heat transfer to obtain a stationary solution for each temperature in the gap.
+That means to know the local temperature for each position in the core and in the cladding, for each initial setup.
+
+\paragraph{EM mode analysis}
+
+The second step was to find the different modes of the waveguide for each set of parameters, such as temperature and wavelength.
+
+We emploied an automated algorithm to solve, in the frequency domain, the Helmholtz equation on a fine grid in the waveguide section.
+Each point of evaluation took into account the effective index of the material, slightly changed by the local temperature obtained by the stationary solution.
+
+This algorithm was set to find the eight modes which effective index $n_{eff}$ was closest to $n_{eff}=4$ in absolute value.
+\subsubsection{Data output}
+We obtained the field distribution and a series of parameters as our data output for each parametric configuration.
+In particular the parameters were the effective index $n_{eff}$, the effective area $A_{eff}$ and the nonlinear parameter $\gamma$, for each mode and for each wavelength and temperature.
+
+\subsection{Data classification}
+The next step was to classify these data, depending on the type (TE or TM) and order (1,2,3...) of the modes.
+We achieved this by analyzing a sample taken at $y=0$ of the field distributions.
+The ratio between the maxima values of the x-component and y-component of the electric field allowed to distinguish the mode type: TE or TM.
+Those fields which had the maximum component in the y direction were categorized as TE modes while those which had the maximum component in the x direction as TM modes.
+The number of maxima of the modulus of the field showed us the order of the mode.
+
+We obtained then a well organized data matrix filled with the value of effective index $n_{eff}$, effective area $A_{eff}$ and nonlinear parameter $\gamma$ for each combination of parameters.
 
 \subsection{Data processing}
-Starting from raw data consisting of the effective index for each parametric configuration, we fitted them with a polinomial function of frequency $\omega = 2\pi \nu$ and temperature $T$, obtaining:
-$$n_{eff} = f_{mt,\,mo} \left( \omega, T \right)$$
+
+\subsubsection{Polynomial fit}
+Starting from raw data consisting of the effective index for each parametric configuration, we fitted them with a polinomial function of frequency $\omega = 2\pi \nu$ or $\lambda$ and temperature $T$, obtaining:
+$$n_{eff} = f_{mt,\,mo} \left( \omega, T \right) = f'_{mt,\,mo} \left( \lambda, T \right)$$
 where $mt$ and $mo$ means respectively \textit{mode type} (TE or TM) and \textit{mode order} (1, 2, 3, ...)
 
-\vspace{18pt}
-************************************
+Specifically, we used a polynomial expression of fifth order in wavelength and of second order in temperature ``\texttt{poly52}".
 
-\subsubsection*{Order combination}
+\subsubsection{Order combination}
 
@@
 
-\subsubsection*{Conservation of energy and momentum}
+\subsubsection{Conservation of energy and momentum}
 Starting from the data of the effective index of each order at different wavelengths and temperatures, we evaluated the phase mismatch of all sets.
@@
 
-\subsubsection*{Selection of sets}
+\subsubsection{Selection of sets}
 Once evaluated all the points on the grid for all the sets available, we selected only the interesting combinations.
@@
 
-\subsubsection*{Data aggregation}
-After the selection of sets, we evaluated the dependence of each maximum in temperature.
-\section{Prototyping}
+\subsubsection{Data aggregation}
+After the selection of sets, we evaluated the dependence of each maximum on temperature.
 
-\subsection{Heater configurations}
+\subsection{Second heater configuration}
 In order to achieve a greater effect from the different temperature, we tried to move the heater from over the center of the core to the side.
@@
 
-\section{Conclusion}
+\section{Conclusions}
+\subsection{Improvements}
+\subsection{Results}
 
@@
 \bibitem{saleh} B. E. A. Saleh, M. C. Teich. Fundamentals of photonics, 2nd edition. 2007
+\bibitem{n_db} http://refractiveindex.info/
 \end{thebibliography}

### 2015-09-19 gitcode/phase-matching/single_combination.m

@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 2001;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 1001;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -73,7 +73,7 @@ for ww=1:pm.n_sample_wl
 end
 
 % sampling temperature
-pm.n_sample_t = 401;
+pm.n_sample_t = 1001;
 pm.step_t = (vec.temp(end) - vec.temp(1) )/(pm.n_sample_t - 1);
 
 vec.sample_temp = zeros(pm.n_sample_t,1);
@@ -311,15 +311,48 @@ toc
 
 %% 3D surface plot w/ temperature
 % creat grid of evaluation
+tic
 [wlen_grid, temp_grid]  = meshgrid(vec.sample_wlen, vec.sample_temp);
 
 f = figure(1);
 axes1 = axes('Parent',f);
 mesh(wlen_grid, temp_grid, f_Lcoh(wlen_grid, temp_grid));
 hold(axes1,'on');
-zlim(axes1,[-0.1 2]);
+zlim(axes1,[0.1 2]);
 
+toc
 clear wlen_grid temp_grid
 
-%% 2D plots of center & bandwidth
+%% 2D contour plots
 
+tic
+[wlen_grid, temp_grid]  = meshgrid(vec.sample_wlen, vec.sample_temp);
+
+f = figure(2);
+axes1 = axes('Parent',f);
+contour(1.1>f_Lcoh(wlen_grid, temp_grid)>=1);
+toc
+
+%% 2D plots of center & bandwidth
+%{
+f_z     = @(xs,L) 2.*pi./abs(f_delta(xs,t))-L;
+f_zero  = @(xs) f_z(xs,L);
+
+contx = zeros(pm.n_sample_t,10).*NaN;
+conty = zeros(pm.n_sample_t,10).*NaN;
+
+L = 1;
+for tt=1:pm.n_sample_t
+    fprintf(tt,'\n');
+    t = vec.sample_temp(tt);
[…]

### 2015-09-19 latex/article.tex
up to data aggregation

@@
     	\multirow{2}{*}{Materials}    & $\rho$ & $\kappa_{TH}$ & $C_P$ & TOC\\
-  		& [\si{\kg\m^3}] & [\si{\W\per\m\per\K}] & [\si{\J\per\kg\per\K}] & [$10^{-4}$\si{\per\K}] \\
+  		& [\si{\kg\m^3}] & [\si{\W\per\m\per\K}] & [\si{\J\per\kg\per\K}] & [\si{\per\K}] \\
     \midrule
-    Silicon (Si)			& 2329	& 130	& 700	& 1.87\\
+    Silicon (Si)			& 2329	& 130	& 700	& \num{1.87e-4}\\
     Silica (SiO$_2$)		& 2203	& 1.38	& 703	& 0\\
@@
 
-Specifically, we used a polynomial expression of fifth order in wavelength and of second order in temperature ``\texttt{poly52}".
+Specifically, we used a polynomial expression of fifth order in wavelength and second order in temperature ``\texttt{poly52}".
 
@@
 Only those in which the sum of the orders is an even number are interesting.
-To narrow the possible sets, we chose to permit only full TE or full TM  combinations.
+To narrow the possible sets, we chose only full TE or full TM  combinations.
 
-We eventually obtained a list of combinations and for each one we verified the conservation of energy and momentum.
+We eventually obtained a list of combinations and for each one we evaluated the phase mismatch.
 
 \subsubsection{Conservation of energy and momentum}
-Starting from the data of the effective index of each order at different wavelengths and temperatures, we evaluated the phase mismatch of all sets.
-The evaluation was made on a grid of temperature and signal wavelength.
+As it is, the phase mismatch is a function of the wavelenghts of pump, signal and idler.
+Imposing the conservation of energy,
+\begin{equation}
+2\omega_P = \omega_S + \omega_I
+\qquad \Longrightarrow \qquad
+\omega_I = 2\omega_P - \omega_S \\
+\end{equation}
+we obtained the only frequency permitted for $\omega_I$.
 
-Each point was evaluated with the next system:
-\[
-\left\{
-	\begin{array}{rl}
-		\omega_I		&= 2\omega_P - \omega_S \\
-		\\
-		\Delta k		&= \beta_S + \beta_I - 2\beta_P \\
-					&= \frac{2\pi}{\lambda_S}n_{eff}\left( \omega_s, T \right) + \frac{2\pi}{\lambda_I}n_{eff}\left( \omega_I, T \right) - 2\frac{2\pi}{\lambda_P}n_{eff}\left( \omega_P, T \right)
-	\end{array}
-\right.
-\]
-Imposing the conservation of energy, we obtained the only frequency permitted for $\omega_I$.
-We replaced its value in the conservation of momentum formula, giving us the phase mismatch as a function of signal wavelength and temperature, for each set of orders.
+We replaced its value in the conservation of momentum formula, giving us the phase mismatch as a function only of signal wavelength and temperature of the heater, for each set of orders.
+
+Then, starting from the fits of the effective index at different wavelengths and temperatures, we evaluated the phase mismatch of all sets.
+The evaluation was made on a grid of temperature and signal wavelength arbitrarily dense.
 
@@
 
+\section{Results}
 \section{Conclusions}
 \subsection{Improvements}
-\subsection{Results}
+\subsection{Summary}
 

### 2015-09-20 latex/article.tex
almost there

@@
 \usepackage{multirow}
+
+\usepackage{caption}		% to use subfigure
+\usepackage{subcaption}
 
@@
 	\includegraphics[width=.5\textwidth]{2Dmodes.png}
+	\caption{graphical rapresentation of field distribution of 2D modes}
 	\label{fig_2dmodes}
-	\caption{graphical rapresentation of field distribution of 2D modes}
 \end{figure}
@@
 
+\subsubsection{Coupled amplitude equations}
+
 Replacing Eq.
-(\ref{eq_P}) in Helmholtz equation (\ref{eq_helm_P}) leads to eight coupled equations: four of them are equivalent of Eq.
+(\ref{eq_P}) in the Helmholtz equation (\ref{eq_helm_P}) leads to eight coupled equations: four of them are equivalent of Eq.
 (\ref{eq_wg_a}) and describe the field distribution of the mode of each wave.
@@
 
-\subsubsection*{Approximate solution}
+\subsubsection{Approximate solution}
 The previous equations are quite general (they include SPM, XPM in addition to FWM) and require a numerical approach to be solved exactly.
@@
 
-\section{Computational models}
+\section{Computational model}
 To understand the behaviour of the waveguide, it is necessary to first know how waves of different frequency are transmitted through the waveguide.
@@
 	\centering
-	\includegraphics[width=.55\textwidth]{geometry.png}
+	\includegraphics[width=1\textwidth]{geometry.pdf}
 	\label{fig_wg_Section}
@@
 The cladding was set to be silica (SiO2) and coated the top of the core with a thickness of \SI{.35}{\um}.
-For both materials was defined a refractive index dependent on the wavelength $n=n(\lambda)$, as given by the empirical relationship called \textit{Sellmeier equation}.
+For both materials was defined a refractive index dependent on the wavelength $n=n(\lambda)$, as given by the empirical relationship called \textit{Sellmeier equation}:
 \begin{equation}
@@
 
-We positioned a thermal reservoir, a ``\textit{heater}", \SI{0.3}{\um} wide at the top of the cladding, exactly over the center of the waveguide core and set to mantain a specific temperature in the gap, given by the configuration chosen.
+We positioned a thermal reservoir, a ``\textit{heater}", \SI{0.3}{\um} wide at the top of the cladding, exactly over the center of the waveguide core and set to mantain a specific temperature $T_H$ in the gap $[\SI{293.15}{\K} - \SI{693.15}{\K}]$, given by the configuration chosen.
 To 
@@
     	\multirow{2}{*}{Materials}    & $\rho$ & $\kappa_{TH}$ & $C_P$ & TOC\\
-  		& [\si{\kg\m^3}] & [\si{\W\per\m\per\K}] & [\si{\J\per\kg\per\K}] & [\si{\per\K}] \\
+  		& [\si{\kg\m^3}] & [\si{\W\per(\m\K)}] & [\si{\J\per(\kg\K)}] & [\si{\per\K}] \\
     \midrule
@@
 where $\mathrm{TOC}|_{\mathrm{Si}} = \SI{1.87e-4}{\per\K}$\cite{n_db} is called Termo-Optic Coefficient.
-The coefficient of silica glass is negligible and coefficient was therefore considered zero $\mathrm{TOC}|_{\mathrm{SiO}_2} \approx 0$.
+The coefficient of silica glass is negligible and therefore was considered zero $\mathrm{TOC}|_{\mathrm{SiO}_2} \approx 0$.
 
@@
 
+It was necessary to set the boundary conditions: the two sides (left, right) and the bottom the condition were considered as thermal reservoirs with a temperature $T = T_{amb} = \SI{293.15}{\K}$.
+The top was, instead, split into three sections: the heater, as we explained before, and the remaining two parts.
+Those were set to have a convective heat flux with air at ambient temperature.
+Silica heat transfer coefficient was set to $\mathrm{HTC}_{\mathrm{SiO}_2} = \SI{5}{\W\per(\m^2\K)}$.
+
+It is important to note that the value of the heat transfer coefficient can vary a lot depending on the air motion.
+We considered the typical laboratory condition.
+
 \paragraph{EM mode analysis}
@@
 
-We emploied an automated algorithm to solve, in the frequency domain, the Helmholtz equation on a fine grid in the waveguide section.
+We employed an automated algorithm to solve, in the frequency domain, the Helmholtz equation on a fine grid in the waveguide section.
 Each point of evaluation took into account the effective index of the material, slightly changed by the local temperature obtained by the stationary solution.
+
+As in the stationary solution of the heat transfer, we needed the boundary conditions.
+We set all four sides (top, bottom, left, right) to ``\texttt{scattering boundary condition}", that is a condition where the boundary is completely transparent to scattered waves.
+That means that the core and cladding is isolated from the outside. \ref{}
 
@@
 Starting from raw data consisting of the effective index for each parametric configuration, we fitted them with a polinomial function of frequency $\omega = 2\pi \nu$ or $\lambda$ and temperature $T$, obtaining:
-$$n_{eff} = f_{mt,\,mo} \left( \omega, T \right) = f'_{mt,\,mo} \left( \lambda, T \right)$$
+$$n_{eff} = f_{mt,\,mo} \left( \omega, T_H \right) = f'_{mt,\,mo} \left( \lambda, T_H \right)$$
 where $mt$ and $mo$ means respectively \textit{mode type} (TE or TM) and \textit{mode order} (1, 2, 3, ...)
@@
 
-We replaced its value in the conservation of momentum formula, giving us the phase mismatch as a function only of signal wavelength and temperature of the heater, for each set of orders.
+We replaced its value in the conservation of momentum formula, giving us the phase mismatch as a function of signal wavelength and temperature of the heater only, for each set of orders.
 
@@
 The critical parameter on which the choice was based on is the coherence length: only those sets which had a maximum value of coherence length greater than a supposed sample length $L_{sam} = $\SI{1}{\cm} was chosen.
-$$L_{coh} = \frac{2\pi}{|\Delta k|} \geq L_{sam}$$
+\begin{equation}
+	L_{coh} = \frac{2\pi}{|\Delta k|} \geq L_{sam}
+	\label{eq_lcoh_crit}
+\end{equation}
 Again, we had a list of the only combination interesting for our purpose.
@@
 
-\subsubsection{Data aggregation}
-After the selection of sets, we evaluated the dependence of each maximum on temperature.
+\subsection{Data analysis}
+We studied the value of $L_{coh}$ of the selected configurations with a rough analysis of 3D plots of $L_{coh}(\lambda,T_{H})$.
+We observed the presence of different (mainly one or two) peaks in wavelength wich were almost conserved in the temperature shift.
+
+Given the definition of function $L_{coh}$, it value should technically diverge in the proximity of phase-match condition.
+However, we evaluated the function on a discrete grid.
+Thus we had, as a matter of fact, a very peaked function of wavelength most of the time.
+An example is given in Figure (\ref{fig_peaks}).
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.75\textwidth]{delta_example.png}
+	\caption{Example of $L_{coh}$ at $T_H$ fixed.}
+	\label{fig_peaks}
+\end{figure}
+
+We could therefore find the local maxima of such function and assume they are the centers of the peaks.
+If their position change significally while shifting the temperature, it means we are able to control the phase-match condition.
+
+Another important parameter is the width of the peak: to be consistent with the seletion criteria used in (\ref{eq_lcoh_crit}), we defined the bandwidth as the peak width at $L_{coh} = 1$.
+
+We obtained graphs representing the position and the bandwidth of peaks vs temperature of each solution, as shown if Figure (\ref{fig_examples}).
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width=1\textwidth]{ex_pos.png}
+		\caption{Example of peaks vs $T_H$.}
+		\label{fig_example_position}
+	\end{subfigure}\hspace{.05\textwidth}
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width=1\textwidth]{ex_bw.png}
+		\caption{Example of bandwidth vs $T_H$.}
+		\label{fig_example_bandwidth}
+	\end{subfigure}
+	\caption{Examples of peaks position and bandwidth dependence on temperature $T_H$}
+	\label{fig_examples}
+\end{figure}
+
+\section{Results}
+\subsubsection{data aggregation}
+Examining the graphs obtained from the data analysis of the symmetric configuration, we noticed that for each solution selected were one or two straight lines.
+Therefore we summarized them by collecting the slopes and the value of the functions at ambient temperature.
+
+The next Figures (\ref{fig_sym_pp}) and (\ref{fig_sym_bw}) show the results obtained, excluding the sets which only phasematch was at $\lambda = \SI{1.55}{\um}$
+
+\begin{figure}[h!]
+	\centering
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width=1\textwidth]{ppaat2.pdf}
+		\label{fig_sym_pp@t2} 	% pp@t = bandwidth @ T_amb,
+								% 2 = no points at 1.55um
+		\caption{Example of peaks vs $T_H$.}
+	\end{subfigure}\hspace{.05\textwidth}
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width=1\textwidth]{ppc2.pdf}
+		\label{fig_sym_ppc2} % ppc = bandwidth change
+		\caption{Example of bandwidth vs $T_H$.}
+	\end{subfigure}
+	\caption{Peak position summary}
+	\label{fig_sym_pp}
+\end{figure}
+
+\begin{figure}[h!]
+	\centering
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width=1\textwidth]{baat2.pdf}
+		\label{fig_sym_b@t2} % b@t = bandwidth @ T_amb
+		\caption{Example of peaks vs $T_H$.}
+	\end{subfigure}\hspace{.05\textwidth}
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width=1\textwidth]{bc2.pdf}
+		\label{fig_sym_bc2} % bc = bandwidth change
+		\caption{Example of bandwidth vs $T_H$.}
+	\end{subfigure}
+	\caption{Bandwidth summary}
+	\label{fig_sym_bw}
+\end{figure}
 
@@
 This operation was intended to increase the difference of behaviour between low and high orders enabling thus the creation of new peaks in the coherence length.
-\subsection{Different geometries}
 
-\section{Results}
+The new geometry is represented in Figure (\ref{fig_geometry_asym}).
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=1\textwidth]{geometry2.pdf}
+	\caption{Scheme of the side heater configuration.}
+	\label{fig_geometry_asym}
+\end{figure}
+
+\subsubsection{data aggregation}
+Examining the graphs obtained from the data analysis of the asymmetric configuration, we noticed variety of different situation.
+Therefore we could not anymore summarize the results with slopes an value at $T_{amb}$.
+
 \section{Conclusions}
 \subsection{Improvements}
+
+There are a few improvements which were not introduced in our study because of the limited time available.
+They could be eventually implemented in an extended study of the very same topic.
+
+A rough list of them is proposed next:
+\begin{itemize}
+\item	The heater should be simulated as a metal conductor media, instead of a simple boundary condition, in addition to its thermal reservoir property.
+This is necessary because a metal plaque over the waveguide core could interfere with the wave propagation in the waveguide, drawing energy from the EM wave.
+
+\item	It should be considered the thermal expansion of materials.
+The thermal expansion coefficients of both silicon and silica are small but, on the other hand, the temperature change is quite high.
+It should not easily considered as negligible contribution as it could change the waveguide geometry and therefore the modes.
+
+\item	The aim of this study was to understand if it was possible at all to control FWM with temperature.
+It is important also to develop the correlation between temperature and efficiency of energy conversion from the pump to the idler.
+
+\item	As next step in enhancing the influence of temperature on effective index, different core geometries could be studied.
+This could greatly condition the wave propagation, but is also a difficult problem with many degrees of freedom.
+
+\end{itemize}
+
 \subsection{Summary}

### 2015-09-20 gitcode/phase-matching/single_combination.m

@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 1001;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 10001;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -73,7 +73,7 @@ for ww=1:pm.n_sample_wl
 end
 
 % sampling temperature
-pm.n_sample_t = 1001;
+pm.n_sample_t = 201;
 pm.step_t = (vec.temp(end) - vec.temp(1) )/(pm.n_sample_t - 1);
 
 vec.sample_temp = zeros(pm.n_sample_t,1);
@@ -316,7 +316,7 @@ tic
 
 f = figure(1);
 axes1 = axes('Parent',f);
-mesh(wlen_grid, temp_grid, f_Lcoh(wlen_grid, temp_grid));
+mesh(wlen_grid, temp_grid, f_Lcoh(wlen_grid, temp_grid) );
 hold(axes1,'on');
 zlim(axes1,[0.1 2]);
 
@@ -330,7 +330,7 @@ tic
 
 f = figure(2);
 axes1 = axes('Parent',f);
-contour(1.1>f_Lcoh(wlen_grid, temp_grid)>=1);
+contourf(1.1>f_Lcoh(wlen_grid, temp_grid));
 toc
 
 %% 2D plots of center & bandwidth

### 2015-09-20 latex/article.tex
100 factor!

@@
 
+Significant FWM occurs only if the phase match nearly vanishes.
+This require the matching of frequencies as well as of the wave vectors.
+Thus the phase-matching condition requires a specific choice of input wavelengths and media parameters before FWM can occur with high efficiency.
+
+From the definition of $\phi_-$ and $\phi_+$ we can gather that there are two types of FWM.
+The term containing $\phi_-$ correspond to the case in which two photons at frequencies $\omega_1$ and $\omega_2$ are annihilated, while two photons at frequencies $\omega_3$ and $\omega_4$ are created simultaneously.
+On the other hand, the term containing $\phi_+$ correspond to the case in which three photons at frequencies $\omega_1$, $\omega_2$ and $\omega_3$ are annihilated, while one photon at frequency $\omega_4$ is created.
+
+Our study focuses on a special condition of the second case, where $\omega_1 = \omega_2 = \omega_P$.
+The setup is therefore consist of a strong pump of frequency  $\omega_P$ and a signal of frequency  $\omega_3 = \omega_S$, resulting in the creation of the idler wave of frequency $\omega_4 = \omega_I$.
+The condition of frequency and phase matching are therefore:
+\begin{equation}
+\left\{
+ 	\begin{aligned}
+		\omega_I &= 2\omega_P - \omega_S \\
+		\Delta k &= 2\beta_P - \beta_S - \beta_I = 0
+	\end{aligned}
+\right.
+\label{eq_f&pmc}
+\end{equation} %frequency & phase matching conditions
+
 \subsubsection{Coupled amplitude equations}
@@
 
-\vspace{18pt}
-************************************************************************
-\vspace{12pt}
+The solution that we have developed so far is valid only when the pump waves remain largely undepleted.
+For a solution that includes pump depletion it is necessary to solve exactly the complete set of four equations, Eqs (\ref{eq_coupled_amplitude_a} - \ref{eq_coupled_amplitude_d}).
 
-****		è necessario verificare conservazione di energia e momento
-\vspace{12pt}
+We made a further assumption, that is that $\kappa = \Delta k + \gamma(P_1 + P_2) \approx \Delta k$, since $\Delta \gg \gamma(P_1 + P_2)$ almost always.
+In order to be efficient, the parametric process needs to verify both the conservation of energy and momentum, as given in Eq. (\ref{eq_f&pmc}).
 
-In order to be efficient, the parametric process needs to verify both the conservation of energy and momentum.
-$$\omega_1 + \omega_2 = \omega_3 + \omega_4$$
-$$\Delta k = \beta_3 + \beta_4 - \beta_1 - \beta_2$$
-****
-$$\Omega_S = \omega_1 + \omega_3 = \omega_4 - \omega_1$$
-where we assume $\omega_3 < \omega_4$.
-$$\Omega_S = |\omega_P - \omega_I| = |\omega_S - \omega_P|$$
-
-We can define a length scale, known as the coherence length, using $L_{coh} = 2\pi/|\Delta\kappa|$, where $\Delta\kappa$ is the maximum value of the effective phase mismatch that can be tolerated.
+We can also define a length scale, known as the coherence length, using $L_{coh} = 2\pi/|\Delta\kappa|$, where $\Delta\kappa$ is the maximum value of the effective phase mismatch that can be tolerated.
 Moreover significant FWM occurs if $L_{sam}<L_{coh}$ where $L_{sam}$ is the sample length.
@@
 
-\begin{figure}[ht]
+\begin{figure}[!h]
 	\centering

### 2015-09-20 gitcode/phase-matching/single_combination.m

@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 10001;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 1001;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -304,8 +304,9 @@ i.fi2       = @(xi,t) i.fi(xi,t,i.p00,i.p10,i.p01,i.p20,i.p11,i.p02,i.p30,i.p21,
 
 xp = 1.55e-6;
 
-f_delta = @(xs,t) 2.*pi.*( 2.*p.fp2(xp,t)./xp - s.fs2(xs,t)./xs - i.fi2(2.*xp-xs,t)./(2.*xp-xs) );
-f_Lcoh  = @(xs,t) 2.*pi./abs(f_delta(xs,t));
+f_delta     = @(xs,t) 2.*pi.*( 2.*p.fp2(xp,t)./xp - s.fs2(xs,t)./xs - i.fi2(2.*xp-xs,t)./(2.*xp-xs) );
+f_Lcoh      = @(xs,t) 2.*pi./abs(f_delta(xs,t));
+f_Lcoh_cm   = @(xs,t) 200*pi./abs(f_delta(xs,t));
 
 toc
 
@@ -316,7 +317,7 @@ tic
 
 f = figure(1);
 axes1 = axes('Parent',f);
-mesh(wlen_grid, temp_grid, f_Lcoh(wlen_grid, temp_grid) );
+mesh(wlen_grid, temp_grid, f_Lcoh_cm(wlen_grid, temp_grid) );
 hold(axes1,'on');
 zlim(axes1,[0.1 2]);
 
@@ -330,7 +331,15 @@ tic
 
 f = figure(2);
 axes1 = axes('Parent',f);
-contourf(1.1>f_Lcoh(wlen_grid, temp_grid));
+contourf(f_Lcoh_cm(wlen_grid, temp_grid)>=1);
+toc
+
+tic
+[wlen_grid, temp_grid]  = meshgrid(vec.sample_wlen, vec.sample_temp);
+
+f = figure(3);
+axes1 = axes('Parent',f);
[…]

### 2015-09-20 gitcode/phase-matching/phasematching_v3.m
peaks & bws

@@ -333,11 +333,11 @@ for rr=1:pm.n_results;
                 maxL = max([maxL, length(locs)]);
                 y(tt, 1:length(locs)) = vec.sample_wlen(locs);
                 
-                zData_0 = zData;
-                zData_0(1,tt) = 0;
-                zData_0(end,tt) = 0;
+                zData_0 = zData(:,tt);
+                zData_0(1) = 0;
+                zData_0(end) = 0;
                 
-                a = zData_0(:,tt) >= 1;
+                a = zData_0(:) >= 1;
                 b = abs( diff(a) );
                 c = find(b == 1);
                 %d = vec.sample_wlen( c );

### 2015-09-20 gitcode/phase-matching/single_combination.m

@@ -73,7 +73,7 @@ for ww=1:pm.n_sample_wl
 end
 
 % sampling temperature
-pm.n_sample_t = 201;
+pm.n_sample_t = 501;
 pm.step_t = (vec.temp(end) - vec.temp(1) )/(pm.n_sample_t - 1);
 
 vec.sample_temp = zeros(pm.n_sample_t,1);
@@ -220,7 +220,7 @@ if ~overwrite
         end
     end
     
-    clear check str order TE
+    clear check str order TE ss ii pp
 else
     % overwrite here
     TE      = true;
@@ -255,6 +255,8 @@ p.fit   = data.fit_neff( ww, hh, pm.comb(1,1), pm.comb(2,1)).fit;
 s.fit   = data.fit_neff( ww, hh, pm.comb(1,2), pm.comb(2,2)).fit;
 i.fit   = data.fit_neff( ww, hh, pm.comb(1,3), pm.comb(2,3)).fit;
 
+clear ww hh
+
 % get coefficients
 cn = cell2mat( coeffnames(p.fit) );
 cv = coeffvalues(p.fit);
@@ -273,6 +275,8 @@ cv = coeffvalues(i.fit);
 for jj=1:length(cv)
     eval([ 'i.', cn(jj,:), '= cv(jj);']);
 end
+
+clear jj cv cn
 
 % get formulas
 p.fstr      = formula(p.fit);
@@ -322,7 +326,7 @@ hold(axes1,'on');
 zlim(axes1,[0.1 2]);
 
 toc
-clear wlen_grid temp_grid
+clear wlen_grid temp_grid axes1 f
 
 %% 2D contour plots
 
@@ -335,14 +339,61 @@ contourf(f_Lcoh_cm(wlen_grid, temp_grid)>=1);
 toc
 
 tic
-[wlen_grid, temp_grid]  = meshgrid(vec.sample_wlen, vec.sample_temp);
-
 f = figure(3);
 axes1 = axes('Parent',f);
 contour(f_Lcoh_cm(wlen_grid, temp_grid)>=1);
 toc
 
+clear wlen_grid temp_grid axes1 f
+
 %% 2D plots of center & bandwidth
+
+tic
+[wlen_grid, temp_grid]  = meshgrid(vec.sample_wlen, vec.sample_temp);
+
+x       = temp_grid;
+y       = wlen_grid;
[…]

### 2015-09-20 gitcode/phase-matching/single_combination.m
bsym

@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 1001;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 4001;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -176,8 +176,8 @@ toc
 % ex: TE P,S,I = [1, 1, 1; 4,2,6] or TM P,S,I = [2, 2, 2; 5, 3, 1]
 
 tic
-%overwrite = true;
-overwrite = false;
+overwrite = true;
+%overwrite = false;
 
 if ~overwrite
     check = false;
@@ -225,8 +225,8 @@ else
     % overwrite here
     TE      = true;
     %TE      = false;
-    pump    = 5;
-    signal  = 5;
+    pump    = 4;
+    signal  = 3;
     idler   = 5;
     if TE
         pm.comb = [1, 1, 1; pump, signal, idler];
@@ -354,65 +354,119 @@ tic
 x       = temp_grid;
 y       = wlen_grid;
 z       = f_Lcoh_cm(wlen_grid, temp_grid);
-bool_z  = z(:,:) >=1;
 
 peaks   = zeros(pm.n_sample_t, 30).*NaN; %idivide(int32(pm.n_sample_wl),int32(2)) ).*NaN;
 bws     = zeros(pm.n_sample_t, 30).*NaN;
 
 maxL = 0;
 for tt=1:pm.n_sample_t
-	[~, locs]   = findpeaks(z(tt,:),'MinPeakHeight',1);
+    zv          = z(tt,:)';
+	[~, locs]   = findpeaks(zv,'MinPeakHeight',1);
     n_peaks     = length(locs);
-    peaks(tt,1:n_peaks) = locs;
+    peaks(tt,1:n_peaks) = vec.sample_wlen(locs);
     
-    maxL = max(maxL,n_peaks);
+    maxL = max([maxL,n_peaks]);
     
-    a   = bool_z(tt,:);
+    zv0      = zv;
+    zv0(1)   = 0;
+    zv0(end) = 0;
     
-    clear locs n_peaks
+    a   = zv0 >= 1;
+    b   = abs(diff(a));
[…]

### 2015-09-20 latex/article.tex
geometries

@@
 I discussed different topics with the professors and some researchers.
-One of the researcher, who would later become my advisor, suggested me a few interesting topics in guided-wave optics which could be studied as a undergraduate thesis.
+One of the researchers, who would later become my advisor, suggested me a few interesting topics in guided-wave optics which could be studied as a undergraduate thesis.
 
@@
 
-The general solution of Eq. (\ref{eq_helm_P}) is a transverse electromagnetic (TEM) wave, which electric and magnetic fields are perpendicular to the propagation direction.
+The general solution of Eq. (\ref{eq_helm_P}) is a transverse electromagnetic (TEM) wave, whose electric and magnetic fields are perpendicular to the propagation direction.
 Without losing generality, we could assume $\hat{z}$ as the propagation direction and electric field of the form:
@@
 Significant FWM occurs only if the phase match nearly vanishes.
-This require the matching of frequencies as well as of the wave vectors.
+This requires the matching of frequencies as well as of the wave vectors.
 Thus the phase-matching condition requires a specific choice of input wavelengths and media parameters before FWM can occur with high efficiency.
@@
 From the definition of $\phi_-$ and $\phi_+$ we can gather that there are two types of FWM.
-The term containing $\phi_-$ correspond to the case in which two photons at frequencies $\omega_1$ and $\omega_2$ are annihilated, while two photons at frequencies $\omega_3$ and $\omega_4$ are created simultaneously.
+The term containing $\phi_-$ corresponds to the case in which two photons at frequencies $\omega_1$ and $\omega_2$ are annihilated, while two photons at frequencies $\omega_3$ and $\omega_4$ are created simultaneously.
 On the other hand, the term containing $\phi_+$ correspond to the case in which three photons at frequencies $\omega_1$, $\omega_2$ and $\omega_3$ are annihilated, while one photon at frequency $\omega_4$ is created.
@@
 Our study focuses on a special condition of the second case, where $\omega_1 = \omega_2 = \omega_P$.
-The setup is therefore consist of a strong pump of frequency  $\omega_P$ and a signal of frequency  $\omega_3 = \omega_S$, resulting in the creation of the idler wave of frequency $\omega_4 = \omega_I$.
+The setup therefore consists of a strong pump of frequency  $\omega_P$ and a signal of frequency  $\omega_3 = \omega_S$, resulting in the creation of the idler wave of frequency $\omega_4 = \omega_I$.
 The condition of frequency and phase matching are therefore:
@@
 (\ref{eq_wg_a}) and describe the field distribution of the mode of each wave.
-The remaining four are the equivalent of Eq. (\ref{eq_wg_b}) and describe how the field change while travelling through the waveguide.
+The remaining four are the equivalent of Eq. (\ref{eq_wg_b}) and describe how the fields change while travelling through the waveguide.
 Those, considering $E_j(\textbf{r}) = F_j(x,y)A_j(z)$ where $F_j$ is the spatial distribution of the mode, can be written as:
@@
 We made a further assumption, that is that $\kappa = \Delta k + \gamma(P_1 + P_2) \approx \Delta k$, since $\Delta \gg \gamma(P_1 + P_2)$ almost always.
-In order to be efficient, the parametric process needs to verify both the conservation of energy and momentum, as given in Eq. (\ref{eq_f&pmc}).
+In order to be efficient, the parametric process needs to verify the conservation of both energy and momentum, as given in Eq. (\ref{eq_f&pmc}).
 
@@
 \section{Computational model}
-To understand the behaviour of the waveguide, it is necessary to first know how waves of different frequency are transmitted through the waveguide.
+To understand the behaviour of the waveguide, it is first necessary to know how waves of different frequencies are transmitted through the waveguide.
 We chose to simulate the modes with temperature and frequency as a parameters.
@@
 We positioned a thermal reservoir, a ``\textit{heater}", \SI{0.3}{\um} wide at the top of the cladding, exactly over the center of the waveguide core and set to mantain a specific temperature $T_H$ in the gap $[\SI{293.15}{\K} - \SI{693.15}{\K}]$, given by the configuration chosen.
-To 
+To **** 
 define the density $\rho$ in [\si{\kg\m^3}], the thermal conductivity $\kappa_{TH}$ in [\si{\W\per\m\per\K}] and the heat capacity $C_P$ in [\si{\J\per\kg\per\K}] of the different materials.
@@
 \subsubsection{Numerical solution}
-Because the degree of freedom of the problem were too many, we resorted to automated algorithms which gave us a numerical, and therefore approximate, solution.
+Because the degrees of freedom of the problem were too many, we resorted to automated algorithms which gave us a numerical, and therefore approximate, solution.
 
@@
 
-It was necessary to set the boundary conditions: the two sides (left, right) and the bottom the condition were considered as thermal reservoirs with a temperature $T = T_{amb} = \SI{293.15}{\K}$.
+It was necessary to set the boundary conditions: the two sides (left, right) and the bottom were considered as thermal reservoirs with a temperature $T = T_{amb} = \SI{293.15}{\K}$.
 The top was, instead, split into three sections: the heater, as we explained before, and the remaining two parts.
@@
 As in the stationary solution of the heat transfer, we needed the boundary conditions.
-We set all four sides (top, bottom, left, right) to ``\texttt{scattering boundary condition}", that is a condition where the boundary is completely transparent to scattered waves.
+We set all four sides (top, bottom, left, right) to ``\texttt{scattering boundary condition}", which is a condition where the boundary is completely transparent to scattered waves.
 That means that the core and cladding is isolated from the outside. \ref{}
@@
 \end{equation}
-Again, we had a list of the only combination interesting for our purpose.
+Again, we obtained a list containing only the combinations interesting for our purpose.
 
-It is important to note that, in general, each combination could have more that one maximum of coherence length $L_{coh}$ in wavelength for each temperature value.
+It is important to note that, in general, each combination could have more than one maximum of coherence length $L_{coh}$ in wavelength for each temperature value.
 
@@
 We studied the value of $L_{coh}$ of the selected configurations with a rough analysis of 3D plots of $L_{coh}(\lambda,T_{H})$.
-We observed the presence of different (mainly one or two) peaks in wavelength wich were almost conserved in the temperature shift.
+We observed the presence of different (mainly one or two) peaks in wavelength which were almost conserved in the temperature shift.
 
-Given the definition of function $L_{coh}$, it value should technically diverge in the proximity of phase-match condition.
+Given the definition of function $L_{coh}$, its value should technically diverge in the proximity of phase-match condition.
 However, we evaluated the function on a discrete grid.
@@
 \subsubsection{data aggregation}
-Examining the graphs obtained from the data analysis of the symmetric configuration, we noticed that for each solution selected were one or two straight lines.
+Examining the graphs obtained from the data analysis of the symmetric configuration, we noticed that for each solution selected there were one or two straight lines.
 Therefore we summarized them by collecting the slopes and the value of the functions at ambient temperature.
@@
 								% 2 = no points at 1.55um
-		\caption{Example of peaks vs $T_H$.}
+		\caption{Peaks position at $T_{amb}$.}
 	\end{subfigure}\hspace{.05\textwidth}
@@
 		\label{fig_sym_ppc2} % ppc = bandwidth change
-		\caption{Example of bandwidth vs $T_H$.}
+		\caption{Change of peak position.}
 	\end{subfigure}
@@
 		\label{fig_sym_b@t2} % b@t = bandwidth @ T_amb
-		\caption{Example of peaks vs $T_H$.}
+		\caption{Bandwidth at $T_{amb}$.}
 	\end{subfigure}\hspace{.05\textwidth}
@@
 		\label{fig_sym_bc2} % bc = bandwidth change
-		\caption{Example of bandwidth vs $T_H$.}
+		\caption{Change of bandwidth.}
 	\end{subfigure}
@@
 	\centering
-	\includegraphics[width=1\textwidth]{geometry2.pdf}
+	\includegraphics[width=1\textwidth]{geometryA.pdf}
 	\caption{Scheme of the side heater configuration.}
@@
 \subsubsection{data aggregation}
-Examining the graphs obtained from the data analysis of the asymmetric configuration, we noticed variety of different situation.
-Therefore we could not anymore summarize the results with slopes an value at $T_{amb}$.
+Examining the graphs obtained from the data analysis of the asymmetric configuration, we noticed a variety of different situations.
+Therefore we could not summarize the results with slopes and value at $T_{amb}$ anymore.
 
@@
 \item	The heater should be simulated as a metal conductor media, instead of a simple boundary condition, in addition to its thermal reservoir property.
-This is necessary because a metal plaque over the waveguide core could interfere with the wave propagation in the waveguide, drawing energy from the EM wave.
+This is necessary because a metal plaque over the waveguide core could interfere with the wave propagation in the waveguide itself, drawing energy from the EM wave.
 
@@
 The thermal expansion coefficients of both silicon and silica are small but, on the other hand, the temperature change is quite high.
-It should not easily considered as negligible contribution as it could change the waveguide geometry and therefore the modes.
+It should not be easily considered as negligible contribution as it could change the waveguide geometry and therefore the modes.
 
 \item	The aim of this study was to understand if it was possible at all to control FWM with temperature.
-It is important also to develop the correlation between temperature and efficiency of energy conversion from the pump to the idler.
+It is also important to develop the correlation between temperature and efficiency of energy conversion from the pump to the idler.
 
 \item	As next step in enhancing the influence of temperature on effective index, different core geometries could be studied.
-This could greatly condition the wave propagation, but is also a difficult problem with many degrees of freedom.
+This could greatly condition the wave propagation, but it is also a difficult problem with many degrees of freedom.
 

### 2015-09-21 latex/article.tex
images and problems

@@
 \usepackage{subcaption}
+
+\usepackage{svg}			% to include svgs
 
@@
 	\label{eq_wg_a} \\
-	\frac{\partial^2\tilde{A}(z,\omega)}{\partial z^2} +2\mathrm{i}\beta\frac{\partial \tilde{A}(z,\omega)}{\partial z} +3n^2k_0^2\tilde{A}(z,\omega) = 0
+	\frac{\partial^2\tilde{A}(z,\omega)}{\partial z^2} +2\mathrm{i}\beta\frac{\partial \tilde{A}(z,\omega)}{\partial z} -n^2k_0^2\tilde{A}(z,\omega) = 0
 	\quad ! \neq ! \quad
@@
 
-The second equation (\ref{eq_wg_b}), on the other hand, define the change of field distribution along the $\hat{z}$ axis, or the waveguide axis.
+The second equation (\ref{eq_wg_b}), on the other hand, defines the change of field distribution along the $\hat{z}$ axis, or the waveguide axis.
 Imposing to this equation to be zero means that we force the field distribution $F$ not to change.
@@
 \subsection{Data processing}
+We focused on the information given by the effective index.
 
@@
 
-We obtained graphs representing the position and the bandwidth of peaks vs temperature of each solution, as shown if Figure (\ref{fig_examples}).
+We obtained graphs representing the position and the bandwidth of peaks vs temperature of each solution, as shown in Figures (\ref{fig_example_position}) and (\ref{fig_example_bandwidth}).
 
@@
 	\centering
-	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[width=1\textwidth]{ex_pos.png}
+	\includegraphics[width=.75\textwidth]{ex_pos.png}
 	\caption{Example of peaks vs $T_H$.}
 	\label{fig_example_position}
-	\end{subfigure}\hspace{.05\textwidth}
-	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[width=1\textwidth]{ex_bw.png}
+\end{figure}
+\begin{figure}[!h]
+	\centering
+%	\includegraphics[scale=1]{ex_bw.png}
+	\includegraphics[width=.75\textwidth]{ex_bw.png}
 	\caption{Example of bandwidth vs $T_H$.}
 	\label{fig_example_bandwidth}
-	\end{subfigure}
-	\caption{Examples of peaks position and bandwidth dependence on temperature $T_H$}
-	\label{fig_examples}
 \end{figure}
+
+%\begin{figure}[!h]
+%	\centering
+%	\begin{subfigure}[b]{0.45\textwidth}
+%		\includegraphics[width=1\textwidth]{ex_pos.png}
+%		\caption{Example of peaks vs $T_H$.}
+%		\label{fig_example_position}
+%	\end{subfigure}%\hspace{.02\textwidth}
+%	\begin{subfigure}[b]{0.45\textwidth}
+%		\includegraphics[width=1\textwidth]{ex_bw.png}
+%		\caption{Example of bandwidth vs $T_H$.}
+%		\label{fig_example_bandwidth}
+%	\end{subfigure}
+%	\caption{Examples of peaks position and bandwidth dependence on temperature $T_H$}
+%	\label{fig_examples}
+%\end{figure}
 
@@
 
-The next Figures (\ref{fig_sym_pp}) and (\ref{fig_sym_bw}) show the results obtained, excluding the sets which only phasematch was at $\lambda = \SI{1.55}{\um}$
+%The next Figures (\ref{fig_sym_pp}) and (\ref{fig_sym_bw}) show the results obtained, excluding the sets which only phasematch was at $\lambda = \SI{1.55}{\um}$
 

### 2015-09-21 gitcode/phase-matching/phasematching_v3.m

@@ -413,7 +413,7 @@ end
 results.indexes = find(results.indexes == 1);
 results.n_final = length(results.indexes);
 toc
-%%
+
 clear ans xGrid yGrid zdata zData rr jj tt y y2 maxL locs bw fitresult f name subplot1 subplot2 top
 
 %% 2D plots data vs orders

### 2015-09-21 gitcode/phase-matching/problem.m

@@ -1,0 +1,33 @@
+%% problem
+
+% carico quello simmetrico
+[ans1, ans2] = uigetfile({'../data/*.mat'});     % choose file to load
+load( strcat(ans2, ans1) );
+sym     = data;
+fprintf(['File ', ans1, ' loaded.\n']);
+
+% carico quello asimmetrico
+[ans1, ans2] = uigetfile({'../data/*.mat'});     % choose file to load
+load( strcat(ans2, ans1) );
+symA    = data;
+fprintf(['File ', ans1, ' loaded.\n']);
+
+% carico quello bisimmetrico
+[ans1, ans2] = uigetfile({'../data/*.mat'});     % choose file to load
+load( strcat(ans2, ans1) );
+symB    = data;
+fprintf(['File ', ans1, ' loaded.\n']);
+
+clear data ans1 ans2
+
+% create matrix @ T_amb for TE only, all orders, all
+Msym = squeeze(sym.neff(:,1,1,1,1,:));
+MsymA = squeeze(symA.neff(:,1,1,1,1,:));
+MsymB = squeeze(symB.neff(:,1,1,1,1,:));
+
+% sym vs asym
+SvsA = Msym - MsymA;
+% sym vs bsym
+SvsB = Msym - MsymB;
+% asym vs bsym
+AvsB = MsymA - MsymB;

### 2015-09-21 gitcode/phase-matching/single_combination.m

@@ -225,9 +225,9 @@ else
     % overwrite here
     TE      = true;
     %TE      = false;
-    pump    = 4;
-    signal  = 3;
-    idler   = 5;
+    pump    = 2;
+    signal  = 1;
+    idler   = 3;
     if TE
         pm.comb = [1, 1, 1; pump, signal, idler];
     else
@@ -470,3 +470,47 @@ title(name);
 toc
 
 clear TE name
+
+%%  import  sym, sol 213, and print L_coh [cm] (λ) @ T_amb = 293.15
+%{
+[wlen_grid, temp_grid]  = meshgrid(vec.sample_wlen, vec.sample_temp);
+
+f = figure('name', 'sol27 213 sym');
+axes1 = axes('Parent',f);
+hold(axes1,'on');
+plot(vec.sample_wlen,f_Lcoh_cm(wlen_grid(1,:), temp_grid(1,:)) )
+ylim([0 2]);
+xlabel({'\lambda [\mum]'});
+ylabel({'L_{coh} [cm]'});
+title('L_{coh}(\lambda) at T_H = T_{amb} = 293.15 K');
+plot(vec.sample_wlen, ones(pm.n_sample_wl,1), '--')
+%}
+%%  import asym, sol 213, and print L_coh [cm] (λ) @ T_amb = 293.15
+%{
+
+[wlen_grid, temp_grid]  = meshgrid(vec.sample_wlen, vec.sample_temp);
+
+f = figure('name', 'sol27 213 asym');
+axes1 = axes('Parent',f);
+hold(axes1,'on');
+plot(vec.sample_wlen,f_Lcoh_cm(wlen_grid(1,:), temp_grid(1,:)) )
+ylim([0 2]);
+xlabel({'\lambda [\mum]'});
+ylabel({'L_{coh} [cm]'});
+title('L_{coh}(\lambda) at T_H = T_{amb} = 293.15 K');
+plot(vec.sample_wlen, ones(pm.n_sample_wl,1), '--')
+%}
+%%  import bsym, sol 213, and print L_coh [cm] (λ) @ T_amb = 293.15
+%{
+[wlen_grid, temp_grid]  = meshgrid(vec.sample_wlen, vec.sample_temp);
+
+f = figure('name', 'sol27 213 bsym');
+axes1 = axes('Parent',f);
+hold(axes1,'on');
[…]

### 2015-09-21 latex/article.tex
sadness

@@
 \subsection{Motivation}
-In my scholastic career I approached the study of optics in an elective course of my third year of undergraduate academic degree.
-I became very interested in the subject, in particular because of the potential developement of photonics for communication and computing.
-I discussed different topics with the professors and some researchers.
-One of the researchers, who would later become my advisor, suggested me a few interesting topics in guided-wave optics which could be studied as a undergraduate thesis.
+In my academic career I first approached the study of optics during an elective course of my third year of undergraduate academic degree.
+I became very interested in the subject, in particular because of the potential developement of photonics for communications and computing.
+I discussed different topics with several professors and researchers.
+One of the researchers, who would later become my advisor, suggested me a few interesting topics in guided-wave optics which could be studied in an undergraduate thesis.
 
 I chose to study the temperature behaviour of silicon waveguides.
-The reason of the choice is that there are always discrepancies between the design of silicon objects and their actual production by the factory.
+The reason of this choice is the constant presence of discrepancies between the design of silicon objects and their actual industrial production.
 The aim of the study is to exploit behaviour of silicon to correct these possible production defects of the materials.
@@
 
-In general FWM implies the mix of four waves of different frequency.
-Partial degenerate FWM, instead, is a specific case in which two waves have the same frequency and are considered as one (pump).
+In general FWM implies the mixing of four waves of different frequencies.
+Partial degenerate FWM, instead, is a specific case where two waves have the same frequency and are considered as one (pump).
 Therefore it is about the pump wave and a second weaker one (signal) which generate a third wave (idler) of frequency different from that of the former two.
@@
 
-Taking the curl of Eq. (\ref{eq_maxwell_a}) and substituting in it Eq. (\ref{eq_maxwell_c}) it leads to the Helmholtz equation:
+Taking the curl of Eq. (\ref{eq_maxwell_a}) and substituting it in Eq. (\ref{eq_maxwell_c}) leads to the Helmholtz equation:
 \begin{equation}
@@
 
-Defining the refractive index $n \equiv \sqrt{\varepsilon_r}$ of the material the previous equation (\ref{eq_helm_P}) and using the definition of \textbf{P} as in Eq. (\ref{eq_P_L})
+Defining the refractive index of the material $n \equiv \sqrt{\varepsilon_r}$ and using the definition of \textbf{P} as in Eq. (\ref{eq_P_L}), the previous Eq. (\ref{eq_helm_P}) becomes
 \begin{equation}
@@
 \end{equation}
-Moreover, $n$ represent the ratio between the speed of light in vacuum and in the material $n = c/v$ and it depends on the frequency of the EM wave.
+Moreover, $n$ represents the ratio between the speed of light in vacuum and in the material ($n = c/v$) and it depends on the frequency of the EM wave.
 
-The general solution of Eq. (\ref{eq_helm_P}) is a transverse electromagnetic (TEM) wave, whose electric and magnetic fields are perpendicular to the propagation direction.
-Without losing generality, we could assume $\hat{z}$ as the propagation direction and electric field of the form:
+The general solution of Eq. (\ref{eq_helm_P}) is a transverse electromagnetic (TEM) wave, whose electric and magnetic fields are perpendicular to the direction of propagation.
+Without losing generality, we could assume $\hat{z}$ as the propagation direction and an electric field of the form:
 \begin{equation}
@@
 with $E$ amplitude of the electric field, $k = 2\pi/\lambda$ the wavevector and $\omega = 2\pi f$ the angular frequency.
-$\lambda$ and $f$ are relatively the wavelength and the frequency of the electromagnetic wave.
+$\lambda$ and $f$ are respectively the wavelength and the frequency of the electromagnetic wave.
 The magnetic field has a similar equation.
@@
 \subsection{Silicon waveguides}
-In linear optics the technology for trasmitting a light wave by confining it in a finite space is the guided-wave optics.
+In linear optics the technology for trasmitting a light wave by confining it in a finite space is called guided-wave optics.
 The instruments employed for achieving such purpose are called waveguides.
@@
 In a ray-optics picture, silicon waveguides are dielectric waveguides and make use of the interface between two media with different refractive index.
-Precisely they exploit the phenomenon of total internal reflection: if a propagating wave reaches a boundary between two mediums, one with higher refractive index ($n_H$) and another with lower refractive index ($n_L$), with an angle of incidence greater than the \textit{critical angle}, then the wave is completely reflected in the first medium.
+They exploit the phenomenon of total internal reflection: if a propagating wave reaches a boundary between two mediums, one with higher refractive index ($n_H$) and another with lower refractive index ($n_L$), with an angle of incidence greater than the \textit{critical angle}, then the wave is completely reflected in the first medium.
 %accorciare la precedente frase%
-Angles are defined relative to the normal vector of the interface and the critical angle can be obtained by the Snell law:
+Angles are defined relative to the normal vector of the interface and the critical angle can be obtained through the Snell's law:
 
@@
 
-Silicon waveguides are composed by core and cladding \textbf{(?)}. %is called cladding only for fiber or also for slab/strip wg?
+Silicon waveguides are composed by core and cladding. %is called cladding only for fiber or also for slab/strip wg?
 The former is the higher refractive index medium in which the wave is confined, the latter is the lower refractive index medium which surrounds the core, thus creating the interface.
-Theoretically the cladding could also be vacuum.
+Theoretically, the cladding could also be vacuum.
 
@@
 The previous equation represents what is called a ``transverse electric" (TE) wave.
-A second family of solution could be acquired by defining the sum of TEM wave with the magnetic field always perpendicular to the propagation direction.
+A second family of solutions could be acquired by defining the sum of TEM waves with the magnetic field always perpendicular to the propagation direction.
 This is called a ``transverse magnetic" (TM) wave.
@@
 
-The second equation (\ref{eq_wg_b}), on the other hand, defines the change of field distribution along the $\hat{z}$ axis, or the waveguide axis.
-Imposing to this equation to be zero means that we force the field distribution $F$ not to change.
-Indeed not all field distributions are transmitted through the waveguide without energy loss \textbf{(?)} and thus without changing $F$.
+The second equation (\ref{eq_wg_b}), on the other hand, defines the change in field distribution along the $\hat{z}$ axis, or the waveguide axis.
+Imposing this equation to be zero means that we force the field distribution $F$ not to change.
+%Indeed not all field distributions are transmitted through the waveguide without energy loss \textbf{(?)} and thus without changing $F$.
 % Modes are fields that maintain the same transverse distribution and polarization at all locations along the waveguide axis.
 Those field distributions which maintain the same transverse distribution and polarization at all locations along the waveguide axis are called modes.
-These modes can be categorized in two main groups, depending on the polarization of the wave: transverse electric (TE) modes and transverse magnetic (TM) modes, which have respectively the electric and magnetic field transverse to the waveguide axis.
+These modes are the eigenfunctions of the system.
+They can be categorized in two main groups, according to the polarization of the wave: transverse electric (TE) modes and transverse magnetic (TM) modes, which have respectively the electric and magnetic field transverse to the waveguide axis.
 
@@
 Higher-order modes travel with smaller propagation constants.
-For a 1D slab waveguide $\beta$ has a simple relation with the bounce angles $\theta_m$, which are quantized between $0$ and $\bar{\theta}_C = \pi - \theta_C$:
+Considering the simplest case: a 1D waveguide, which has a planar core of thickness $d$ and cladding over and under it expanding to infinite.
+For this waveguide, also called a \textit{slab}, $\beta$ has a simple relation with the bounce angles $\theta_m$, which are quantized between $0$ and $\bar{\theta}_C = \pi - \theta_C$:
 $$\beta_m = n_H k_0 \cos \theta_m$$
@@
 
-\subsection{Rectangular dielectric waveguides}
-In general, in a rectangular dielectric waveguide the classification of modes need two indexes because we have two degrees of freedom.
-In Figure (\ref{fig_2dmodes}) is *** a graphical representation of the distribution of the fields in modulus.
-
-\begin{figure}[ht]
+\begin{figure}[!hb]
 	\centering
-	\includegraphics[width=.5\textwidth]{2Dmodes.png}
-	\caption{graphical rapresentation of field distribution of 2D modes}
+	\includegraphics[width=.45\textwidth]{2Dmodes.png}
+	\caption{Graphical rapresentation of field distribution of 2D modes}
 	\label{fig_2dmodes}
@@
 
-For our purpose, due to the thin geometry of the core, modes with the higher effective index are fundamental modes in the height axis.
+\subsection{Rectangular dielectric waveguides}
+In general, in a rectangular dielectric waveguide the classification of modes need two indexes because we have two degrees of freedom.
+In Figure (\ref{fig_2dmodes}) is graphically represented the distribution of the fields in modulus.
+
+For our purpose, due to the thin geometry of the core, the waveguide does not support modes with the higher order in the height axis than the fundamental one.
 The first row is of our interest.
@@
 \section{Non-linear optics}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=.75\textwidth]{nonlinearity.png}
+	\caption{Example of nonlinear relation between \textbf{P} and \textbf{E}}
+	\label{fig_nonlinearity}
+\end{figure}
+
 A nonlinear dielectric medium is characterized by a nonlinear relation between \textbf{P} and \textbf{E}, such as
@@
 
-In everyday condition linear effects are much larger than nonlinear ones.
+In everyday conditions linear effects are much larger than nonlinear ones.
 The relation between \textbf{P} and \textbf{E} becomes nonlinear when $\mathrm{E}$ has a value comparable to interatomic electric fields, which are typically $\sim 10^5-10^8$ \si{\V\per\m}.
@@
 
-The nonlinear component of the induced electric polarization vector, considering significant only the third-order term, is
+Considering significant only the third-order term, the nonlinear component of the induced electric polarization vector is
 \begin{equation}
@@
 
-Considering a silicon waveguide with a rectangular core section, to study the propagation of four wave, the total electric field and be expressed as
+Considering a silicon waveguide with a rectangular core section, to study the propagation of four waves, the total electric field can be expressed as
 \begin{equation}
@@
 	P_4 &= \frac{3\varepsilon_0}{4} \chi^3_{xxxx}\left[ |\mathrm{E}_4|^2\mathrm{E}_4 2(|\mathrm{E}_1|^2+|\mathrm{E}_2|^2+|\mathrm{E}_3|^2)\mathrm{E}_4 \right. \\
-	&+ \left. 2\mathrm{E}_1\mathrm{E}_2\mathrm{E}_3\mathrm{e}^{i\phi_+}+2\mathrm{E}_1\mathrm{E}_2\mathrm{E}_3^*\mathrm{e}^{i\phi_-}\right] \\
+	&+ \left. 2\mathrm{E}_1\mathrm{E}_2\mathrm{E}_3\mathrm{e}^{i\phi_+}+2\mathrm{E}_1\mathrm{E}_2\mathrm{E}_3^*\mathrm{e}^{i\phi_-} + ...\right]\\
 
@@
 The term containing $\phi_-$ corresponds to the case in which two photons at frequencies $\omega_1$ and $\omega_2$ are annihilated, while two photons at frequencies $\omega_3$ and $\omega_4$ are created simultaneously.
-On the other hand, the term containing $\phi_+$ correspond to the case in which three photons at frequencies $\omega_1$, $\omega_2$ and $\omega_3$ are annihilated, while one photon at frequency $\omega_4$ is created.
+On the other hand, the term containing $\phi_+$ corresponds to the case in which three photons at frequencies $\omega_1$, $\omega_2$ and $\omega_3$ are annihilated, while one photon at frequency $\omega_4$ is created.
 
 Our study focuses on a special condition of the second case, where $\omega_1 = \omega_2 = \omega_P$.
-The setup therefore consists of a strong pump of frequency  $\omega_P$ and a signal of frequency  $\omega_3 = \omega_S$, resulting in the creation of the idler wave of frequency $\omega_4 = \omega_I$.
+The setup therefore consists of a strong pump of frequency  $\omega_P$ and a signal of frequency  $\omega_3 = \omega_S$, resulting in the creation of the idler wave of frequency $\omega_4 = \omega_I$, as in Figure (\ref{fig_setup}).
 The condition of frequency and phase matching are therefore:
@@
 
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=.55\textwidth]{setup.png}
+	\caption{Symbolical rapresentation of the setup}
+	\label{fig_setup}
+\end{figure}
+
 \subsubsection{Coupled amplitude equations}
@@
 The remaining four are the equivalent of Eq. (\ref{eq_wg_b}) and describe how the fields change while travelling through the waveguide.
-Those, considering $E_j(\textbf{r}) = F_j(x,y)A_j(z)$ where $F_j$ is the spatial distribution of the mode, can be written as:
+Considering $E_j(\textbf{r}) = F_j(x,y)A_j(z)$ where $F_j$ is the spatial distribution of the mode, they can be written as:
 
@@
 \end{align}
+\label{eq_coupled}
 \end{subequations}
@@
 \hspace{18pt}are the overlap integrals of the different modes, where the brackets mean an integration on a plane $\langle g(x,y)\rangle = \int\int_{-\inf}^{\inf}g(x,y)\mathrm{dxdy}$.
-The physical interpretation of such quantities is how much different modes are superimposed/\ref{}/overlapped with each others.
+The physical interpretation of such quantities is how much different modes are overlapped with each others.
 
@@
 The previous equations are quite general (they include SPM, XPM in addition to FWM) and require a numerical approach to be solved exactly.
-For this reason, we propose an approximate solution to understand the physical implication.
-The first approximation is called ``undepleted pump" and consist of assuming the pump waves to be much more intense than the other waves.
+For this reason, we propose an approximate solution to understand the physical implications.
+The first approximation is called ``undepleted pump" and consists in assuming the pump waves to be much more intense than the other waves.
 As a further simplification, we assume that all overlap integrals are nearly the same
@@
 
-Using the same approximations on (\ref{eq_coupled_amplitude_c}) and (\ref{eq_coupled_amplitude_d}) and replacing Eqs (\ref{eq_pump_sol}) where needed we obtain two linear coupled equations for signal and idler:
+Using the same approximations on (\ref{eq_coupled_amplitude_c}) and (\ref{eq_coupled_amplitude_d}) and replacing Eqs (\ref{eq_pump_sol}a) and (\ref{eq_pump_sol}b) where needed we obtain two linear coupled equations for signal and idler:
 \begin{subequations}
@@
 
-We made a further assumption, that is that $\kappa = \Delta k + \gamma(P_1 + P_2) \approx \Delta k$, since $\Delta \gg \gamma(P_1 + P_2)$ almost always.
+We can also define a length scale, known as the coherence length, using $L_{coh} = 2\pi/|\Delta\kappa|$, where $\Delta\kappa$ is the maximum value of the effective phase mismatch that can be tolerated.
+Moreover significant FWM occurs if $L_{sam}<L_{coh}$ where $L_{sam}$ is the sample length.
+This definition allow us to make a further assumption, that is $\kappa = \Delta k + \gamma(P_1 + P_2) \approx \Delta k$.
+Considering a pump power $P_1+P_2 = \SI{1}{\W}$ and a sample length $L_{sample} = \SI{1}{\cm}$ we obtain
+\begin{equation}
+\left\{
+ 	\begin{aligned}
+		\gamma(P_1 + P_2) = \frac{n_2\omega}{cA_{eff}}P_0 = \frac{\SI{4.5e-18}{\m^2\per\W}}{}
+		\Delta k &= 2\beta_P - \beta_S - \beta_I = 0
+	\end{aligned}
+\right.
+\label{eq_f&pmc}
+\end{equation}
+
+since $\Delta k \gg \gamma(P_1 + P_2)$ almost always.
 In order to be efficient, the parametric process needs to verify the conservation of both energy and momentum, as given in Eq. (\ref{eq_f&pmc}).
 
-We can also define a length scale, known as the coherence length, using $L_{coh} = 2\pi/|\Delta\kappa|$, where $\Delta\kappa$ is the maximum value of the effective phase mismatch that can be tolerated.
-Moreover significant FWM occurs if $L_{sam}<L_{coh}$ where $L_{sam}$ is the sample length.
+\section{Computational model}
 
-\section{Computational model}
+Our aim is to study how the generation of a new wave at different frequency through FWM is influenced by the different modes of the waveguide.
+Waveguide modes indeed react differently to the change of frequency and temperature of the system, which are the free variables of the problem.
+
 To understand the behaviour of the waveguide, it is first necessary to know how waves of different frequencies are transmitted through the waveguide.
@@
 Our aim was to develop a model to work with an infrared laser pump with $\lambda_{p} = \SI{1.55}{\um}$.
-The reason for this choice is that silicon is transparent at these wavelength and also because of the availability of lasers that emit at the specific wavelength.
+The reasons are that silicon is transparent at these wavelength and also that lasers that emit at the specific wavelength are largely available.
 
 We narrowed our simulations to a frequency gap centered in $\omega_p = 2\pi \nu_p = 2\pi c / \lambda_{p}$.
-The gap chosen was precisely $[\SI{1.45}{\um} ,\, \SI{1.65}{\um}]$ or the equivalent $[\SI{182}{\THz} ,\, \SI{207}{\THz}]$.
+The gap chosen was precisely $[\SI{1.45}{\um} ,\, \SI{1.65}{\um}]$ or the equivalent $[\SI{182}{\THz} ,\, \SI{207}{\THz}]$, because we have tunable lasers which work in this spectral range.
 The temperature gap, on the other hand, was chosen to be $[\SI{0}{\K} - \SI{400}{\K}]$ over ambient temperature $T_{amb} = \SI{293.15}{\K} = \SI{20}{\celsius}$, that is $[\SI{293.15}{\K} - \SI{693.15}{\K}]$.
+It is reasonable to heat the silicon up to \SI{400}{\celsius}.
 
@@
 
-We modelized a dielectric waveguide with a silicon (Si) core \SI{3}{\um} wide and \SI{.25}{\um} high.
+We modelled a dielectric waveguide with a silicon (Si) core \SI{3}{\um} wide and \SI{.25}{\um} high.
 The cladding was set to be silica (SiO2) and coated the top of the core with a thickness of \SI{.35}{\um}.
@@
 We positioned a thermal reservoir, a ``\textit{heater}", \SI{0.3}{\um} wide at the top of the cladding, exactly over the center of the waveguide core and set to mantain a specific temperature $T_H$ in the gap $[\SI{293.15}{\K} - \SI{693.15}{\K}]$, given by the configuration chosen.
-To **** 
-define the density $\rho$ in [\si{\kg\m^3}], the thermal conductivity $\kappa_{TH}$ in [\si{\W\per\m\per\K}] and the heat capacity $C_P$ in [\si{\J\per\kg\per\K}] of the different materials.
+To solve the heat equation we defined the density $\rho$ in [\si{\kg\m^3}], the thermal conductivity $\kappa_{TH}$ in [\si{\W\per\m\per\K}] and the heat capacity $C_P$ in [\si{\J\per\kg\per\K}] of the different materials.
 
@@
 \subsubsection{Numerical solution}
-Because the degrees of freedom of the problem were too many, we resorted to automated algorithms which gave us a numerical, and therefore approximate, solution.
+Since the degrees of freedom of the problem were too many, we resorted to automated algorithms which gave us a numerical, and therefore approximate, solution.
 
@@
 It was necessary to set the boundary conditions: the two sides (left, right) and the bottom were considered as thermal reservoirs with a temperature $T = T_{amb} = \SI{293.15}{\K}$.
-The top was, instead, split into three sections: the heater, as we explained before, and the remaining two parts.
-Those were set to have a convective heat flux with air at ambient temperature.
+The top was, instead, split into three sections: the heater, as we explained previously, and the remaining two parts.
+These were set to have a convective heat flux with air at ambient temperature.
 Silica heat transfer coefficient was set to $\mathrm{HTC}_{\mathrm{SiO}_2} = \SI{5}{\W\per(\m^2\K)}$.
@@
 
-We employed an automated algorithm to solve, in the frequency domain, the Helmholtz equation on a fine grid in the waveguide section.
+We employed an automated FEM algorithm to solve, in the frequency domain, the Helmholtz equation on a fine grid in the waveguide section.
 Each point of evaluation took into account the effective index of the material, slightly changed by the local temperature obtained by the stationary solution.
@@
 We set all four sides (top, bottom, left, right) to ``\texttt{scattering boundary condition}", which is a condition where the boundary is completely transparent to scattered waves.
-That means that the core and cladding is isolated from the outside. \ref{}
+That means that the core and cladding is isolated from the outside.
 
-This algorithm was set to find the eight modes which effective index $n_{eff}$ was closest to $n_{eff}=4$ in absolute value.
+This algorithm was set to find the eight modes whose effective index $n_{eff}$ was closest to $n_{eff}=4$ in absolute value.
 \subsubsection{Data output}
@@
 Due to the intrinsic symmetry of the problem (and thus of the integrals) not all combinations of orders can produce FWM.
-Only those in which the sum of the orders is an even number are interesting.
+Only those in which the sum of the orders is an even number are interesting, because only in those combinations the overlap integrals in Eq. (\ref{eq_coupled}) are not zero.
 To narrow the possible sets, we chose only full TE or full TM  combinations.
@@
 As it is, the phase mismatch is a function of the wavelenghts of pump, signal and idler.
-Imposing the conservation of energy,
+By imposing the conservation of energy,
 \begin{equation}
@@
 We could therefore find the local maxima of such function and assume they are the centers of the peaks.
-If their position change significally while shifting the temperature, it means we are able to control the phase-match condition.
+If their position changes significantly while shifting the temperature, it means we are able to control the phase-match condition.
 
@@
 There are a few improvements which were not introduced in our study because of the limited time available.
-They could be eventually implemented in an extended study of the very same topic.
+They could be eventually implemented in an extended study of this topic.
 
@@
 
-\item	It should be considered the thermal expansion of materials.
-The thermal expansion coefficients of both silicon and silica are small but, on the other hand, the temperature change is quite high.
-It should not be easily considered as negligible contribution as it could change the waveguide geometry and therefore the modes.
+\item	Thermal expansion of materials should be considered.
+While the thermal expansion coefficients of both silicon and silica are small, the temperature change is quite high.
+It should not be lightly considered as a negligible contribution as it could change the waveguide geometry and therefore the modes.
 
-\item	The aim of this study was to understand if it was possible at all to control FWM with temperature.
+\item	The aim of this study was limited to understanding if it was possible at all to control FWM with temperature.
 It is also important to develop the correlation between temperature and efficiency of energy conversion from the pump to the idler.

### 2015-09-21 gitcode/comsol-extractor/comsol_extractor_v3_TE_only.m

@@ -1,0 +1,297 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%   fork of stanamodi v04 of M.Borghi, M.Mancinelli, M.Bernard from
+%
+%                                                         D. Bazzanella   
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+
+close all;
+clc;
+
+fprintf('Memory Cleared\n');
+
+%% INITIAL PARAMETERS
+
+% setting up initial parameters
+fprintf('\nSetting up initial parameters\n');
+
+[ans1, ans2] = uigetfile({'../comsol/*.mph'});  % choose file to load
+setting.comsolfile = strcat(ans2,ans1);         % filepath of the comsol model
+setting.data_set = 'dset3';                     % name of the dataset in the consol model
+setting.save_path = '../data/';                 % filepath of filesaves
+
+% file-saving parameters
+setting.FILE_EXT	= '.mat';         	% Determines the extension of the files: .mat or .dat
+setting.FILE_TYP	= '-mat';        	% Determines the file type of the files: -mat or -ascii
+
+% processig parameters
+setting.SAVE_H		= false;        	% 1: saves also the H fields
+setting.COMPUTE_H	= true;            	% 1: Compute H from matlab though impedance, 0 loads from COMsol.
+setting.IMAGINARY	= false;            % Extract also imaginary part of the fields
+setting.FIT_ORD     = true;             % Order of the fit in the effective index dispersion as a function of lambda
+setting.TM_TOO      = true;             % classify also TM modes [1=yes]
+setting.SAVE_FIELDS = true;             % 1: saves fields as matrix
+
+% sampling parameters
+setting.smpx		= 1300;             % Total samples per x direction for all the box
+setting.smpy        = 1300;             % Total samples per y direction for all the box
+setting.BOX_CONST   = true;             % If the box is fixed, the grid is generated only once
[…]

### 2015-09-21 gitcode/phase-matching/phasematching_v3.m

@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 601;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 3001;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -73,7 +73,7 @@ for ww=1:pm.n_sample_wl
 end
 
 % sampling temperature
-pm.n_sample_t = 201;
+pm.n_sample_t = 301;
 pm.step_t = (vec.temp(end) - vec.temp(1) )/(pm.n_sample_t - 1);
 
 vec.sample_temp = zeros(pm.n_sample_t,1);
@@ -109,7 +109,7 @@ setting.fit_str = 'poly52';
 
 for ww=1:par.n_wg_wid
     for hh=1:par.n_wg_hgt
-        for pp=1:2
+        for pp=1:1 % no TM!!
             for mm=1:par.n_modi
                 
                 data.fit_neff(ww,hh,pp,mm).exist = false;
@@ -184,8 +184,9 @@ clear ww hh pp mm ll tt ans fit1 gof1 xdata ydata zdata index disp
 fprintf('\nListing the configuration of permitted orders\n');
 
 tic
+par.ord_max = par.n_modi;
 pm.comb = [];
-for TE=1:2
+for TE=1:1  % no TM!!!
     for pp=1:par.ord_max       % DA CORREGGERE! corretto?
         for ss=1:par.ord_max
             for ii=1:par.ord_max

### 2015-09-21 gitcode/phase-matching/single_combination.m

@@ -101,7 +101,7 @@ setting.fit_str = 'poly52';
 
 for ww=1:par.n_wg_wid
     for hh=1:par.n_wg_hgt
-        for pp=1:2
+        for pp=1:1 % no TM
             for mm=1:par.n_modi
                 
                 data.fit_neff(ww,hh,pp,mm).exist = false;

### 2015-09-21 gitcode/phase-matching/phasematching_v3.m
3003

@@ -419,29 +419,42 @@ clear ans xGrid yGrid zdata zData rr jj tt y y2 maxL locs bw fitresult f name su
 
 %% 2D plots data vs orders
 
+tmp = [];
+for jj=1:length(results.indexes)
+    tmp = [tmp; num2str(pm.comb( 2,:,results.indexes(jj) ) ) ];
+end
+
 f = figure('name', 'peak position at ambient temperature');
-title('peak position at ambient temperature [um]');
-hold on;
+axes1 = axes('Parent',f,...%'YGrid','on','XGrid','on',...
+    'XTickLabel', {'   ',mat2cell( squeeze( pm.comb(2,:,results.indexes) )', ones(length(results.indexes),1), 3 ),'   '},...
+    'XTickLabelRotation', 90,...
+    'XTick', {0:1:length(results.indexes+1)},...
+    'LineStyleOrderIndex',2);
+hold(axes1,'on');
+title('Peaks position at ambient temperature [\mum]');
 plot( 1e6*results.max.q(results.indexes,1:end), 'o' );
-saveas(f, 'ppaat', 'pdf');
+ylabel({'Position [\mum]'});
+xlabel({'Combination'});
+
+saveas(f, 'ppaat', 'png');
 
 f = figure('name', 'peak position: m');
-title('peak position change [nm/100°C]');
+title('Change in peaks position [nm/100°C]');
 hold on;
 plot( 1e11*results.max.m(results.indexes,1:end), 'o' );
-saveas(f, 'ppc', 'pdf');
+saveas(f, 'ppc', 'png');
 
 f = figure('name', 'bandwidth');
-title('bandwidth at ambient temperature [nm]');
+title('Bandwidth at ambient temperature [nm]');
 hold on;
 plot( 1e9*results.bw.q(results.indexes,1:end), 'o' );
-saveas(f, 'baat', 'pdf');
+saveas(f, 'baat', 'png');
 
 f = figure('name', 'bandwidth: m');
-title('bandwidth change [nm/100°C]');
+title('Bandwidth change [nm/100°C]');
 hold on;
 plot( 1e11*results.bw.m(results.indexes,1:end), 'o' );
-saveas(1, 'bc', 'pdf');
+saveas(1, 'bc', 'png');
 
 %% 2D plots data vs orders, w/out degenerate states
 

### 2015-09-21 gitcode/phase-matching/single_combination.m

@@ -439,9 +439,6 @@ ylabel({'\lambda [\mum]'});
 title(name);
 
 
-
-
-
 top = round( max([1,max(bws(:)*2e9)] ),1,'significant');
 
 name = strcat( 'Bandwidth of combination ',TE,[' ', num2str(pm.comb(2,:))] );

### 2015-09-21 latex/article.tex
aggregation

@@
 Considering a pump power $P_1+P_2 = \SI{1}{\W}$ and a sample length $L_{sample} = \SI{1}{\cm}$ we obtain
-\begin{equation}
+\begin{equation*}
 \left\{
  	\begin{aligned}
-		\gamma(P_1 + P_2) = \frac{n_2\omega}{cA_{eff}}P_0 = \frac{\SI{4.5e-18}{\m^2\per\W}}{}
-		\Delta k &= 2\beta_P - \beta_S - \beta_I = 0
+		\gamma(P_1 + P_2) &= \frac{n_2\omega}{cA_{eff}}P_0 = \frac{\SI{4.5e-18}{\m^2\per\W}}{c\SI{e-12}{\m^2}}\frac{2\pi c}{\SI{1.55e-6}{\m}}\SI{1}{\W} \approx \SI{20}{\per\m} \approx \SI{e1}{\per\m}\\
+		|\Delta k |&= \frac{2\pi}{L_{sam}} = \frac{2\pi}{\SI{1}{\cm}} \approx \SI{600}{\per\m} \approx \num{e2} - \SI{e3}{\per\m}
 	\end{aligned}
@@
 \label{eq_f&pmc}
-\end{equation}
+\end{equation*}
 
-since $\Delta k \gg \gamma(P_1 + P_2)$ almost always.
-In order to be efficient, the parametric process needs to verify the conservation of both energy and momentum, as given in Eq. (\ref{eq_f&pmc}).
+since |$\Delta k| \gg \gamma(P_1 + P_2)$ almost always we can consider it trascurable.
+
+Therefore, in order to be efficient, the parametric process needs to verify the conservation of both energy and momentum, as given in Eq. (\ref{eq_f&pmc}).
 
@@
 \subsection{Data analysis}
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=.75\textwidth]{delta_example.png}
+	\caption{Example of $L_{coh}$ at $T_H$ fixed.}
+	\label{fig_peaks}
+\end{figure}
+
 We studied the value of $L_{coh}$ of the selected configurations with a rough analysis of 3D plots of $L_{coh}(\lambda,T_{H})$.
@@
 An example is given in Figure (\ref{fig_peaks}).
-
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=.75\textwidth]{delta_example.png}
-	\caption{Example of $L_{coh}$ at $T_H$ fixed.}
-	\label{fig_peaks}
-\end{figure}
 
@@
 	\centering
-	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[width=1\textwidth]{ppaat2.pdf}
+	\begin{subfigure}[b]{0.75\textwidth}
+		\includegraphics[width=1\textwidth]{ppaat2.png}
 		\label{fig_sym_pp@t2} 	% pp@t = bandwidth @ T_amb,
@@
 		\caption{Peaks position at $T_{amb}$.}
-	\end{subfigure}\hspace{.05\textwidth}
-	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[width=1\textwidth]{ppc2.pdf}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.75\textwidth}
+		\includegraphics[width=1\textwidth]{ppc2.png}
 		\label{fig_sym_ppc2} % ppc = bandwidth change
@@
 	\centering
-	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[width=1\textwidth]{baat2.pdf}
+	\begin{subfigure}[b]{0.75\textwidth}
+		\includegraphics[width=1\textwidth]{baat2.png}
 		\label{fig_sym_b@t2} % b@t = bandwidth @ T_amb
 		\caption{Bandwidth at $T_{amb}$.}
-	\end{subfigure}\hspace{.05\textwidth}
-	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[width=1\textwidth]{bc2.pdf}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.75\textwidth}
+		\includegraphics[width=1\textwidth]{bc2.png}
 		\label{fig_sym_bc2} % bc = bandwidth change

### 2015-09-21 gitcode/phase-matching/phasematching_v3.m

@@ -419,44 +419,74 @@ clear ans xGrid yGrid zdata zData rr jj tt y y2 maxL locs bw fitresult f name su
 
 %% 2D plots data vs orders
 
-tmp = [];
+tmp = [''];
 for jj=1:length(results.indexes)
     tmp = [tmp; num2str(pm.comb( 2,:,results.indexes(jj) ) ) ];
 end
+tmp = [tmp; '' ];
+tmp = cellstr(tmp)';
 
-f = figure('name', 'peak position at ambient temperature');
-axes1 = axes('Parent',f,...%'YGrid','on','XGrid','on',...
-    'XTickLabel', {'   ',mat2cell( squeeze( pm.comb(2,:,results.indexes) )', ones(length(results.indexes),1), 3 ),'   '},...
-    'XTickLabelRotation', 90,...
-    'XTick', {0:1:length(results.indexes+1)},...
+f = figure('name', 'Peak position at ambient temperature');
+axes1 = axes('Parent',f,'XGrid','on','YGrid','on',...
+    'XTickLabelRotation', 60,...
+    'XTick', [1:1:length(results.indexes)],...
+    'XTickLabel', tmp,...
     'LineStyleOrderIndex',2);
 hold(axes1,'on');
-title('Peaks position at ambient temperature [\mum]');
+title('Peak position at ambient temperature [µm]');
 plot( 1e6*results.max.q(results.indexes,1:end), 'o' );
-ylabel({'Position [\mum]'});
+xlim([0 length(results.indexes)+1])
+ylabel({'Position [µm]'});
 xlabel({'Combination'});
 
-saveas(f, 'ppaat', 'png');
+saveas(1, 'ppaat', 'png');
 
-f = figure('name', 'peak position: m');
-title('Change in peaks position [nm/100°C]');
-hold on;
+f = figure('name', 'Change in peaks position [nm/100°C]');
+axes1 = axes('Parent',f,'XGrid','on','YGrid','on',...
+    'XTickLabelRotation', 60,...
+    'XTick', [1:1:length(results.indexes)],...
+    'XTickLabel', tmp,...
+    'LineStyleOrderIndex',2);
+hold(axes1,'on');
+title('Change in peak position [nm/100°C]');
 plot( 1e11*results.max.m(results.indexes,1:end), 'o' );
-saveas(f, 'ppc', 'png');
[…]

### 2015-09-21 gitcode/phase-matching/single_combination.m

@@ -421,7 +421,7 @@ if pm.comb(1,1) == 1
 else
     TE = ' TM: ';
 end
-name = strcat( 'Peaks position of combination ',TE,[' ', num2str(pm.comb(2,:))] );
+name = strcat( 'Peak position of combination ',TE,[' ', num2str(pm.comb(2,:))] );
 f = figure('name', name); % 'OuterPosition',[100, 100, 960, 480]
 axes1 = axes('Parent',f);
 hold(axes1,'on');
@@ -433,7 +433,7 @@ ylim(axes1, [1.4 1.7] );
 xlabel({'T_H [K]'});
 
 % Create ylabel
-ylabel({'\lambda [\mum]'});
+ylabel({'λ [µm]'});
 
 % Create title
 title(name);
@@ -475,12 +475,13 @@ clear TE name
 f = figure('name', 'sol27 213 sym');
 axes1 = axes('Parent',f);
 hold(axes1,'on');
-plot(vec.sample_wlen,f_Lcoh_cm(wlen_grid(1,:), temp_grid(1,:)) )
+plot(1e6.*vec.sample_wlen,f_Lcoh_cm(wlen_grid(1,:), temp_grid(1,:)) )
 ylim([0 2]);
-xlabel({'\lambda [\mum]'});
+xlim([1.45 1.65])
+xlabel({'λ [µm]'});
 ylabel({'L_{coh} [cm]'});
-title('L_{coh}(\lambda) at T_H = T_{amb} = 293.15 K');
-plot(vec.sample_wlen, ones(pm.n_sample_wl,1), '--')
+title('L_{coh}(λ) at T_H = T_{amb} = 293.15 K');
+plot(1e6.*vec.sample_wlen, ones(pm.n_sample_wl,1), '--')
 %}
 %%  import asym, sol 213, and print L_coh [cm] (λ) @ T_amb = 293.15
 %{
@@ -492,7 +493,7 @@ axes1 = axes('Parent',f);
 hold(axes1,'on');
 plot(vec.sample_wlen,f_Lcoh_cm(wlen_grid(1,:), temp_grid(1,:)) )
 ylim([0 2]);
-xlabel({'\lambda [\mum]'});
+xlabel({'λ [\mum]'});
 ylabel({'L_{coh} [cm]'});
 title('L_{coh}(\lambda) at T_H = T_{amb} = 293.15 K');
[…]

### 2015-09-21 latex/article.tex
nefastità

@@
 \usepackage{subcaption}
+\usepackage{sidecap}
 
@@
 
+\begin{equation}
+	\Delta k = 2\beta_P(\omega_P)-\beta_S(\omega_S)-\beta_I(2\omega_P-\omega_S)
+\end{equation}
+
 Then, starting from the fits of the effective index at different wavelengths and temperatures, we evaluated the phase mismatch of all sets.
@@
 
-\subsection{Data analysis}
-
 \begin{figure}[!h]
@@
 
+\subsection{Data analysis}
 We studied the value of $L_{coh}$ of the selected configurations with a rough analysis of 3D plots of $L_{coh}(\lambda,T_{H})$.
@@
 
-\begin{figure}[!h]
+\begin{SCfigure}%[!h]
 	\centering
-	\includegraphics[width=.75\textwidth]{ex_pos.png}
-	\caption{Example of peaks vs $T_H$.}
+	\includegraphics[width=.64\textwidth]{ex_pos.png}
+	\caption{Example of peak position vs $T_H$.}
 	\label{fig_example_position}
-\end{figure}
-\begin{figure}[!h]
+\end{SCfigure}
+\begin{SCfigure}%[!h]
 	\centering
 %	\includegraphics[scale=1]{ex_bw.png}
-	\includegraphics[width=.75\textwidth]{ex_bw.png}
+	\includegraphics[width=.64\textwidth]{ex_bw.png}
 	\caption{Example of bandwidth vs $T_H$.}
 	\label{fig_example_bandwidth}
-\end{figure}
+\end{SCfigure}
 
@@
 %	\centering
-%	\begin{subfigure}[b]{0.45\textwidth}
+%	\begin{subfigure}[b]{0.49\textwidth}
 %		\includegraphics[width=1\textwidth]{ex_pos.png}
@@
 %	\end{subfigure}%\hspace{.02\textwidth}
-%	\begin{subfigure}[b]{0.45\textwidth}
+%	\begin{subfigure}[b]{0.49\textwidth}
 %		\includegraphics[width=1\textwidth]{ex_bw.png}
@@
 Therefore we summarized them by collecting the slopes and the value of the functions at ambient temperature.
+To make the graphs easier to read, we excluded set of data the pointsof no interest: those which peak had the same frequency $\omega_P = \SI{1.55}{\um}$ of the pump.
 
+The first Figure (\ref{fig_sym_pp@t2}) tell us where we found phase-matching condition.
+We can see that every set has its symmetric one.
+For example, combination \texttt{517} is the symmetric of \texttt{571}.
+In the coupled equations and in the 
 %The next Figures (\ref{fig_sym_pp}) and (\ref{fig_sym_bw}) show the results obtained, excluding the sets which only phasematch was at $\lambda = \SI{1.55}{\um}$
 
-\begin{figure}[h!]
+\begin{figure}[!h]
 	\centering
-	\begin{subfigure}[b]{0.75\textwidth}
-		\includegraphics[width=1\textwidth]{ppaat2.png}
-		\label{fig_sym_pp@t2} 	% pp@t = bandwidth @ T_amb,
-								% 2 = no points at 1.55um
-		\caption{Peaks position at $T_{amb}$.}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.75\textwidth}
-		\includegraphics[width=1\textwidth]{ppc2.png}
+	\includegraphics[width=.75\textwidth]{ppaat2.png}
+	\caption{Peak position at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler orders.}
+	\label{fig_sym_pp@t2} 	% pp@t = bandwidth @ T_amb, 2 = no points at 1.55um
+\end{figure}
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=.75\textwidth]{ppc2.png}
+	\caption{Change of peak position.}
 	\label{fig_sym_ppc2} % ppc = bandwidth change
-		\caption{Change of peak position.}
-	\end{subfigure}
-	\caption{Peak position summary}
-	\label{fig_sym_pp}
 \end{figure}

### 2015-09-21 gitcode/phase-matching/phasematching_v3.m

@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 3001;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 601;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -73,7 +73,7 @@ for ww=1:pm.n_sample_wl
 end
 
 % sampling temperature
-pm.n_sample_t = 301;
+pm.n_sample_t = 201;
 pm.step_t = (vec.temp(end) - vec.temp(1) )/(pm.n_sample_t - 1);
 
 vec.sample_temp = zeros(pm.n_sample_t,1);
@@ -238,7 +238,7 @@ tic
 % creat grid of evaluation
 [~, pgrid]      = meshgrid(vec.sample_temp, pm.pump_w.*ones(pm.n_sample_wl,1));
 [ygrid, sgrid]  = meshgrid(vec.sample_temp, vec.sample_wlen);
-[~, igrid]      = meshgrid(vec.sample_temp, 2*pm.pump_w - vec.sample_wlen);
+[~, igrid]      = meshgrid(vec.sample_temp, 1./(2/pm.pump_w - 1./vec.sample_wlen));
 
 for ww=1:par.n_wg_wid                                   % number of widths
     for hh=1:par.n_wg_hgt                               % number of heights
@@ -439,7 +439,7 @@ xlim([0 length(results.indexes)+1])
 ylabel({'Position [µm]'});
 xlabel({'Combination'});
 
-saveas(1, 'ppaat', 'png');
+%saveas(1, 'ppaat', 'png');
 
 f = figure('name', 'Change in peaks position [nm/100°C]');
 axes1 = axes('Parent',f,'XGrid','on','YGrid','on',...
@@ -454,7 +454,7 @@ xlim([0 length(results.indexes)+1])
 ylabel({'Δ-position [nm/100°C]'});
 xlabel({'Combination'});
 
-saveas(2, 'ppc', 'png');
+%saveas(2, 'ppc', 'png');
 
[…]

### 2015-09-21 gitcode/phase-matching/single_combination.m

@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 4001;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 1001;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -73,7 +73,7 @@ for ww=1:pm.n_sample_wl
 end
 
 % sampling temperature
-pm.n_sample_t = 501;
+pm.n_sample_t = 201;
 pm.step_t = (vec.temp(end) - vec.temp(1) )/(pm.n_sample_t - 1);
 
 vec.sample_temp = zeros(pm.n_sample_t,1);
@@ -308,7 +308,7 @@ i.fi2       = @(xi,t) i.fi(xi,t,i.p00,i.p10,i.p01,i.p20,i.p11,i.p02,i.p30,i.p21,
 
 xp = 1.55e-6;
 
-f_delta     = @(xs,t) 2.*pi.*( 2.*p.fp2(xp,t)./xp - s.fs2(xs,t)./xs - i.fi2(2.*xp-xs,t)./(2.*xp-xs) );
+f_delta     = @(xs,t) 2.*pi.*( 2.*p.fp2(xp,t)./xp - s.fs2(xs,t)./xs - i.fi2(1./(2./xp-1./xs),t).*(2./xp-1./xs) );
 f_Lcoh      = @(xs,t) 2.*pi./abs(f_delta(xs,t));
 f_Lcoh_cm   = @(xs,t) 200*pi./abs(f_delta(xs,t));
 
@@ -323,7 +323,7 @@ f = figure(1);
 axes1 = axes('Parent',f);
 mesh(wlen_grid, temp_grid, f_Lcoh_cm(wlen_grid, temp_grid) );
 hold(axes1,'on');
-zlim(axes1,[0.1 2]);
+zlim(axes1,[0 2]);
 
 toc
 clear wlen_grid temp_grid axes1 f

### 2015-09-22 latex/article.tex
sleep
rough times

@@
 This definition allow us to make a further assumption, that is $\kappa = \Delta k + \gamma(P_1 + P_2) \approx \Delta k$.
-Considering a pump power $P_1+P_2 = \SI{1}{\W}$ and a sample length $L_{sample} = \SI{1}{\cm}$ we obtain
+Considering a peak power $P_1+P_2 = \SI{1}{\W}$ of the pump and a sample length $L_{sam} = \SI{1}{\cm}$ we obtain
 \begin{equation*}
@@
 
-since |$\Delta k| \gg \gamma(P_1 + P_2)$ almost always we can consider it trascurable.
+since $|\Delta k| \gg \gamma(P_1 + P_2)$ almost always we can consider it trascurable.
 
@@
 \begin{equation}
-n = n(\lambda)+\mathrm{TOC}\cdot T
+n = n(\lambda)+\mathrm{TOC}\cdot (T-T_{amb})
 \end{equation}
@@
 \end{equation}
+$$or \qquad \qquad \lambda_I = \left( \frac{2}{\lambda_P} - \frac{1}{\lambda_S}\right)^{-1} $$
 we obtained the only frequency permitted for $\omega_I$.
@@
 
-\begin{equation}
-	\Delta k = 2\beta_P(\omega_P)-\beta_S(\omega_S)-\beta_I(2\omega_P-\omega_S)
-\end{equation}
+%\begin{equation}
+\begin{align*}
+	\Delta k &= 2\beta_P(\omega_P)-\beta_S(\omega_S)-\beta_I(2\omega_P-\omega_S)\\
+			 &= 2\pi\left[ 2\frac{n_{eff}^P(\lambda_P)}{\lambda_P}
+			 - \frac{n_{eff}^S(\lambda_S)}{\lambda_S}
+			 - \frac{n_{eff}^I(\lambda_I)}{\lambda_I}\right]
+\end{align*}
+%\end{equation}
 
@@
 \bibitem{n_db} http://refractiveindex.info/
+\bibitem{spectrum} Lau, Ryan KW, et al. "Continuous-wave mid-infrared frequency conversion in silicon nanowaveguides." Optics letters 36.7 (2011): 1263-1265.
 \end{thebibliography}

### 2015-09-22 gitcode/comsol-extractor/rough_comsol_extractor_v3.m

@@ -1,0 +1,174 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%   fork of stanamodi v04 of M.Borghi, M.Mancinelli, M.Bernard from
+%
+%                                                         D. Bazzanella   
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+
+close all;
+clc;
+
+fprintf('Memory Cleared\n');
+
+%% INITIAL PARAMETERS
+
+% setting up initial parameters
+fprintf('\nSetting up initial parameters\n');
+
+[ans1, ans2] = uigetfile({'../comsol/*.mph'});  % choose file to load
+setting.comsolfile = strcat(ans2,ans1);         % filepath of the comsol model
+setting.data_set = 'dset3';                     % name of the dataset in the consol model
+setting.save_path = '../data/';                 % filepath of filesaves
+
+% file-saving parameters
+setting.FILE_EXT	= '.mat';         	% Determines the extension of the files: .mat or .dat
+setting.FILE_TYP	= '-mat';        	% Determines the file type of the files: -mat or -ascii
+
+% processig parameters
+setting.SAVE_H		= false;        	% 1: saves also the H fields
+setting.COMPUTE_H	= true;            	% 1: Compute H from matlab though impedance, 0 loads from COMsol.
+setting.IMAGINARY	= false;            % Extract also imaginary part of the fields
+setting.FIT_ORD     = true;             % Order of the fit in the effective index dispersion as a function of lambda
+setting.TM_TOO      = true;             % classify also TM modes [1=yes]
+setting.SAVE_FIELDS = true;             % 1: saves fields as matrix
+
+% sampling parameters
+setting.smpx		= 1300;             % Total samples per x direction for all the box
+setting.smpy        = 1300;             % Total samples per y direction for all the box
[…]

### 2015-09-22 gitcode/phase-matching/phasematching_v3.m

@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 601;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 3001;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -73,7 +73,7 @@ for ww=1:pm.n_sample_wl
 end
 
 % sampling temperature
-pm.n_sample_t = 201;
+pm.n_sample_t = 301;
 pm.step_t = (vec.temp(end) - vec.temp(1) )/(pm.n_sample_t - 1);
 
 vec.sample_temp = zeros(pm.n_sample_t,1);
@@ -405,7 +405,7 @@ for rr=1:pm.n_results;
             results.maxima( 1:size(y,1), 1:size(y,2), rr, 1, 1) = y;
             results.bwid( 1:size(y2,1), 1:size(y2,2), rr, 1, 1) = y2;
             
-            saveas(f, strcat('sol',num2str(rr),'_',num2str(pm.comb(2,:,rr))), 'pdf');
+            %saveas(f, strcat('sol',num2str(rr),'_',num2str(pm.comb(2,:,rr))), 'pdf');
             close 1
             
         end 
@@ -563,14 +563,14 @@ xlabel({'Combination'});
 
 %saveas(8, 'bc2', 'png');
 
-saveas(1, 'ppaat', 'png');
-saveas(2, 'ppc', 'png');
-saveas(3, 'baat', 'png');
-saveas(4, 'bc', 'png');
-saveas(5, 'ppaat2', 'png');
-saveas(6, 'ppc2', 'png');
-saveas(7, 'baat2', 'png');
-saveas(8, 'bc2', 'png');
+% saveas(1, 'ppaat', 'png');
+% saveas(2, 'ppc', 'png');
+% saveas(3, 'baat', 'png');
+% saveas(4, 'bc', 'png');
+% saveas(5, 'ppaat2', 'png');
+% saveas(6, 'ppc2', 'png');
+% saveas(7, 'baat2', 'png');
+% saveas(8, 'bc2', 'png');
 
 clear f
 

### 2015-09-22 latex/article.tex
highway to hell

@@
 \cleardoublepage
-\setcounter{page}{3}
+\section*{Abstract}
+The silicon photonics platform is broadly being studied as an attractive platform for the extremely dense integration of optical functions at telecommunication wavelengths \cite{Jalali}.
+The use of CMOS fabrication technology, leading to high yield and the potential for integration of electronic circuits, and the high refractive index contrast available on a silicon-insulator waveguide platform ($\Delta n \sim 2$) are the main drivers for this evolution.
+While photonic integrated circuits were primarily intended to serve the telecommunication and data communication markets, the use of silicon photonics in other applications is also being explored, predominantly geared towards sensing.
+Examples of such fields of research are silicon-based bio-sensors \cite{DeVos}, gas sensors \cite{Robinson} and the development of bio-medical instrumentation \cite{Dumon}.
+In these applications, one typically retains the use of the telecommunication wavelength range, for reasons of experimental simplicity, the availability of characterized building blocks, etc.
+However, a number of applications would benefit from the use of highly integrated silicon photonic circuits specifically tailored to operate at longer wavelengths.
+For the specific field of spectroscopic sensing, probing of the molecular fingerprint absorption lines of molecules exploits the strong absorption features of molecules in the short-wave (1.4-3 \si{\um}) and mid wave (3-8 \si{\um}) infrared (MIR) \cite{Crowder}.
+The availability of an integration platform covering these two wavelength ranges could enable ultra-compact, low-cost sensor solutions, designed to outperform existing solutions.
+Within this frame the four-wave mixing process (FWM), naturally supported by the silicon platform, could be used for this purpose to convert a telecom signal to the NIR and MIR spectral region, as previously demonstrated on-chip in silicon wire waveguides \cite{Espinola}-\cite{Foster}.
+
+The FWM process involves four optical waves that have to fulfil two conditions in order to efficiently interact which are the energy conservation, naturally satisfied, and momentum conservation.
+This work is focused on the study of the momentum conservation, the so called phase matching, that is usually not trivial to achieve due to the refractive index dispersion.
+To fulfil the momentum conservation we used the multimodal phase matching (PM) technique \cite{agrawal}.
+In this specific case, it is possible to let the four waves travel in different order modes supported by the waveguide to get the phase matching.
+The PM condition can be tailored changing the waveguide geometry and more generally by changing the waveguide dispersion.
+Moreover, the dispersion can be actively tuned exploiting the thermo-optic coefficient (TOE) of silicon, that is, the temperature dependence of the refractive index.
+
+In this work a detailed theoretical study of the phase matching condition in a multimodal waveguide as a function of the temperature is carried out.
+In particular, the converted frequency position and the process BW as a function of the temperature are investigated.
+The aim is to lay the basis and prepare a design for the fabrication of an integrated device for frequency conversion applications with the possibility to be thermal tuned.
+
+\cleardoublepage 
+%\setcounter{page}{3}
 \tableofcontents
@@
 
+\clearpage
 \section{Electromagnetic waves in dielectric media}
@@
 	\label{eq_wg_a} \\
-	\frac{\partial^2\tilde{A}(z,\omega)}{\partial z^2} +2\mathrm{i}\beta\frac{\partial \tilde{A}(z,\omega)}{\partial z} -n^2k_0^2\tilde{A}(z,\omega) = 0
-	\quad ! \neq ! \quad
-	2\mathrm{i}\beta_0\frac{\partial \tilde{A}(z,\omega)}{\partial z} +(\tilde{\beta}^2 - \beta_0^2)\tilde{A}(z,\omega) = 0
+	2\mathrm{i}\beta\frac{\partial \tilde{A}(z,\omega)}{\partial z} -n^2k_0^2\tilde{A}(z,\omega) = 0
 	\label{eq_wg_b}
@@
 \end{subequations}
+%	\frac{\partial^2\tilde{A}(z,\omega)}{\partial z^2} +2\mathrm{i}\beta\frac{\partial \tilde{A}(z,\omega)}{\partial z} -n^2k_0^2\tilde{A}(z,\omega) = 0
+%	\quad ! \neq ! \quad
+%	2\mathrm{i}\beta_0\frac{\partial \tilde{A}(z,\omega)}{\partial z} +(\tilde{\beta}^2 - \beta_0^2)\tilde{A}(z,\omega) = 0
 where $k_0$ is the wavevector in vacuum and $n=n(x,y)$ is a function of the position (mainly $x$ and $y$ for a straight waveguide).
@@
 
-\begin{figure}[!hb]
+\subsection{Rectangular dielectric waveguides}
+In general, in a rectangular dielectric waveguide the classification of modes need two indexes because we have two degrees of freedom.
+In Figure (\ref{fig_2dmodes}) is graphically represented the distribution of the fields in modulus.
+
+\begin{figure}[!ht]
 	\centering
@@
 
-\subsection{Rectangular dielectric waveguides}
-In general, in a rectangular dielectric waveguide the classification of modes need two indexes because we have two degrees of freedom.
-In Figure (\ref{fig_2dmodes}) is graphically represented the distribution of the fields in modulus.
-
 For our purpose, due to the thin geometry of the core, the waveguide does not support modes with the higher order in the height axis than the fundamental one.
@@
 Only one significant index is then left to describe the order of modes.
+Figure (\ref{fig_ex_mode}) portrays a TE configuration of the third order.
 
+\begin{figure}[hb]
+	\centering
+	\includegraphics[width=0.85\textwidth]{output_mode.pdf}
+	\caption{Example of third order TE mode in a \SI{3}{\um} wide waveguide}
+	\label{fig_ex_mode}
+\end{figure}
+
+\clearpage
 \section{Non-linear optics}
+
+A nonlinear dielectric medium is characterized by a nonlinear relation between \textbf{P} and \textbf{E}, such as
+\begin{equation}
+	\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) = \mathrm{\textbf{P}_L} + \mathrm{\textbf{P}_{NL}}
+	\label{eq_P_general}
+\end{equation}
+which originates from the behaviour of bound electrons.
 
@@
 \end{figure}
-
-A nonlinear dielectric medium is characterized by a nonlinear relation between \textbf{P} and \textbf{E}, such as
-\begin{equation}
-	\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) = \mathrm{\textbf{P}_L} + \mathrm{\textbf{P}_{NL}}
-	\label{eq_P_general}
-\end{equation}
-which originates from the behaviour of bound electrons.
 
@@
 For a solution that includes pump depletion it is necessary to solve exactly the complete set of four equations, Eqs (\ref{eq_coupled_amplitude_a} - \ref{eq_coupled_amplitude_d}).
+An example of output spectrum is given in Figure (\ref{fig_spectrum}).
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=.55\textwidth]{spectrum.png}
+	\caption{Measured FWM spectra showing broadband wavelength conversion across \SI{748}{\nm}. The signal, pump, and idler wavelengths are \num{1636}, \num{1940}, and \SI{2384}{\nm}, respectively.}
+	\label{fig_spectrum}
+\end{figure}
 
@@
 
+\clearpage
 \section{Computational model}
@@
 
-We obtained graphs representing the position and the bandwidth of peaks vs temperature of each solution, as shown in Figures (\ref{fig_example_position}) and (\ref{fig_example_bandwidth}).
+We obtained graphs representing the position and the bandwidth of peaks vs temperature of each solution.
 
-\begin{SCfigure}%[!h]
+\begin{figure}[!hb]
 	\centering
-	\includegraphics[width=.64\textwidth]{ex_pos.png}
+	\includegraphics[width=.75\textwidth]{ex_pos.png}
 	\caption{Example of peak position vs $T_H$.}
 	\label{fig_example_position}
-\end{SCfigure}
-\begin{SCfigure}%[!h]
-	\centering
-%	\includegraphics[scale=1]{ex_bw.png}
-	\includegraphics[width=.64\textwidth]{ex_bw.png}
-	\caption{Example of bandwidth vs $T_H$.}
-	\label{fig_example_bandwidth}
-\end{SCfigure}
+\end{figure}
 
-%\begin{figure}[!h]
-%	\centering
-%	\begin{subfigure}[b]{0.49\textwidth}
-%		\includegraphics[width=1\textwidth]{ex_pos.png}
-%		\caption{Example of peaks vs $T_H$.}
-%		\label{fig_example_position}
-%	\end{subfigure}%\hspace{.02\textwidth}
-%	\begin{subfigure}[b]{0.49\textwidth}
-%		\includegraphics[width=1\textwidth]{ex_bw.png}
-%		\caption{Example of bandwidth vs $T_H$.}
-%		\label{fig_example_bandwidth}
-%	\end{subfigure}
-%	\caption{Examples of peaks position and bandwidth dependence on temperature $T_H$}
-%	\label{fig_examples}
-%\end{figure}
-
+\clearpage
 \section{Results}
 \subsubsection{data aggregation}
-Examining the graphs obtained from the data analysis of the symmetric configuration, we noticed that for each solution selected there were one or two straight lines.
+Examining the graphs obtained from the data analysis of the symmetric configuration, we noticed that for each solution selected there were only straight lines.
 Therefore we summarized them by collecting the slopes and the value of the functions at ambient temperature.
-To make the graphs easier to read, we excluded set of data the pointsof no interest: those which peak had the same frequency $\omega_P = \SI{1.55}{\um}$ of the pump.
+To make the graphs easier to read, we excluded set of data the points of no interest: those which peak had the same frequency $\omega_P = \SI{1.55}{\um}$ of the pump.
 
 The first Figure (\ref{fig_sym_pp@t2}) tell us where we found phase-matching condition.
-We can see that every set has its symmetric one.
-For example, combination \texttt{517} is the symmetric of \texttt{571}.
-In the coupled equations and in the 
-%The next Figures (\ref{fig_sym_pp}) and (\ref{fig_sym_bw}) show the results obtained, excluding the sets which only phasematch was at $\lambda = \SI{1.55}{\um}$
+We can see that we have only two condition in which the phasematch is verified.
+Also, combination \texttt{517} is the symmetric of \texttt{571}.
 
@@
 	\centering
-	\includegraphics[width=.75\textwidth]{ppaat2.png}
-	\caption{Peak position at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler orders.}
+	\includegraphics[width=.85\textwidth]{ppaat2.png}
+	\caption{Peak position at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler orders. We have two TE conbinations and two TM combinations.}
 	\label{fig_sym_pp@t2} 	% pp@t = bandwidth @ T_amb, 2 = no points at 1.55um
@@
 
+The second Figure (\ref{fig_sym_ppc2}) shows us that thant the change in position is of a fraction of \si{\nm}.
+This value should be compared to the bandwidth of the phase-match condition.
+In order to be interesting, its order of magnitude should be the same as the order of the bandwidth.
+
 \begin{figure}[!h]
 	\centering
-	\includegraphics[width=.75\textwidth]{ppc2.png}
-	\caption{Change of peak position.}
+	\includegraphics[width=.85\textwidth]{ppc2.png}
+	\caption{Change of peak position. The label of the x axis are to be read as pump-signal-idler orders. We have two TE conbinations and two TM combinations.}
 	\label{fig_sym_ppc2} % ppc = bandwidth change
@@
 
-\begin{figure}[h!]
+In Figure (\ref{fig_sym_b@t2}) is represented the bandwidth at ambient temperature.
+
+We can see that the bandwidths are in range between \SI{.5}{\nm} and \SI{.8}{\nm} while the changes in peak position are between \SI{.2}{\nm} and \SI{.4}{\nm}, in absolute value.
+Thus, having the same order of magnitude we can state that we have a slight control over peak position with temperature tuning.
+\begin{figure}[!h]
 	\centering
-	\begin{subfigure}[b]{0.75\textwidth}
-		\includegraphics[width=1\textwidth]{baat2.png}
+	\includegraphics[width=.85\textwidth]{baat2.png}
+	\caption{Bandwidth at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler orders. We have two TE conbinations and two TM combinations.}
 	\label{fig_sym_b@t2} % b@t = bandwidth @ T_amb
-		\caption{Bandwidth at $T_{amb}$.}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.75\textwidth}
-		\includegraphics[width=1\textwidth]{bc2.png}
-		\label{fig_sym_bc2} % bc = bandwidth change
-		\caption{Change of bandwidth.}
-	\end{subfigure}
-	\caption{Bandwidth summary}
-	\label{fig_sym_bw}
 \end{figure}
 
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=1\textwidth]{bc2.png}
+%	\caption{Change of bandwidth.}
+%	\label{fig_sym_bc2} % bc = bandwidth change
+%\end{figure}
+
+\clearpage
 \subsection{Second heater configuration}
@@
 \subsubsection{data aggregation}
-Examining the graphs obtained from the data analysis of the asymmetric configuration, we noticed a variety of different situations.
-Therefore we could not summarize the results with slopes and value at $T_{amb}$ anymore.
+Unfortunately, examining the graphs obtained from the data analysis of the asymmetric configuration, we do not noticed anything new.
 
@@
 \subsection{Summary}
+We had little results in the frequency gap chosen.
+This because we probably need to study further the geometry of the waveguide, in order to enhance the effect of the overlap integrals between the optical mode and the thermal profile.
 
@@
 \begin{thebibliography}{9}
+\bibitem{Jalali} B. Jalali and S. Fathpour, “Silicon photonics,” J. Lightw. Technol., vol. 24, no. 12, pp. 4600-4615, 2006.
+\bibitem{DeVos} K.
+De Vos, I.
+Bartolozzi, E.
+Schacht, P.
+Bienstman, and R.
+Baets, “Silicon-on-insulator microring resonator for sensitive and label-free biosensing,” Opt.
+Exp., vol.
+15, no.
+12, pp.
+7610–7615, 2007.
+\bibitem{Robinson} ] J. T. Robinson, L. Chen, and M. Lipson, “On-chip gas detection in silicon optical microcavities,” Opt. Exp., vol. 16, no. 6, pp. 4296–4301, 2008.
+\bibitem{Dumon} A.
+G.
+Yurtsever, P.
+Dumon, W.
+Bogaerts, and R.
+Baets, “Integrated photonic circuit in silicon on insulator for fourier domain optical coherence tomography,” Proc.
+SPIE, vol.
+75541B, pp.
+75541-1–75541-5, Feb.
+2010.
+\bibitem{Crowder} J. G. Crowder, S. D. Smith, A. Vass, and J. Keddie, “Infrared methods for gas detection,” in Mid-Infrared Semiconductor Optoelectronics. New York: Springer-Verlag, 2006.
+\bibitem{Espinola} R. Espinola, J. Dadap, R. Osgood, Jr., S. McNab, and Y. Vlasov, "C-band wavelength conversion in silicon photonic wire waveguides," Opt. Express 13, 4341-4349 (2005).
+\bibitem{Fukuda} H.
+Fukuda, K.
+Yamada, T.
+Shoji, M.
+Takahashi, T.
+Tsuchizawa, T.
+Watanabe, J.
+Takahashi, and S.
+Itabashi, "Four-wave mixing in silicon wire waveguides," Opt.
+Express 13, 4629-4637 (2005).
+\bibitem{Foster} M. A. Foster, A. C. Turner, J. E. Sharping, B. S. Schmidt, M. Lipson and A. L. Gaeta, “Broad-band optical parametric gain on a silicon photonic chip,” Nature 441, 960-963 (2006).
+
 \bibitem{agrawal} G. Agrawal. Nonlinear Fiber Optics, 5th edition. 2013
@@
 \bibitem{spectrum} Lau, Ryan KW, et al. "Continuous-wave mid-infrared frequency conversion in silicon nanowaveguides." Optics letters 36.7 (2011): 1263-1265.
+
 \end{thebibliography}

### 2015-09-22 gitcode/comsol-extractor/rough_comsol_extractor_v3.m

@@ -139,25 +139,31 @@ for jj=1:par.n_sol
     index.hgt     = find( vec.hgt  == sol.hgt(jj)  );
     index.temp    = find( vec.temp == sol.temp(jj) );
     
-    TEc = fliplr( real( sol.neff(jj,:) ) );
-    TMc = TEc(8:end);
-    TEc = TEc(1:7);
-	TMc(find(TMc) < 1.9) = [];
+    TEc         = fliplr( real( sol.neff(jj,:) ) );
+    indexTE     = fliplr([1:1:length(TEc)]);
+    TEc         = TEc(1:7);
+    indexTE     = indexTE(1:7);
     
-	data.neff(index.wlen, index.temp, index.wid, index.hgt, 1, :)     = TEc;
-    data.neff(index.wlen, index.temp, index.wid, index.hgt, 2, :)     = TMc;
+    TMc         = real( sol.neff(jj,:) );
+    indexTM     = [1:1:length(TMc)];
+    TMc         = TMc(1:7);
+    indexTM     = indexTM(1:7);
+    d           = diff(TMc);
+    TMc(find(d<=0)+1)       = [];
+    indexTM(find(d<=0)+1)   = [];
+    TMc         = fliplr( TMc );
+    indexTM     = fliplr(indexTM);
     
-    TEc = fliplr( sol.Aeff(jj,:) );
-    TMc = TEc(8:end);
-    TEc = TEc(1:7);
-	TMc(find(TMc) < 1.9) = [];
+	data.neff(index.wlen, index.temp, index.wid, index.hgt, 1, 1:length(TEc))	= TEc;
+    data.neff(index.wlen, index.temp, index.wid, index.hgt, 2, 1:length(TMc))   = TMc;
     
-	data.neff(index.wlen, index.temp, index.wid, index.hgt, 1, :)     = TEc;
-    data.neff(index.wlen, index.temp, index.wid, index.hgt, 2, :)     = TMc;
+	data.Aeff(index.wlen, index.temp, index.wid, index.hgt, 1, 1:length(TEc))   = real( sol.Aeff(jj, indexTE) );
+    data.Aeff(index.wlen, index.temp, index.wid, index.hgt, 2, 1:length(TMc))   = real( sol.Aeff(jj, indexTM) );
 
 end
 toc
 
+clear TEc TMc indexTE indexTM ans d
 %% SAVING
 
 tic

### 2015-09-22 gitcode/phase-matching/phasematching_v3.m

@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 3001;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 601;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -73,7 +73,7 @@ for ww=1:pm.n_sample_wl
 end
 
 % sampling temperature
-pm.n_sample_t = 301;
+pm.n_sample_t = 201;
 pm.step_t = (vec.temp(end) - vec.temp(1) )/(pm.n_sample_t - 1);
 
 vec.sample_temp = zeros(pm.n_sample_t,1);
@@ -109,7 +109,7 @@ setting.fit_str = 'poly52';
 
 for ww=1:par.n_wg_wid
     for hh=1:par.n_wg_hgt
-        for pp=1:1 % no TM!!
+        for pp=1:2
             for mm=1:par.n_modi
                 
                 data.fit_neff(ww,hh,pp,mm).exist = false;
@@ -184,9 +184,9 @@ clear ww hh pp mm ll tt ans fit1 gof1 xdata ydata zdata index disp
 fprintf('\nListing the configuration of permitted orders\n');
 
 tic
-par.ord_max = par.n_modi;
+par.ord_max = 7;
 pm.comb = [];
-for TE=1:1  % no TM!!!
+for TE=1:2
     for pp=1:par.ord_max       % DA CORREGGERE! corretto?
         for ss=1:par.ord_max
             for ii=1:par.ord_max
@@ -405,7 +405,7 @@ for rr=1:pm.n_results;
             results.maxima( 1:size(y,1), 1:size(y,2), rr, 1, 1) = y;
             results.bwid( 1:size(y2,1), 1:size(y2,2), rr, 1, 1) = y2;
             
-            %saveas(f, strcat('sol',num2str(rr),'_',num2str(pm.comb(2,:,rr))), 'pdf');
+            saveas(f, strcat('sol',num2str(rr),'_',num2str(pm.comb(2,:,rr))), 'png');
             close 1
             
         end 

### 2015-09-22 gitcode/phase-matching/phasematching_v3_TE_only.m

@@ -1,0 +1,627 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+%   This script will search for phase matching condition                    %
+%                                                                         %
+%                                                         D. Bazzanella   %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Import data structures
+
+ans1 = 0;
+while ( ans1 == 0 )
+    % Construct a questdlg with three options
+    choice = questdlg('Import a file or to exit the program?', 'Import File', 'Import File', 'Exit program', 'Go on', ...
+        'Import File');
+    % Handle response
+    switch choice
+        case 'Import File'
+            disp('Choose the file to import.\nShould be something like yyyy-MM-dd_HH:mm:ss.mat\n');
+            ans1 = 0;
+        case 'Exit program'
+            %disp('\n\nExiting right now.')
+            clear ans1 choice
+            error('Exiting right now.');
+        %{
+        case 'Go on'
+            disp('\nGoing on...\n');
+            ans1 = 1;
+        %}
+    end
+    
+    if (ans1 == 0 )
+        [ans1, ans2] = uigetfile({'../data/*.mat'});     % choose file to load
+        
+        fprintf('File chosen: ', strcat(ans2, ans1));
+        load( strcat(ans2, ans1) );
+    end
+end
+
+% physical constants
+const.c     = 299792458;        % [m/s]
+const.T     = 293.15;           % [K]
+
+% rescale unit of measure
+vec.wid  = vec.wid .* 1e-6;     % [m]
+vec.hgt  = vec.hgt .* 1e-6;     % [m]
+vec.temp = vec.temp + const.T;  % [K]
+
+clear ans1 ans2 choice
+
+%% Set initial parameters
+
+tic
+fprintf('\nSetting initial parameters\n');
+
+% phase matching parameters
+% wlens
+pm.pump_w   = 1.55e-6;          % [m]
+pm.signal_w = 1.45e-6;          % [m]   it's an example wl
[…]

### 2015-09-22 gitcode/phase-matching/single_combination.m

@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 1001;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 4001;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -73,7 +73,7 @@ for ww=1:pm.n_sample_wl
 end
 
 % sampling temperature
-pm.n_sample_t = 201;
+pm.n_sample_t = 401;
 pm.step_t = (vec.temp(end) - vec.temp(1) )/(pm.n_sample_t - 1);
 
 vec.sample_temp = zeros(pm.n_sample_t,1);
@@ -101,7 +101,7 @@ setting.fit_str = 'poly52';
 
 for ww=1:par.n_wg_wid
     for hh=1:par.n_wg_hgt
-        for pp=1:1 % no TM
+        for pp=1:2 % w/ TM
             for mm=1:par.n_modi
                 
                 data.fit_neff(ww,hh,pp,mm).exist = false;
@@ -225,9 +225,9 @@ else
     % overwrite here
     TE      = true;
     %TE      = false;
-    pump    = 2;
+    pump    = 5;
     signal  = 1;
-    idler   = 3;
+    idler   = 7;
     if TE
         pm.comb = [1, 1, 1; pump, signal, idler];
     else

### 2015-09-23 latex/davide_bazzanella.tex
break

--- 2015-09-22 latex/article.tex
@@
 Therefore we summarized them by collecting the slopes and the value of the functions at ambient temperature.
-To make the graphs easier to read, we excluded set of data the points of no interest: those which peak had the same frequency $\omega_P = \SI{1.55}{\um}$ of the pump.
+Moreover, to make the graphs easier to read, we excluded from the set of data the points of no interest: those which peak had the same frequency $\omega_P = \SI{1.55}{\um}$ of the pump.
+We had a remaining of four combinations: two TE (\texttt{517} and \texttt{571}) and two TM (\texttt{453} and \texttt{564}).
 
 The first Figure (\ref{fig_sym_pp@t2}) tell us where we found phase-matching condition.
-We can see that we have only two condition in which the phasematch is verified.
-Also, combination \texttt{517} is the symmetric of \texttt{571}.
+We can see that combination \texttt{517} is the symmetric of \texttt{571}, while the remaining TM modes have no symmetric configuration.
+That is because the corresponding symmetric wavelength of, for example, \SI{1.46}{\um} is \SI{1,652}{\um} which is unfortunately out of our wavelength gap.
 
@@
 	\includegraphics[width=.85\textwidth]{ppaat2.png}
-	\caption{Peak position at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler orders. We have two TE conbinations and two TM combinations.}
+	\caption{Peak position at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE conbinations and TM combinations.}
 	\label{fig_sym_pp@t2} 	% pp@t = bandwidth @ T_amb, 2 = no points at 1.55um
@@
 
-The second Figure (\ref{fig_sym_ppc2}) shows us that thant the change in position is of a fraction of \si{\nm}.
+The second Figure (\ref{fig_sym_ppc2}) shows us that the change in position is of a fraction of \si{\nm}.
 This value should be compared to the bandwidth of the phase-match condition.
@@
 	\includegraphics[width=.85\textwidth]{ppc2.png}
-	\caption{Change of peak position. The label of the x axis are to be read as pump-signal-idler orders. We have two TE conbinations and two TM combinations.}
+	\caption{Change of peak position. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE conbinations and TM combinations.}
 	\label{fig_sym_ppc2} % ppc = bandwidth change
@@
 	\includegraphics[width=.85\textwidth]{baat2.png}
-	\caption{Bandwidth at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler orders. We have two TE conbinations and two TM combinations.}
+	\caption{Bandwidth at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE conbinations and TM combinations.}
 	\label{fig_sym_b@t2} % b@t = bandwidth @ T_amb
@@
 This is necessary because a metal plaque over the waveguide core could interfere with the wave propagation in the waveguide itself, drawing energy from the EM wave.
+This could happen in particular for the TM modes, because their field distribution is stronger in the height axis and therefore could easily reach the metal plaque.
 
-\item	Thermal expansion of materials should be considered.
+\item	Although is probably negligible, thermal expansion of materials should be considered.
 While the thermal expansion coefficients of both silicon and silica are small, the temperature change is quite high.
@@
 
-\item	As next step in enhancing the influence of temperature on effective index, different core geometries could be studied.
-This could greatly condition the wave propagation, but it is also a difficult problem with many degrees of freedom.
-
 \end{itemize}
@@
 We had little results in the frequency gap chosen.
-This because we probably need to study further the geometry of the waveguide, in order to enhance the effect of the overlap integrals between the optical mode and the thermal profile.
+This because we probably need to study further the geometry of the waveguide,
+
+As next step in enhancing the influence of temperature on effective index, different core geometries could be studied.
+In order to enhance the effect of the overlap integrals between the optical mode and the thermal profile.
+This could greatly condition the wave propagation, but it is also a difficult problem with many degrees of freedom.
 

### 2015-09-23 latex/davide_bazzanella.tex
is this the end?

@@
 	\centering
-	\includegraphics[width=.45\textwidth]{2Dmodes.png}
+	\includegraphics[width=.4\textwidth]{2Dmodes.png}
 	\caption{Graphical rapresentation of field distribution of 2D modes}
@@
 Only one significant index is then left to describe the order of modes.
-Figure (\ref{fig_ex_mode}) portrays a TE configuration of the third order.
-
-\begin{figure}[hb]
+Figures (\ref{fig_ex_mode_TE}) and (\ref{fig_ex_mode_TM}) portray simulations of TE and TM third order modes.
+\begin{figure}[!hb]
 	\centering
-	\includegraphics[width=0.85\textwidth]{output_mode.pdf}
-	\caption{Example of third order TE mode in a \SI{3}{\um} wide waveguide}
-	\label{fig_ex_mode}
+	\includegraphics[width=0.89\textwidth]{output_modeTE.pdf}
+	\caption{Example of third order TE mode in a \SI{3}{\um} wide waveguide [V/m]}
+	\label{fig_ex_mode_TE}
+\end{figure}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.89\textwidth]{output_modeTM.pdf}
+	\caption{Example of third order TM mode in a \SI{3}{\um} wide waveguide [V/m]}
+	\label{fig_ex_mode_TM}
 \end{figure}
@@
 	\includegraphics[width=.55\textwidth]{spectrum.png}
-	\caption{Measured FWM spectra showing broadband wavelength conversion across \SI{748}{\nm}. The signal, pump, and idler wavelengths are \num{1636}, \num{1940}, and \SI{2384}{\nm}, respectively.}
+	\caption{Measured FWM spectra showing broadband wavelength conversion across \SI{748}{\nm}.
+The signal, pump, and idler wavelengths are \num{1636}, \num{1940}, and \SI{2384}{\nm}, respectively.
+\cite{spectrum}}
 	\label{fig_spectrum}
@@
 \right.
-\label{eq_f&pmc}
+\label{eq_gamma_comparison}
 \end{equation*}
@@
   \label{tab_materials}
-  \caption{Thermal properties of silicon and silica glass}
+  \caption{Thermal properties of silicon and silica glass. \cite{n_db} and }
 \end{table}
@@
 \end{equation}
-where $\mathrm{TOC}|_{\mathrm{Si}} = \SI{1.87e-4}{\per\K}$\cite{n_db} is called Termo-Optic Coefficient.
+where $\mathrm{TOC}|_{\mathrm{Si}} = \SI{1.87e-4}{\per\K}$ is called Termo-Optic Coefficient.
 The coefficient of silica glass is negligible and therefore was considered zero $\mathrm{TOC}|_{\mathrm{SiO}_2} \approx 0$.
@@
 We replaced its value in the conservation of momentum formula, giving us the phase mismatch as a function of signal wavelength and temperature of the heater only, for each set of orders.
-
-%\begin{equation}
 \begin{align*}
@@
 \end{align*}
-%\end{equation}
 
@@
 	\centering
-	\includegraphics[width=.75\textwidth]{delta_example.png}
+	\includegraphics[width=.8\textwidth]{delta_example.png}
 	\caption{Example of $L_{coh}$ at $T_H$ fixed.}
@@
 We obtained graphs representing the position and the bandwidth of peaks vs temperature of each solution.
-
+Figure (\ref{fig_example_position}) gives an example of peak position as a function of temperature $T_H$.
 \begin{figure}[!hb]
 	\centering
-	\includegraphics[width=.75\textwidth]{ex_pos.png}
+	\includegraphics[width=.8\textwidth]{ex_pos.png}
 	\caption{Example of peak position vs $T_H$.}
@@
 	\centering
-	\includegraphics[width=.85\textwidth]{ppaat2.png}
-	\caption{Peak position at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE conbinations and TM combinations.}
+	\includegraphics[width=.85\textwidth]{ppaat22.png}
+	\caption{Peak position at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE combinations and TM combinations.}
 	\label{fig_sym_pp@t2} 	% pp@t = bandwidth @ T_amb, 2 = no points at 1.55um
@@
 	\includegraphics[width=.85\textwidth]{ppc2.png}
-	\caption{Change of peak position. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE conbinations and TM combinations.}
+	\caption{Change of peak position. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE combinations and TM combinations.}
 	\label{fig_sym_ppc2} % ppc = bandwidth change
@@
 Thus, having the same order of magnitude we can state that we have a slight control over peak position with temperature tuning.
+
+Moreover there was almost no change in bandwidth as the temperature arised.
 \begin{figure}[!h]
@@
 	\includegraphics[width=.85\textwidth]{baat2.png}
-	\caption{Bandwidth at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE conbinations and TM combinations.}
+	\caption{Bandwidth at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE combinations and TM combinations.}
 	\label{fig_sym_b@t2} % b@t = bandwidth @ T_amb
@@
 \subsection{Second heater configuration}
-In order to achieve a greater effect from the different temperature, we tried to move the heater from over the center of the core to the side.
+In order to achieve a greater effect from the differences in temperature, we tried to move the heater from over the center of the core to the side.
 This operation was intended to increase the difference of behaviour between low and high orders enabling thus the creation of new peaks in the coherence length.
@@
 	\centering
-	\includegraphics[width=1\textwidth]{geometryA.pdf}
+	\includegraphics[width=.9\textwidth]{geometryA.pdf}
 	\caption{Scheme of the side heater configuration.}
@@
 \subsubsection{data aggregation}
-Unfortunately, examining the graphs obtained from the data analysis of the asymmetric configuration, we do not noticed anything new.
+Unfortunately, examining the graphs obtained from the data analysis of the asymmetric configuration, we found that instead of enhancing the effect, as we hoped, the thermal tuning was inhibited, expecially for the TE modes.
+
+\begin{figure}[!hb]
+	\centering
+	\includegraphics[width=.75\textwidth]{asym_ppc2.png}
+	\caption{Change of peak position. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE combinations and TM combinations.}
+	\label{fig_asym_ppc2} % ppc = bandwidth change
+\end{figure}
 
@@
 
+\item	Thermo-Optic Coefficient also depends on the wavelength of the signal.
+An extended study of this topic should also consider this small factor.
 \end{itemize}
 
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=.75\textwidth]{variationTEsym.png}
+	\caption{Percentage variation of $n_{eff}$ for TE modes at \SI{1.55}{\um} from its value at ambient temperature in the symmetric configuration.}
+	\label{fig_variation}
+\end{figure}
+
 \subsection{Summary}
-We had little results in the frequency gap chosen.
-This because we probably need to study further the geometry of the waveguide,
+Due to the frequency gap chosen, we had few data points.
+A wider range in frequency would have brought more data, but it also would have needed a lot more computational time to complete.
+Therefore it was not in our possibilities.
 
-As next step in enhancing the influence of temperature on effective index, different core geometries could be studied.
-In order to enhance the effect of the overlap integrals between the optical mode and the thermal profile.
-This could greatly condition the wave propagation, but it is also a difficult problem with many degrees of freedom.
+Despite the few data, we could infer that a thermal tuning of the FWM phase-match is, in fact, possible.
+We also understood that the way temperature affects phase-matching is restrained from the limited interaction between the temperature of material and different modes.
 
-\cleardoublepage
+In Figure (\ref{fig_variation}) is represented the change of effective index, for wavelength $\lambda = \SI{1.55}{\um}$, from ambient temperature to \SI{400}{\K} over it in ratio to its value at $T_{amb}=\SI{293.15}{\K}$.
+This curve suggest us that higher orders are more influenced by the difference in temperature than the low orders.
+We can therefore hypothesize that configuration with a high difference between their orders could be controlled better.
+In this view, as next step in enhancing the influence of temperature on effective index, different core geometries should be studied.
+%, in order to maximise the effect of the overlap integrals between the optical mode and the thermal profile.
+This could greatly condition the wave propagation, and therefore the thermal tuning, but it is also a difficult problem with many degrees of freedom.
+
+\clearpage
 \begin{thebibliography}{9}
@@
 \bibitem{Crowder} J. G. Crowder, S. D. Smith, A. Vass, and J. Keddie, “Infrared methods for gas detection,” in Mid-Infrared Semiconductor Optoelectronics. New York: Springer-Verlag, 2006.
-\bibitem{Espinola} R. Espinola, J. Dadap, R. Osgood, Jr., S. McNab, and Y. Vlasov, "C-band wavelength conversion in silicon photonic wire waveguides," Opt. Express 13, 4341-4349 (2005).
+\bibitem{Espinola} R. Espinola, J. Dadap, R. Osgood, Jr., S. McNab, and Y. Vlasov, “C-band wavelength conversion in silicon photonic wire waveguides," Opt. Express 13, 4341-4349 (2005).
 \bibitem{Fukuda} H.
@@
 Takahashi, and S.
-Itabashi, "Four-wave mixing in silicon wire waveguides," Opt.
+Itabashi, “Four-wave mixing in silicon wire waveguides," Opt.
 Express 13, 4629-4637 (2005).
@@
 
-\bibitem{agrawal} G. Agrawal. Nonlinear Fiber Optics, 5th edition. 2013
-\bibitem{saleh} B. E. A. Saleh, M. C. Teich. Fundamentals of photonics, 2nd edition. 2007
+\bibitem{agrawal} Agrawal, Govind. “Nonlinear Fiber Optics", 5th edition. Academic Press, 2013.
+\bibitem{saleh} Saleh, Bahaa EA, and Malvin Carl Teich. “Fundamentals of photonics", 2nd edition. Wiley, 2007
 \bibitem{n_db} http://refractiveindex.info/
-\bibitem{spectrum} Lau, Ryan KW, et al. "Continuous-wave mid-infrared frequency conversion in silicon nanowaveguides." Optics letters 36.7 (2011): 1263-1265.
+\bibitem{spectrum} Lau, Ryan KW, et al. “Continuous-wave mid-infrared frequency conversion in silicon nanowaveguides." Optics letters 36.7 (2011): 1263-1265.
+\bibitem{toc}	Frey, Bradley J., Douglas B.
+Leviton, and Timothy J.
+Madison.
+“Themperature-dependent refractive index of silicon and germanium." SPIE Astronomical Telescopes+ Instrumentation.
+International Society for Optics and Photonics, 2006.
 

### 2015-09-23 gitcode/phase-matching/phasematching_v3.m

@@ -64,7 +64,7 @@ pm.low_w = 1.45e-6;             % [m]
 pm.high_w = 1.65e-6;            % [m]
 
 % number of points in wlen interval [low_w, high_w]
-pm.n_sample_wl = 601;              % should be an odd number, to center the pump wlen.
+pm.n_sample_wl = 1001;              % should be an odd number, to center the pump wlen.
 pm.step = (pm.high_w - pm.low_w)/(pm.n_sample_wl - 1);
 
 vec.sample_wlen = zeros(pm.n_sample_wl,1);
@@ -507,12 +507,14 @@ f = figure('name', 'peak position at ambient temperature');
 axes1 = axes('Parent',f,'XGrid','on','YGrid','on',...
     'XTickLabelRotation', 60,...
     'XTick', [1:1:length(results.indexes2)],...
+    'YTick', [1.45:0.05:1.65],...
     'XTickLabel', tmp,...
     'LineStyleOrderIndex',2);
 hold(axes1,'on');
 title('Peak position at ambient temperature [µm]');
 plot( 1e6*results.max.q(results.indexes2,1:end), 'o' );
 xlim([0 length(results.indexes2)+1])
+ylim([1.44 1.66])
 ylabel({'Position [µm]'});
 xlabel({'Combination'});
 
@@ -563,14 +565,14 @@ xlabel({'Combination'});
 
 %saveas(8, 'bc2', 'png');
 
-% saveas(1, 'ppaat', 'png');
-% saveas(2, 'ppc', 'png');
-% saveas(3, 'baat', 'png');
-% saveas(4, 'bc', 'png');
-% saveas(5, 'ppaat2', 'png');
-% saveas(6, 'ppc2', 'png');
-% saveas(7, 'baat2', 'png');
-% saveas(8, 'bc2', 'png');
+saveas(1, 'ppaat', 'png');
+saveas(2, 'ppc', 'png');
+saveas(3, 'baat', 'png');
+saveas(4, 'bc', 'png');
+saveas(5, 'ppaat2', 'png');
+saveas(6, 'ppc2', 'png');
+saveas(7, 'baat2', 'png');
+saveas(8, 'bc2', 'png');
 
 clear f
 

### 2015-09-24 latex/davide_bazzanella.tex
stampa

@@
 
+\vspace{20pt}
+\noindent\textbf{Keywords}: photonics, SOI, multimode waveguide, nonlinear, FWM, thermo-optic coefficient, thermal tuning
+
 \cleardoublepage 
@@
 Four-Wave Mixing (FWM) is a nonlinear optical effect due to the susceptibility of silicon.
-Silicon is an isotropic material and therefore second order susceptibility $\chi^{(2)}$ (almost) vanishes.
+Silicon is an isotropic material and therefore second order susceptibility $\chi^{(2)}$ vanishes.
 Third order susceptibility $\chi^{(3)}$, on the other hand, is non-zero and is responsible among the other effects for FWM, which is indeed a third order phenomenon.
@@
 
-From the definition of $\phi_-$ and $\phi_+$ we can gather that there are two types of FWM.
-The term containing $\phi_-$ corresponds to the case in which two photons at frequencies $\omega_1$ and $\omega_2$ are annihilated, while two photons at frequencies $\omega_3$ and $\omega_4$ are created simultaneously.
-On the other hand, the term containing $\phi_+$ corresponds to the case in which three photons at frequencies $\omega_1$, $\omega_2$ and $\omega_3$ are annihilated, while one photon at frequency $\omega_4$ is created.
+From the definition of $\phi_+$ and $\phi_-$ we can gather that there are two types of FWM.
+The term containing $\phi_+$ corresponds to the case in which three photons at frequencies $\omega_1$, $\omega_2$ and $\omega_3$ are annihilated, while one photon at frequency $\omega_4$ is created.
+On the other hand, the term containing $\phi_-$ corresponds to the case in which two photons at frequencies $\omega_1$ and $\omega_2$ are annihilated, while two photons at frequencies $\omega_3$ and $\omega_4$ are created simultaneously.
 
@@
 Considering a peak power $P_1+P_2 = \SI{1}{\W}$ of the pump and a sample length $L_{sam} = \SI{1}{\cm}$ we obtain
-\begin{equation*}
+\begin{equation}
 \left\{
@@
 \label{eq_gamma_comparison}
-\end{equation*}
+\end{equation}
 
@@
 
-Therefore, in order to be efficient, the parametric process needs to verify the conservation of both energy and momentum, as given in Eq. (\ref{eq_f&pmc}).
+Therefore, in order to be efficient, the parametric process needs to verify the conservation of both energy and momentum, as given in Eq. (\ref{eq_f&pmc}):
+
+\begin{equation*}
+\left\{
+ 	\begin{aligned}
+		\omega_I &= 2\omega_P - \omega_S \\
+		\Delta k &= 2\beta_P - \beta_S - \beta_I = 0
+	\end{aligned}
+\right.
+\end{equation*}
 
@@
     	\multirow{2}{*}{Materials}    & $\rho$ & $\kappa_{TH}$ & $C_P$ & TOC\\
-  		& [\si{\kg\m^3}] & [\si{\W\per(\m\K)}] & [\si{\J\per(\kg\K)}] & [\si{\per\K}] \\
+  		& [\si{\kg/\m^3}] & [\si{\W\per(\m\K)}] & [\si{\J\per(\kg\K)}] & [\si{\per\K}] \\
     \midrule
@@
   \label{tab_materials}
-  \caption{Thermal properties of silicon and silica glass. \cite{n_db} and }
+  \caption{Thermal properties of silicon and silica glass. \cite{n_db} and \cite{toc}}
 \end{table}
@@
 \begin{equation}
-n = n(\lambda)+\mathrm{TOC}\cdot (T-T_{amb})
+n = n(\lambda)+\mathrm{TOC}\cdot (T(x,y)-T_{amb})
 \end{equation}
@@
 
+\begin{figure}[!hb]
+	\centering
+	\includegraphics[width=1\textwidth]{thermal.pdf}
+	\caption{Contour graph of a stationary solution for $T_H = T_{amb} + \SI{400}{\K}$}
+	\label{fig_ex_thermal}
+\end{figure}
+
 It was necessary to set the boundary conditions: the two sides (left, right) and the bottom were considered as thermal reservoirs with a temperature $T = T_{amb} = \SI{293.15}{\K}$.
@@
 We considered the typical laboratory condition.
+
+An example of solution is given in Figure (\ref{fig_ex_thermal}).
 
@@
 
-This algorithm was set to find the eight modes whose effective index $n_{eff}$ was closest to $n_{eff}=4$ in absolute value.
+This algorithm was set to find the fifteen modes whose effective index $n_{eff}$ was closest to $n_{eff}=4$ in absolute value.
 \subsubsection{Data output}
 We obtained the field distribution and a series of parameters as our data output for each parametric configuration.
-In particular the parameters were the effective index $n_{eff}$, the effective area $A_{eff}$ and the nonlinear parameter $\gamma$, for each mode and for each wavelength and temperature.
+In particular the parameters were the effective index $n_{eff}$ and the effective area $A_{eff}$, for each mode and for each wavelength and temperature.
 
@@
 The ratio between the maxima values of the x-component and y-component of the electric field allowed to distinguish the mode type: TE or TM.
-Those fields which had the maximum component in the y direction were categorized as TE modes while those which had the maximum component in the x direction as TM modes.
+Those fields which had the maximum component in the x direction were categorized as TE modes while those which had the maximum component in the y direction as TM modes.
 The number of maxima of the modulus of the field showed us the order of the mode.
 
-We obtained then a well organized data matrix filled with the value of effective index $n_{eff}$, effective area $A_{eff}$ and nonlinear parameter $\gamma$ for each combination of parameters.
+We obtained then a well organized data matrix filled with the value of effective index $n_{eff}$ and effective area $A_{eff}$ for each combination of parameters.
 
 \subsection{Data processing}
-We focused on the information given by the effective index.
+We used the $A_{eff}$ data to evaluate the nonlinear parameter $\gamma$ and verify Eq. (\ref{eq_gamma_comparison}).
+We focused then on the information given by the effective index.
 
@@
 
-Specifically, we used a polynomial expression of fifth order in wavelength and second order in temperature ``\texttt{poly52}".
+Specifically, we used a polynomial expression of fifth order in wavelength and second order in temperature ``\texttt{poly52}", which is defined as:
+\begin{align*}
+	\texttt{poly52} = \,\,
+		&p00 
+		+ p10x + p01y
+		+ p20x^2 + p11xy + p02y^2
+		+ p30x^3 + p21x^2y + p12xy^2 +\\
++\,\,	&p40x^4 + p31x^3y + p22x^2y^2 
+		+ p50x^5 + p41x^4y + p32x^3y^2
+\end{align*}
+where $x=\lambda$ and $y=T_H$
 
@@
 	\Delta k &= 2\beta_P(\omega_P)-\beta_S(\omega_S)-\beta_I(2\omega_P-\omega_S)\\
-			 &= 2\pi\left[ 2\frac{n_{eff}^P(\lambda_P)}{\lambda_P}
-			 - \frac{n_{eff}^S(\lambda_S)}{\lambda_S}
-			 - \frac{n_{eff}^I(\lambda_I)}{\lambda_I}\right]
+			 &= 2\pi\left[ 2\frac{n_{eff}^P(\lambda_P,T_H)}{\lambda_P}
+			 - \frac{n_{eff}^S(\lambda_S,T_H)}{\lambda_S}
+			 - \frac{n_{eff}^I(\lambda_I,T_H)}{\lambda_I}\right]
 \end{align*}
@@
 
-Another important parameter is the width of the peak: to be consistent with the seletion criteria used in (\ref{eq_lcoh_crit}), we defined the bandwidth as the peak width at $L_{coh} = 1$.
+Another important parameter is the width of the peak: to be consistent with the seletion criteria used in (\ref{eq_lcoh_crit}), we defined the bandwidth as the peak width at
+$$L_{coh}/L_{sam} = 1$$
 
 We obtained graphs representing the position and the bandwidth of peaks vs temperature of each solution.
-Figure (\ref{fig_example_position}) gives an example of peak position as a function of temperature $T_H$.
+Figures (\ref{fig_example_position}) and (\ref{fig_example_bandwidth}) give an example of peak position and bandwidth as a functions of temperature $T_H$.
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=.75\textwidth]{ex_pos.png}
+	\caption{Example of peak position vs $T_H$, zoomed in an area between \SI{1.6}{\um} and \SI{1.61}{\um}.
+The smoothness of the curve is correlated to the step of evaluation in wavelength ($\Delta \lambda = \SI{0.05}{\nm}$)}
+	\label{fig_example_position}
+\end{figure}
+
 \begin{figure}[!hb]
 	\centering
-	\includegraphics[width=.8\textwidth]{ex_pos.png}
-	\caption{Example of peak position vs $T_H$.}
-	\label{fig_example_position}
+	\includegraphics[width=.75\textwidth]{ex_bw.png}
+	\caption{Example of bandwidth vs $T_H$. The figure has a little ripple which is correlated to the step of evaluation in wavelength ($\Delta \lambda = \SI{0.05}{\nm}$).}
+	\label{fig_example_bandwidth}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=.75\textwidth]{variationTEsym.png}
+	\includegraphics[width=.75\textwidth]{variation.png}
 	\caption{Percentage variation of $n_{eff}$ for TE modes at \SI{1.55}{\um} from its value at ambient temperature in the symmetric configuration.}
@@
 In Figure (\ref{fig_variation}) is represented the change of effective index, for wavelength $\lambda = \SI{1.55}{\um}$, from ambient temperature to \SI{400}{\K} over it in ratio to its value at $T_{amb}=\SI{293.15}{\K}$.
-This curve suggest us that higher orders are more influenced by the difference in temperature than the low orders.
+This curve suggest us that low orders are more influenced by the difference in temperature than high orders.
 We can therefore hypothesize that configuration with a high difference between their orders could be controlled better.
@@
 \bibitem{saleh} Saleh, Bahaa EA, and Malvin Carl Teich. “Fundamentals of photonics", 2nd edition. Wiley, 2007
-\bibitem{n_db} http://refractiveindex.info/
 \bibitem{spectrum} Lau, Ryan KW, et al. “Continuous-wave mid-infrared frequency conversion in silicon nanowaveguides." Optics letters 36.7 (2011): 1263-1265.
@@
 International Society for Optics and Photonics, 2006.
+\bibitem{n_db} http://refractiveindex.info/
 

### 2015-09-24 presentazione/presentazione.tex
stampa

\documentclass[11pt]{beamer}
%\usetheme{Montpellier}
\usetheme{Dresden}
\usepackage[utf8]{inputenc}
\usepackage[italian]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[compatibility=false]{caption}
\usepackage{subcaption}
\usepackage{multicol}
\author{Davide Bazzanella}
\title{Thermal tuning of phase-matching in a multimodal SOI waveguide with $\chi^{(3)}$ non linearity}
\date{28 settembre 2015} 
%\textsc{\LARGE \textbf{DEPARTMENT OF PHYSICS}}\\[0.5cm]
%\textsc{\LARGE \textbf{DEGREE IN PHYSICS – LAUREA IN FISICA}}\\[2.5cm]
%\textsc{\Large THESIS}\\[1.3cm]

%\setbeamercovered{transparent} 
\setbeamertemplate{navigation symbols}{} 
%\logo{} 
%\institute{} 
%\subject{}

\usepackage{lmodern}
\newcommand{\frameofframes}{/}
\newcommand{\setframeofframes}[1]{\renewcommand{\frameofframes}{#1}}

\setframeofframes{of}
\makeatletter
\setbeamertemplate{footline}
  {%
    \begin{beamercolorbox}[colsep=1.5pt]{upper separation line foot}
    \end{beamercolorbox}
    \begin{beamercolorbox}[ht=2.5ex,dp=1.125ex,%
      leftskip=.3cm,rightskip=.3cm plus1fil]{author in head/foot}%
      \leavevmode{\usebeamerfont{author in head/foot}\insertshortauthor}%
      \hfill%
      {\usebeamerfont{institute in head/foot}\usebeamercolor[fg]{institute in head/foot}\insertshortinstitute}%
    \end{beamercolorbox}%
    \begin{beamercolorbox}[ht=2.5ex,dp=1.125ex,%
      leftskip=.3cm,rightskip=.3cm plus1fil]{title in head/foot}%
      {\usebeamerfont{title in head/foot}\insertshorttitle}%
      \hfill%
      {\usebeamerfont{frame number}\usebeamercolor[fg]{frame number}\insertframenumber~\frameofframes~\inserttotalframenumber}
    \end{beamercolorbox}%
    \begin{beamercolorbox}[colsep=1.5pt]{lower separation line foot}
    \end{beamercolorbox}
  }
\makeatother

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Outline}
\footnotesize \tableofcontents
\end{frame}

\section{Introduction}
ciao
\section{Nonlinear Optics}
\subsection{Four-Wave Mixing}
\subsection{Conservation of energy and momentum}
\subsubsection{Multimodal Waveguides}
\subsection{Peak tuning}
\subsubsection{Thermo-Optic Coefficient}
\section{Computational model}
\subsection{Mode simulation}
\subsection{•}
\subsection{Results}
\section{Conclusion}

\end{document}

### 2015-09-24 gitcode/phase-matching/single_combination.m

@@ -73,7 +73,7 @@ for ww=1:pm.n_sample_wl
 end
 
 % sampling temperature
-pm.n_sample_t = 401;
+pm.n_sample_t = 1001;
 pm.step_t = (vec.temp(end) - vec.temp(1) )/(pm.n_sample_t - 1);
 
 vec.sample_temp = zeros(pm.n_sample_t,1);
@@ -316,6 +316,7 @@ toc
 
 %% 3D surface plot w/ temperature
 % creat grid of evaluation
+%{
 tic
 [wlen_grid, temp_grid]  = meshgrid(vec.sample_wlen, vec.sample_temp);
 
@@ -327,9 +328,10 @@ zlim(axes1,[0 2]);
 
 toc
 clear wlen_grid temp_grid axes1 f
+%}
 
 %% 2D contour plots
-
+%{
 tic
 [wlen_grid, temp_grid]  = meshgrid(vec.sample_wlen, vec.sample_temp);
 
@@ -345,6 +347,7 @@ contour(f_Lcoh_cm(wlen_grid, temp_grid)>=1);
 toc
 
 clear wlen_grid temp_grid axes1 f
+%}
 
 %% 2D plots of center & bandwidth
 
@@ -426,7 +429,8 @@ f = figure('name', name); % 'OuterPosition',[100, 100, 960, 480]
 axes1 = axes('Parent',f);
 hold(axes1,'on');
 plot(vec.sample_temp, peaks.*1e6 );
-ylim(axes1, [1.4 1.7] );
+ylim( [1.6 1.61] );
+%ylim(axes1, [1.4 1.7] );
 %axis([250 700 1.4e-6 1.7e-6]);
 
 % Create xlabel

### 2015-09-25 latex_raster/davide_bazzanella.tex
Errata corrige e presentazione

--- 2015-09-24 latex/davide_bazzanella.tex
@@
 	\centering
-	\includegraphics[width=0.89\textwidth]{output_modeTE.pdf}
+	\includegraphics[width=0.89\textwidth]{output_modeTE.png}
 	\caption{Example of third order TE mode in a \SI{3}{\um} wide waveguide [V/m]}
@@
 	\centering
-	\includegraphics[width=0.89\textwidth]{output_modeTM.pdf}
+	\includegraphics[width=0.89\textwidth]{output_modeTM.png}
 	\caption{Example of third order TM mode in a \SI{3}{\um} wide waveguide [V/m]}
@@
 	\centering
-	\includegraphics[width=1\textwidth]{geometry.pdf}
+	\includegraphics[width=1\textwidth]{geometry.png}
 	\label{fig_wg_Section}
@@
 We positioned a thermal reservoir, a ``\textit{heater}", \SI{0.3}{\um} wide at the top of the cladding, exactly over the center of the waveguide core and set to mantain a specific temperature $T_H$ in the gap $[\SI{293.15}{\K} - \SI{693.15}{\K}]$, given by the configuration chosen.
-To solve the heat equation we defined the density $\rho$ in [\si{\kg\m^3}], the thermal conductivity $\kappa_{TH}$ in [\si{\W\per\m\per\K}] and the heat capacity $C_P$ in [\si{\J\per\kg\per\K}] of the different materials.
+To solve the heat equation we defined the density $\rho$ in [\si{\kg\per\m^3}], the thermal conductivity $\kappa_{TH}$ in [\si{\W\per(\m\K)}] and the heat capacity $C_P$ in [\si{\J\per(\kg\K)}] of the different materials.
 
@@
   \label{tab_materials}
-  \caption{Thermal properties of silicon and silica glass. \cite{n_db} and \cite{toc}}
+  \caption{Thermal properties of silicon and silica glass. \cite{toc} and \cite{n_db}}
 \end{table}
@@
 \end{equation}
-where $\mathrm{TOC}|_{\mathrm{Si}} = \SI{1.87e-4}{\per\K}$ is called Termo-Optic Coefficient.
+where $\mathrm{TOC}|_{\mathrm{Si}} = \SI{1.87e-4}{\per\K}$ is called Thermo-Optic Coefficient.
 The coefficient of silica glass is negligible and therefore was considered zero $\mathrm{TOC}|_{\mathrm{SiO}_2} \approx 0$.
@@
 	\centering
-	\includegraphics[width=1\textwidth]{thermal.pdf}
+	\includegraphics[width=1\textwidth]{thermal.png}
 	\caption{Contour graph of a stationary solution for $T_H = T_{amb} + \SI{400}{\K}$}
@@
 This value should be compared to the bandwidth of the phase-match condition.
-In order to be interesting, its order of magnitude should be the same as the order of the bandwidth.
+In order to be interesting, its order of magnitude should be the same as the order of the bandwidth, or at most one order of magnitude less than the bandwith.
 
-\begin{figure}[!h]
+\begin{figure}[ht]
 	\centering
@@
 Moreover there was almost no change in bandwidth as the temperature arised.
-\begin{figure}[!h]
+\begin{figure}[hb]
 	\centering
@@
 	\centering
-	\includegraphics[width=.9\textwidth]{geometryA.pdf}
+	\includegraphics[width=.9\textwidth]{geometryA.png}
 	\caption{Scheme of the side heater configuration.}
@@
 	\centering
-	\includegraphics[width=.75\textwidth]{variation.png}
-	\caption{Percentage variation of $n_{eff}$ for TE modes at \SI{1.55}{\um} from its value at ambient temperature in the symmetric configuration.}
+	\includegraphics[width=.75\textwidth]{TOEvariation.png}
+	\caption{Effective TOE for TE modes at \SI{1.55}{\um}.}
 	\label{fig_variation}
@@
 
-In Figure (\ref{fig_variation}) is represented the change of effective index, for wavelength $\lambda = \SI{1.55}{\um}$, from ambient temperature to \SI{400}{\K} over it in ratio to its value at $T_{amb}=\SI{293.15}{\K}$.
-This curve suggest us that low orders are more influenced by the difference in temperature than high orders.
+In Figure (\ref{fig_variation}) is represented the effective TOE of different modes, for wavelength $\lambda = \SI{1.55}{\um}$.
+This curve suggest us that high orders are more influenced by the difference in temperature than low orders.
 We can therefore hypothesize that configuration with a high difference between their orders could be controlled better.

### 2015-09-25 presentazione/presentazione.tex
Errata corrige e presentazione

@@
-\documentclass[11pt]{beamer}
+\documentclass[11pt, leqno]{beamer}
 %\usetheme{Montpellier}
@@
 \usepackage[utf8]{inputenc}
-\usepackage[italian]{babel}
+\usepackage[english]{babel}
 \usepackage{amsmath}
@@
 \usepackage{multicol}
+
+\usepackage{siunitx}
+\usepackage{wrapfig}
+%\usepackage{float}
+
+\usepackage{caption}
+\usepackage{subcaption}
+
 \author{Davide Bazzanella}
@@
 \begin{frame}{Outline}
-\footnotesize \tableofcontents
+%\footnotesize
+\tableofcontents
 \end{frame}
@@
 \section{Introduction}
-ciao
+\begin{frame}{Introduction}
+
+	\textbf{Research field}:\\
+	bio-sensors, gas sensors and bio-medical instrumentation
+
+	\vspace{5pt}
+	\textbf{Problem}:\\
+	lack of sources/sensors in the MIR (3-10\si{\um})
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=\textwidth]{spectrum2.png}
+	\end{figure}
+\end{frame}
+\begin{frame}
+	\textbf{Solution}:\\
+	frequency down convertion from NIR/VIS sources to MIR\\
+	frequency up convertion from MIR signals to NIR/VIS sensor
+
+	\begin{figure}[hb]
+%		\centering
+%		\begin{subfigure}[c]{.725\textwidth}
+			\centering
+			\includegraphics[width=.75\textwidth]{upconversion2_short.png}
+%			\caption{}
+%		\end{subfigure}
+%		\hspace{0.02\textwidth}
+%		\begin{subfigure}[c]{.225\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{upconverter_HITACHI.png}
+%			\caption{}
+%		\end{subfigure}
+	\end{figure}	
+%	\vspace{15pt}
+	\textbf{Aim}:\\
+	Develop integrated frequency converter tunable with temperature
+\end{frame}
+
 \section{Nonlinear Optics}
-\subsection{Four-Wave Mixing}
-\subsection{Conservation of energy and momentum}
-\subsubsection{Multimodal Waveguides}
-\subsection{Peak tuning}
-\subsubsection{Thermo-Optic Coefficient}
+\begin{frame}{Nonlinear Optics}
+	Frequency convertion employs nonlinear properties of materials
+	\begin{equation}
+		\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) = \mathrm{\textbf{P}_L} + \mathrm{\textbf{P}_{NL}}
+		\label{eq_P_general}
+	\end{equation}
+	\begin{wrapfigure}{r}{0.33\textwidth}
+		\centering
+		\includegraphics[width=.3\textwidth]{upconverter_HITACHI.png}
+	\end{wrapfigure}
+	\begin{itemize}
+	\item	$\chi^{(1)}$	:	linear part
+	\item	$\chi^{(2)}$	:	2$^{nd}$ order nonlinearity\\ \hspace{25pt} (SHG, TWM)
+	\item	$\chi^{(3)}$	:	3$^{rd}$ order nonlinearity\\ \hspace{25pt} (THG, FWM)
+	\end{itemize}
+\end{frame}
+%\subsection{Four-Wave Mixing}
+\begin{frame}{Four-Wave Mixing}
+	%\begin{wrapfigure}{r}{0.22\textwidth}
+	%    \includegraphics[width=.22\textwidth]{photons.png}
+	%\end{wrapfigure}
+	\begin{wrapfigure}{r}{0.35\textwidth}
+		\vspace{-20pt}
+	    \includegraphics[width=.33\textwidth]{W&K.png}
+	\end{wrapfigure}
+	FWM uses 3$^{rd}$ order nonlinearity $\chi^{(3)}$.
+	%\begin{wrapfigure}{r}{0.22\textwidth}
+	%    \includegraphics[width=.22\textwidth]{momentum.png}
+	%\end{wrapfigure}
+
+	\vspace{10pt}
+	It consists of the interaction between four EM waves of different frequencies.
+	\begin{align}
+	\omega_1 + \omega_2 &= \omega_3 + \omega_4\\
+	k_1 + k_2 &= k_3 + k_4
+	\label{eq_general_f}
+	\end{align}
+
+	\vspace{5pt}
+	Special case:\\ $\omega_1 = \omega_2 = \omega_P$, with stimulation.
+\end{frame}
+%\subsection{Conservation of energy and momentum}
+\begin{frame}{Conservation of energy and momentum}
+	\begin{figure}
+		\centering
+		\vspace{10pt}
+		\includegraphics[width=.8\textwidth]{setup_b&w.png}
+	\end{figure}
+	Conservation of energy is naturally verified
+	\begin{equation}
+		\omega_I = 2\omega_P - \omega_S = \omega_P \pm \Omega
+		\label{eq_energy}
+	\end{equation}
+	Conservation of momentum is imposed on the phase-mismatch
+	\begin{equation}
+		\Delta k = 2\,k_P(\omega_P) - k_S(\omega_S) -k_I(\omega_I) = 0
+		\label{eq_momentum}
+	\end{equation}
+	%\begin{equation*}
+	%\mathrm{where} \qquad k = \frac{\omega}{c} = \frac{2\pi}{\lambda}
+	%\end{equation*}
+\end{frame}
+\begin{frame}
+	Generation happens also for $\Delta k \approx 0$, but at lower efficiency.
+	\begin{wrapfigure}{r}{0.5\textwidth}
+		\vspace{10pt}
+		\centering
+	    \includegraphics[width=.5\textwidth]{sinc2.png}
+	\end{wrapfigure}
+	\begin{equation}
+	\begin{split}
+		I_I &\propto \left| \int_0^L exp(\mathrm{i}\Delta k z)dz\right| \\
+			&\propto L^2 sinc(\Delta k / 2\pi)
+	\end{split}
+	\end{equation}
+	We define the coherence length
+	\begin{equation}
+		L_{coh} = \frac{2\pi}{|\Delta k|}
+	\label{eq_coherence_length}
+	\end{equation}
+\end{frame}
+\begin{frame}
+	Bulk silicon does not permit to verify both equations.
+	\begin{equation}
+	k(\omega) = k_0 n(\omega)
+	\label{eq_k(w)}
+	\end{equation}
+	\begin{figure}
+		\centering
+%		\vspace{-5pt}
+		\includegraphics[width=0.8\textwidth]{RefractiveIndexINFO.pdf}
+		\label{fig_silicon_dispersion}
+	\end{figure}
+\end{frame}
+%\subsubsection{Multimodal Waveguides}
+\begin{frame}{Multimodal Waveguides}
+	In silicon waveguides both equations can be verified.\\
+	Therefore Eq. \eqref{eq_momentum} becomes:
+	\begin{equation}
+		\Delta k = 2\,\beta_P(\omega_P) -\beta_S(\omega_S) -\beta_I(\omega_I)
+		\label{eq_beta}
+	\end{equation}
+	\begin{equation*}
+		\mathrm{where} \qquad	\beta(\omega) = k_0 n_{eff}(\omega)
+	\end{equation*}
+	\vspace{-5pt}
+	\begin{itemize}
+	\item	If the waveguide supports only one mode, phase-matching is only near the frequency of the pump and $\Omega \ll \omega_P$
+	\item	If the waveguide is multimodal, there are more matching conditions and also $\Omega \lesssim \omega_P$.
+	\end{itemize}
+\end{frame}
+
+%\subsection{Phase-matching tuning}
+\begin{frame}{Phase-matching tuning}
+	\begin{wrapfigure}{r}{0.5\textwidth}
+		\vspace{-10pt}
+		\centering
+	    \includegraphics[width=.55\textwidth]{narrow_bandwidth.png}
+	\end{wrapfigure}
+	Phase-matching conditions have narrow bandwidth.
+
+	\vspace{20pt}
+	It is difficult to obtain phase-matching at the required wavelength.
+
+	\vspace{20pt}
+	We aim to tune with temperature the range where phase-matching is verified.
+\end{frame}
+%\subsubsection{Thermo-Optic Coefficient}
+\begin{frame}{Thermo-Optic Coefficient}
+	Refractive index of silicon is influenced from the temperature.
+
+	\begin{equation}
+	\begin{split}
+		n 	&= n(\omega,T(x,y)) \\
+			&= n(\omega,T_{amb}) + \mathrm{TOC}\cdot(T(x,y)-T_{amb})
+		\label{eq_refractive_index}
+	\end{split}
+	\end{equation}
+
+	\vspace{10pt}
+	Different modes react differently at the change of temperature.
+	\begin{equation}
+		n_{eff} = n_{eff}(\omega,T_{amb}) + \mathrm{TOC}_{eff}\cdot(T_H-T_{amb})
+		\label{eq_effective_index}
+	\end{equation}
+\end{frame}
+\begin{frame}
+	\begin{figure}
+		\centering
+		\vspace{-10pt}
+		\includegraphics[width=.8\textwidth]{effectiveTOC.pdf}
+		\label{fig_TOC_effective}
+		\vspace{-10pt}
+	\end{figure}
+	It should be possible to control phase-matching with temperature.
+\end{frame}
 \section{Computational model}
-\subsection{Mode simulation}
-\subsection{•}
-\subsection{Results}
+\begin{frame}{Computational model}
+	\begin{figure}
+%		\vspace{-15pt}
+		\centering
+		\includegraphics[width=\textwidth]{geometry.pdf}
+	\end{figure}
+\end{frame}
+%\subsection{Temperature simulation}
+\begin{frame}{Temperature simulation}
+	\begin{figure}
+%		\vspace{-15pt}
+		\centering
+		\includegraphics[width=\textwidth]{thermal.pdf}
+	\end{figure}
+\end{frame}
+%\subsection{Mode simulation}
+\begin{frame}{Mode simulation}
+	\begin{figure}
+%		\vspace{-15pt}
+		\centering
+		\includegraphics[width=\textwidth]{output_modeTE.pdf}
+	\end{figure}
+\end{frame}
+\begin{frame}{Mode simulation}
+	\begin{figure}
+%		\vspace{-15pt}
+		\centering
+		\includegraphics[width=\textwidth]{output_modeTM.pdf}
+	\end{figure}
+\end{frame}
+\section{Data analysis}
+\begin{frame}{Data analysis}
+	\begin{itemize}
+	\item	Data extraction from comsol to matlab.
+	\item	Data classification (TE/TM, order).
+	\item	Data processing:\\
+			\begin{itemize}
+			\item	polynomial fit of $\lambda$ and $T_H$.
+			\item	evaluation of phase-mismatch \eqref{eq_momentum} with \eqref{eq_beta} and \eqref{eq_effective_index}
+					\begin{equation}
+					\Delta k = 2	 \frac{2\pi}{ \lambda_P } n_{eff}(\lambda_P,T_H)
+								-\frac{2\pi}{ \lambda_S } n_{eff}(\lambda_S,T_H)
+								-\frac{2\pi}{ \lambda_I } n_{eff}(\lambda_I,T_H)
+					\end{equation}
+					and coherence length $L_{coh} = \frac{2\pi}{|\Delta k|}$.
+			\end{itemize}
+	\item	Data selection: verify condition $L_{coh}/L_{sam} \geq 1$.
+	\item	Data aggregation.
+	\end{itemize}
+\end{frame}
+\section{Results}
+\begin{frame}{Results: symmetric configuration}
+	\begin{figure}
+%		\vspace{-15pt}
+		\centering
+		\includegraphics[height=.8\textheight]{ppaat22.png}
+	\end{figure}
+\end{frame}
+\begin{frame}
+	\begin{figure}
+%		\vspace{-15pt}
+		\centering
+		\includegraphics[height=.9\textheight]{baat2.png}
+	\end{figure}
+\end{frame}
+\begin{frame}
+	\begin{figure}
+%		\vspace{-15pt}
+		\centering
+		\includegraphics[height=.9\textheight]{ppc2.png}
+	\end{figure}
+\end{frame}
+\begin{frame}
+	Combination \texttt{TE 517}, symmetric configuration.
+	\begin{figure}
+%		\vspace{-15pt}
+		\centering
+		\includegraphics[width=.8\textwidth]{bandwidth_movement_TE517_sym.png}
+	\end{figure}
+\end{frame}
+\begin{frame}{Asymmetric configuration}
+	\begin{figure}
+%		\vspace{-15pt}
+		\centering
+		\includegraphics[width=\textwidth]{geometryA.pdf}
+	\end{figure}
+\end{frame}
+\begin{frame}
+	\begin{figure}
+%		\vspace{-15pt}
+		\centering
+		\includegraphics[height=.85\textheight]{asym_ppc2.png}
+	\end{figure}
+\end{frame}
 \section{Conclusion}
-
+%\subsection{Improvements}
+\begin{frame}{Improvements}
+	\begin{itemize}
+		\item	The heater should be simulated as a metal conductor media, instead of a simple boundary condition (TM modes).
+		\item	Thermo-Optic Coefficient also depends on the wavelength of the signal.
+		\item	Different core geometries should be studied.
+		\item	Develop the correlation also between temperature and efficiency of energy conversion.
+	\end{itemize}
+\end{frame}
+%\subsection{Summary}
+\begin{frame}{Summary}
+	\begin{itemize}
+		\item Configurations with a high difference between their orders are to be preferred.
+		\item Limited interaction between the temperature of material and different modes is a constraint.
+		\item Thermal tuning of the FWM phase-match is, in fact, possible.
+	\end{itemize}
+\end{frame}
 \end{document}

### 2015-09-25 gitcode/phase-matching/single_combination.m

@@ -73,7 +73,7 @@ for ww=1:pm.n_sample_wl
 end
 
 % sampling temperature
-pm.n_sample_t = 1001;
+pm.n_sample_t = 11;
 pm.step_t = (vec.temp(end) - vec.temp(1) )/(pm.n_sample_t - 1);
 
 vec.sample_temp = zeros(pm.n_sample_t,1);

### 2015-09-26 latex/davide_bazzanella.tex
final version?

@@
 	\centering
-	\includegraphics[width=1\textwidth]{geometry.pdf}
+	\includegraphics[width=1\textwidth]{geometryR.pdf}
 	\label{fig_wg_Section}
@@
 	\centering
-	\includegraphics[width=.9\textwidth]{geometryA.pdf}
+	\includegraphics[width=.9\textwidth]{geometryAR.pdf}
 	\caption{Scheme of the side heater configuration.}
@@
 	\centering
-	\includegraphics[width=.75\textwidth]{variation.png}
-	\caption{Percentage variation of $n_{eff}$ for TE modes at \SI{1.55}{\um} from its value at ambient temperature in the symmetric configuration.}
+	\includegraphics[width=.7\textwidth]{effectiveTOC.pdf}
+	\caption{Effective TOC for TE modes at \SI{1.55}{\um}.}
 	\label{fig_variation}
@@
 
-In Figure (\ref{fig_variation}) is represented the change of effective index, for wavelength $\lambda = \SI{1.55}{\um}$, from ambient temperature to \SI{400}{\K} over it in ratio to its value at $T_{amb}=\SI{293.15}{\K}$.
-This curve suggest us that low orders are more influenced by the difference in temperature than high orders.
+In Figure (\ref{fig_variation}) is represented the effective TOC of different modes, for wavelength $\lambda = \SI{1.55}{\um}$.
+This curve suggest us that high orders are more influenced by the difference in temperature than low orders.
 We can therefore hypothesize that configuration with a high difference between their orders could be controlled better.

### 2015-09-26 presentazione/presentazione.tex
final version?

@@
 	\end{equation}
-	\begin{wrapfigure}{r}{0.33\textwidth}
+	\begin{wrapfigure}{r}{0.48\textwidth}
 		\centering
-		\includegraphics[width=.3\textwidth]{upconverter_HITACHI.png}
+		\includegraphics[width=.5\textwidth]{ppln-ovens2.jpg}
 	\end{wrapfigure}
@@
 \begin{frame}{Four-Wave Mixing}
-	%\begin{wrapfigure}{r}{0.22\textwidth}
-	%    \includegraphics[width=.22\textwidth]{photons.png}
-	%\end{wrapfigure}
-	\begin{wrapfigure}{r}{0.35\textwidth}
+	\begin{wrapfigure}{r}{0.33\textwidth}
 		\vspace{-20pt}
-	    \includegraphics[width=.33\textwidth]{W&K.png}
+	    \includegraphics[width=.33\textwidth]{photons.png}
 	\end{wrapfigure}
+%	\begin{wrapfigure}{r}{0.35\textwidth}
+%		\vspace{-20pt}
+%	    \includegraphics[width=.33\textwidth]{W&K.png}
+%	\end{wrapfigure}
 	FWM uses 3$^{rd}$ order nonlinearity $\chi^{(3)}$.
@@
 	%\end{wrapfigure}
+	\begin{wrapfigure}{r}{0.45\textwidth}
+		\vspace{-55pt}
+	    \includegraphics[width=.45\textwidth]{frequency.png}
+	\end{wrapfigure}
 
@@
 	\end{equation}
-	Conservation of momentum is imposed on the phase-mismatch
+	Conservation of momentum is imposed in the phase-mismatch
 	\begin{equation}
@@
 		I_I &\propto \left| \int_0^L exp(\mathrm{i}\Delta k z)dz\right| \\
-			&\propto L^2 sinc(\Delta k / 2\pi)
+			&\propto L^2 sinc^2(\Delta k L/ 2\pi)
 	\end{split}
@@
 \begin{frame}{Phase-matching tuning}
-	\begin{wrapfigure}{r}{0.5\textwidth}
-		\vspace{-10pt}
+	\begin{wrapfigure}{r}{0.55\textwidth}
+%		\vspace{-10pt}
 		\centering
-	    \includegraphics[width=.55\textwidth]{narrow_bandwidth.png}
+	    \includegraphics[width=.6\textwidth]{narrow_bandwidth.png}
 	\end{wrapfigure}
@@
 \begin{frame}{Computational model}
+	Definition of the problem: geometry, materials.\\
+	Simulation with FEM in Comsol.
 	\begin{figure}
@@
 		\centering
-		\includegraphics[width=\textwidth]{geometry.pdf}
+		\includegraphics[width=\textwidth]{geometryR.pdf}
 	\end{figure}
@@
 \begin{frame}{Temperature simulation}
+	Stationary solution of heat transfer equation:\\
+	parameter $T_H$ and boundary conditions.
 	\begin{figure}
@@
 \begin{frame}{Mode simulation}
+	Modes as solutions of the Helmholtz equation:\\
+	frequency as parameter and boundary conditions.
 	\begin{figure}
@@
 \begin{frame}{Mode simulation}
+	Both TE, TM, and \textit{leaky} modes were obtained.
 	\begin{figure}
@@
 \begin{frame}{Asymmetric configuration}
+	We aimed to increase the difference of behaviour between low and high orders.
 	\begin{figure}
@@
 		\centering
-		\includegraphics[width=\textwidth]{geometryA.pdf}
+		\includegraphics[width=\textwidth]{geometryAR.pdf}
 	\end{figure}
@@
 		\item	The heater should be simulated as a metal conductor media, instead of a simple boundary condition (TM modes).
-		\item	Thermo-Optic Coefficient also depends on the wavelength of the signal.
+		\item	Thermo-Optic Coefficient also depends on the wavelength of the signal. It is important for high $\Omega$ conversions.
 		\item	Different core geometries should be studied.
@@
 	\begin{itemize}
-		\item Configurations with a high difference between their orders are to be preferred.
-		\item Limited interaction between the temperature of material and different modes is a constraint.
+		\item Configurations with a high difference in TOC between their orders are to be preferred.
+		\item %Limited interaction between the temperature of material and different modes is a constraint.
+		Optimization of the overlap between the thermal and optical spatial profiles in order to maximize the difference of effective TOC in the selected modes.
 		\item Thermal tuning of the FWM phase-match is, in fact, possible.
